---
title: "ConvertPickletoRda"
author: "Sarah Tennant"
date: "28/01/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### ----------------------------------------------------------------------------------------------- ###

## This code loads dataframes with spatial firing of neurons in the virtual reality

Aim: We want to load dataframes from python output which are in pickled format, and save them in Rs dataframe format (.Rda). 

### ----------------------------------------------------------------------------------------------- ###


First we need to set up the python environment. This is so we can call a python script from R that loads the pickled dataframes and sends it back to the R workspace. 
The python environment needs to be >v.3 as 2.7 (system python) doesn't have Pandas package which is needed to open dataframes

To find the path in Linux use 'type -a python3' in the terminal.
```{r}

require(reticulate) # package that allows R to call python code
#Sys.setenv(RETICULATE_PYTHON = "C:\\Users\\44756\\AppData\\Local\\Programs\\Python\\Python310\\python.exe") 
Sys.setenv(RETICULATE_PYTHON = "/usr/bin/python3") 
```


### ----------------------------------------------------------------------------------------------- ###

### LOAD ALL MICE ALL DAYS DATAFRAMES

### ----------------------------------------------------------------------------------------------- ###

## Loading dataframe for all mice and days (all curated cells from one animal/multiple animals)

1. load python code to load pickle dataframe
```{r}
source_python("pickle_reader.py") # run python script which loads the dataframes - should be in working directory

```

2. Load all cohorts, and necessary columns for analysis

## cols needed 
c('session_id', 'cluster_id', 'Mouse', 'Day', 'Day_numeric',  'cohort', 'number_of_rewards', 'max_trial_number','brain_region', 'ramp_score','mean_firing_rate','spikes_in_time', 'Rates_averaged_rewarded_b', 'Rates_averaged_rewarded_nb', 'Rates_averaged_rewarded_p', 'graduation', 'average_stops', 'average_stops_p', 'Avg_FiringRate_RunTrials', 'Avg_FiringRate_TryTrials', 'Avg_FiringRate_HitTrials', 'rewardzone_speed_run', 'rewardzone_speed_try', 'rewardzone_speed_hit', 'speed_in_time_reward', 'speed_in_time_run', 'speed_in_time_try', 'spikes_in_time_reward', 'spikes_in_time_run', 'spikes_in_time_try', 'Speed_mean_rewarded', 'Speed_mean_try', 'Speed_mean_run', 'speed_score', 'speed_score_p_values', 'hd_score', 'rayleigh_score', 'spatial_information_score', 'grid_score', 'border_score', 'speed_threshold_pos', 'speed_threshold_neg', 'hd_threshold', 'rayleigh_threshold', 'spatial_threshold', 'grid_threshold', 'border_threshold','mean_firing_rate_of', 'spike_width', ))

```{r}
dataframe_to_load <- "data_in/Processed_cohort2_with_OF_unsmoothened.pkl"  
spatial_firing1 <- read_pickle_file(file.path(dataframe_to_load)) 
spatial_firing1 <- select(spatial_firing1,c('session_id', 'cluster_id', 'Mouse', 'Day', 'Day_numeric',  'cohort', 'number_of_rewards', 'max_trial_number','brain_region', 'ramp_score','mean_firing_rate','spikes_in_time', 'Rates_averaged_rewarded_b', 'Rates_averaged_rewarded_nb', 'Rates_averaged_rewarded_p', 'Rates_averaged_rewarded_smoothed_b', 'Rates_sd_rewarded_smoothed_b', 'Rates_averaged_rewarded_smoothed_nb', 'Rates_sd_rewarded_smoothed_nb', 'Rates_averaged_rewarded_smoothed_p', 'Rates_sd_rewarded_smoothed_p','Avg_FiringRate_TryTrials_smoothed','SD_FiringRate_TryTrials_smoothed', 'Avg_FiringRate_HitTrials_smoothed', 'SD_FiringRate_HitTrials_smoothed', 'Avg_FiringRate_RunTrials_smoothed', 'SD_FiringRate_RunTrials_smoothed','graduation', 'average_stops', 'average_stops_p', 'Avg_FiringRate_RunTrials', 'Avg_FiringRate_RunTrials_nb', 'Avg_FiringRate_TryTrials', 'Avg_FiringRate_TryTrials_nb', 'Avg_FiringRate_HitTrials', 'Avg_FiringRate_HitTrials_nb', 'Avg_FiringRate_SlowTryTrials', 'Avg_FiringRate_SlowTryTrials_nb', 'Avg_FiringRate_FastTryTrials', 'Avg_FiringRate_FastTryTrials_nb', 'rewardzone_speed_run', 'rewardzone_speed_try', 'rewardzone_speed_hit', 'speed_in_time_reward', 'speed_in_time_run', 'speed_in_time_try', 'spikes_in_time_reward', 'spikes_in_time_run', 'spikes_in_time_try', 'Speed_mean_rewarded', 'Speed_mean_try', 'Speed_mean_run', 'speed_score', 'speed_score_p_values', 'hd_score', 'rayleigh_score', 'spatial_information_score', 'grid_score', 'border_score', 'speed_threshold_pos', 'speed_threshold_neg', 'hd_threshold', 'rayleigh_threshold', 'spatial_threshold', 'grid_threshold', 'border_threshold','mean_firing_rate_of', 'spike_width'))

dataframe_to_load <- "data_in/Processed_cohort3_with_OF_unsmoothened.pkl" 
spatial_firing2 <- read_pickle_file(file.path(dataframe_to_load)) 
spatial_firing2 <- select(spatial_firing2,c('session_id', 'cluster_id', 'Mouse', 'Day', 'Day_numeric',  'cohort', 'number_of_rewards', 'max_trial_number','brain_region', 'ramp_score','mean_firing_rate','spikes_in_time', 'Rates_averaged_rewarded_b', 'Rates_averaged_rewarded_nb', 'Rates_averaged_rewarded_p', 'Rates_averaged_rewarded_smoothed_b', 'Rates_sd_rewarded_smoothed_b', 'Rates_averaged_rewarded_smoothed_nb', 'Rates_sd_rewarded_smoothed_nb', 'Rates_averaged_rewarded_smoothed_p', 'Rates_sd_rewarded_smoothed_p','Avg_FiringRate_TryTrials_smoothed','SD_FiringRate_TryTrials_smoothed', 'Avg_FiringRate_HitTrials_smoothed', 'SD_FiringRate_HitTrials_smoothed', 'Avg_FiringRate_RunTrials_smoothed', 'SD_FiringRate_RunTrials_smoothed','graduation', 'average_stops', 'average_stops_p', 'Avg_FiringRate_RunTrials', 'Avg_FiringRate_RunTrials_nb', 'Avg_FiringRate_TryTrials', 'Avg_FiringRate_TryTrials_nb', 'Avg_FiringRate_HitTrials', 'Avg_FiringRate_HitTrials_nb', 'Avg_FiringRate_SlowTryTrials', 'Avg_FiringRate_SlowTryTrials_nb', 'Avg_FiringRate_FastTryTrials', 'Avg_FiringRate_FastTryTrials_nb', 'rewardzone_speed_run', 'rewardzone_speed_try', 'rewardzone_speed_hit', 'speed_in_time_reward', 'speed_in_time_run', 'speed_in_time_try', 'spikes_in_time_reward', 'spikes_in_time_run', 'spikes_in_time_try', 'Speed_mean_rewarded', 'Speed_mean_try', 'Speed_mean_run', 'speed_score', 'speed_score_p_values', 'hd_score', 'rayleigh_score', 'spatial_information_score', 'grid_score', 'border_score', 'speed_threshold_pos', 'speed_threshold_neg', 'hd_threshold', 'rayleigh_threshold', 'spatial_threshold', 'grid_threshold', 'border_threshold','mean_firing_rate_of', 'spike_width'))

dataframe_to_load <- "data_in/Processed_cohort4_with_OF_unsmoothened.pkl" 
spatial_firing3 <- read_pickle_file(file.path(dataframe_to_load)) 
spatial_firing3 <- select(spatial_firing3,c('session_id', 'cluster_id', 'Mouse', 'Day', 'Day_numeric',  'cohort', 'number_of_rewards', 'max_trial_number','brain_region', 'ramp_score','mean_firing_rate','spikes_in_time', 'Rates_averaged_rewarded_b', 'Rates_averaged_rewarded_nb', 'Rates_averaged_rewarded_p', 'Rates_averaged_rewarded_smoothed_b', 'Rates_sd_rewarded_smoothed_b', 'Rates_averaged_rewarded_smoothed_nb', 'Rates_sd_rewarded_smoothed_nb', 'Rates_averaged_rewarded_smoothed_p', 'Rates_sd_rewarded_smoothed_p','Avg_FiringRate_TryTrials_smoothed','SD_FiringRate_TryTrials_smoothed', 'Avg_FiringRate_HitTrials_smoothed', 'SD_FiringRate_HitTrials_smoothed', 'Avg_FiringRate_RunTrials_smoothed', 'SD_FiringRate_RunTrials_smoothed','graduation', 'average_stops', 'average_stops_p', 'Avg_FiringRate_RunTrials', 'Avg_FiringRate_RunTrials_nb', 'Avg_FiringRate_TryTrials', 'Avg_FiringRate_TryTrials_nb', 'Avg_FiringRate_HitTrials', 'Avg_FiringRate_HitTrials_nb', 'Avg_FiringRate_SlowTryTrials', 'Avg_FiringRate_SlowTryTrials_nb', 'Avg_FiringRate_FastTryTrials', 'Avg_FiringRate_FastTryTrials_nb', 'rewardzone_speed_run', 'rewardzone_speed_try', 'rewardzone_speed_hit', 'speed_in_time_reward', 'speed_in_time_run', 'speed_in_time_try', 'spikes_in_time_reward', 'spikes_in_time_run', 'spikes_in_time_try', 'Speed_mean_rewarded', 'Speed_mean_try', 'Speed_mean_run', 'speed_score', 'speed_score_p_values', 'hd_score', 'rayleigh_score', 'spatial_information_score', 'grid_score', 'border_score', 'speed_threshold_pos', 'speed_threshold_neg', 'hd_threshold', 'rayleigh_threshold', 'spatial_threshold', 'grid_threshold', 'border_threshold','mean_firing_rate_of', 'spike_width'))

dataframe_to_load <- "data_in/Processed_cohort5_with_OF_unsmoothened.pkl" 
spatial_firing4 <- read_pickle_file(file.path(dataframe_to_load))
spatial_firing4 <- select(spatial_firing4,c('session_id', 'cluster_id', 'Mouse', 'Day', 'Day_numeric',  'cohort', 'number_of_rewards', 'max_trial_number','brain_region', 'ramp_score','mean_firing_rate','spikes_in_time', 'Rates_averaged_rewarded_b', 'Rates_averaged_rewarded_nb', 'Rates_averaged_rewarded_p', 'Rates_averaged_rewarded_smoothed_b', 'Rates_sd_rewarded_smoothed_b', 'Rates_averaged_rewarded_smoothed_nb', 'Rates_sd_rewarded_smoothed_nb', 'Rates_averaged_rewarded_smoothed_p', 'Rates_sd_rewarded_smoothed_p','Avg_FiringRate_TryTrials_smoothed','SD_FiringRate_TryTrials_smoothed', 'Avg_FiringRate_HitTrials_smoothed', 'SD_FiringRate_HitTrials_smoothed', 'Avg_FiringRate_RunTrials_smoothed', 'SD_FiringRate_RunTrials_smoothed','graduation', 'average_stops', 'average_stops_p', 'Avg_FiringRate_RunTrials', 'Avg_FiringRate_RunTrials_nb', 'Avg_FiringRate_TryTrials', 'Avg_FiringRate_TryTrials_nb', 'Avg_FiringRate_HitTrials', 'Avg_FiringRate_HitTrials_nb', 'Avg_FiringRate_SlowTryTrials', 'Avg_FiringRate_SlowTryTrials_nb', 'Avg_FiringRate_FastTryTrials', 'Avg_FiringRate_FastTryTrials_nb', 'rewardzone_speed_run', 'rewardzone_speed_try', 'rewardzone_speed_hit', 'speed_in_time_reward', 'speed_in_time_run', 'speed_in_time_try', 'spikes_in_time_reward', 'spikes_in_time_run', 'spikes_in_time_try', 'Speed_mean_rewarded', 'Speed_mean_try', 'Speed_mean_run', 'speed_score', 'speed_score_p_values', 'hd_score', 'rayleigh_score', 'spatial_information_score', 'grid_score', 'border_score', 'speed_threshold_pos', 'speed_threshold_neg', 'hd_threshold', 'rayleigh_threshold', 'spatial_threshold', 'grid_threshold', 'border_threshold','mean_firing_rate_of', 'spike_width'))

dataframe_to_load <- "data_in/Processed_cohort7_with_OF_unsmoothened.pkl"  
spatial_firing5 <- read_pickle_file(file.path(dataframe_to_load)) 
spatial_firing5 <- select(spatial_firing5,c('session_id', 'cluster_id', 'Mouse', 'Day', 'Day_numeric',  'cohort', 'number_of_rewards', 'max_trial_number','brain_region', 'ramp_score','mean_firing_rate','spikes_in_time', 'Rates_averaged_rewarded_b', 'Rates_averaged_rewarded_nb', 'Rates_averaged_rewarded_p', 'Rates_averaged_rewarded_smoothed_b', 'Rates_sd_rewarded_smoothed_b', 'Rates_averaged_rewarded_smoothed_nb', 'Rates_sd_rewarded_smoothed_nb', 'Rates_averaged_rewarded_smoothed_p', 'Rates_sd_rewarded_smoothed_p','Avg_FiringRate_TryTrials_smoothed','SD_FiringRate_TryTrials_smoothed', 'Avg_FiringRate_HitTrials_smoothed', 'SD_FiringRate_HitTrials_smoothed', 'Avg_FiringRate_RunTrials_smoothed', 'SD_FiringRate_RunTrials_smoothed','graduation', 'average_stops', 'average_stops_p', 'Avg_FiringRate_RunTrials', 'Avg_FiringRate_RunTrials_nb', 'Avg_FiringRate_TryTrials', 'Avg_FiringRate_TryTrials_nb', 'Avg_FiringRate_HitTrials', 'Avg_FiringRate_HitTrials_nb', 'Avg_FiringRate_SlowTryTrials', 'Avg_FiringRate_SlowTryTrials_nb', 'Avg_FiringRate_FastTryTrials', 'Avg_FiringRate_FastTryTrials_nb', 'rewardzone_speed_run', 'rewardzone_speed_try', 'rewardzone_speed_hit', 'speed_in_time_reward', 'speed_in_time_run', 'speed_in_time_try', 'spikes_in_time_reward', 'spikes_in_time_run', 'spikes_in_time_try', 'Speed_mean_rewarded', 'Speed_mean_try', 'Speed_mean_run', 'speed_score', 'speed_score_p_values', 'hd_score', 'rayleigh_score', 'spatial_information_score', 'grid_score', 'border_score', 'speed_threshold_pos', 'speed_threshold_neg', 'hd_threshold', 'rayleigh_threshold', 'spatial_threshold', 'grid_threshold', 'border_threshold','mean_firing_rate_of', 'spike_width'))

```

3. Concatinate cohorts together
```{r}
spatial_firing <- rbind(spatial_firing1, spatial_firing2, spatial_firing3, spatial_firing4, spatial_firing5)
```

### ----------------------------------------------------------------------------------------------- ###

### Save concatenated frames for future loading

### ----------------------------------------------------------------------------------------------- ###

6. Save final concatinated dataframe
```{r}
saveRDS(spatial_firing, file="data_in/PythonOutput_Concat_final.Rda")

```



