---
title: "DataSet_Stats"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Script performs basic stats (n numbers, ttest etc) on the dataset

### ----------------------------------------------------------------------------------------- ###

### How many neurons passed criteria in the linear model ? 

1. get numbers of cells for each lm group (positive/negative/unclassified)
```{r}
start <- nrow(subset(spatial_firing, lm_result_o_rewarded == "Negative"))
reward <- nrow(subset(spatial_firing, lm_result_o_rewarded == "Positive"))
nonslope <- nrow(subset(spatial_firing, lm_result_o_rewarded == "Unclassified"))

```

2. find and plot proportions for ramp types in dataset
```{r}
# positive homebound slopes
start <- nrow(subset(spatial_firing, lm_result_o_rewarded == "Negative"))/nrow(spatial_firing)*100
reward <- nrow(subset(spatial_firing, lm_result_o_rewarded == "Positive"))/nrow(spatial_firing)*100
nonslope <- nrow(subset(spatial_firing, lm_result_o_rewarded == "Unclassified"))/nrow(spatial_firing)*100

```


### ----------------------------------------------------------------------------------------- ###

### How much of the shuffled dataset is past criteria? 

1. Proportion of cells in the shuffled datasets that pass criteria
```{r}
shuff_ramps <- nrow(subset(spatial_firing,lm_result_o_shuff == "Positive" | lm_result_o_shuff == "Negative" ))/nrow(spatial_firing)*100
non_shuff_ramps <- nrow(subset(spatial_firing,lm_result_o_shuff == "None" | lm_result_o_shuff == "NoSlope" ))/nrow(spatial_firing)*100

```


### ----------------------------------------------------------------------------------------- ###

### correlate linear model result (i.e. positive/negative/unclassified) with ramp score

1. Extract ramp score 
_since its a list of three (outbound/homebound/all) we extract the first one_
```{r}
extract_ramp_score <- function(df){
  dx <- df[[1]]
  return(dx)
}

spatial_firing <- spatial_firing %>%
  mutate(start_ramp_score = map(ramp_score, extract_ramp_score))

```

2. find apsolute ramp scores for -ve and +ve slopes
```{r}

positive_ramps <- subset(spatial_firing, lm_result_o_rewarded == "Positive")
negative_ramps <- subset(spatial_firing, lm_result_o_rewarded == "Negative")

#shuff_positive_ramps <- subset(spatial_firing, lm_result_o_shuff == "Positive")
#shuff_negative_ramps <- subset(spatial_firing, lm_result_o_shuff == "Negative")

```

3. find apsolute ramp scores for -ve and +ve slopes
```{r}

positive_ramps_scores <- tibble(ramp_score = as.numeric(positive_ramps$start_ramp_score))
negative_ramps_scores <- tibble(ramp_score = as.numeric(negative_ramps$start_ramp_score))

```

4. Find mean of the ramp scores
```{r}
abs_pos_ramp <- positive_ramps_scores  %>%
  summarise(mean(ramp_score, na.rm = TRUE), sd(ramp_score, na.rm = TRUE))
abs_neg_ramp <- negative_ramps_scores  %>%
  summarise(mean(ramp_score, na.rm = TRUE), sd(ramp_score, na.rm = TRUE))
```


## perform ttest on ramp scores

```{r}
positive_ramps_scores <- as.numeric(positive_ramps$start_ramp_score)
shuff_positive_ramps_scores <- as.numeric(shuff_positive_ramps$start_ramp_score)

# paired t-test
t.test(positive_ramps_scores,shuff_positive_ramps_scores) # where y1 & y2 are numeric


negative_ramps_scores <- as.numeric(negative_ramps$start_ramp_score)
shuff_negative_ramps_scores <- as.numeric(shuff_negative_ramps$start_ramp_score)

# paired t-test
t.test(negative_ramps_scores,shuff_negative_ramps_scores) # where y1 & y2 are numeric
```

