---
title: "RampCodes_Figure3"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

---
title: "RampCodes_Figure3"
author: "Sarah Tennant & Matt Nolan"
date: "20/10/2021"
output: html_document
---

### --------------------------------------------------------------------------------- ###
## Compares ramp scores to open field spatial scores. 


First, we are interested to see what proportion of neurons have the following patterns of activity in the open field:

1. Grid cells
2. Head direction
3. Border

To classify cells into these categories above, we will use the classification established in (https://www.sciencedirect.com/science/article/pii/S0896627317301873). 


### ----------------------------------------------------------------------------------------- ###

### Create joined ID for unique mouse identifier (some mice have similar names but in different cohorts)

### ----------------------------------------------------------------------------------------- ###

1. make function to join mouse and cohort into one label
```{r}
join_mouse_cohort <- function(mouse, cohort_n){
  if (is.na(cohort_n)) {
    return('NaN')
  }  
  df <- paste0(mouse, "_", cohort_n)
  df
}

```

2. run on all cells
```{r}
spatial_firing <- spatial_firing %>%
  mutate(joined_id = map2(Mouse, cohort, join_mouse_cohort))

```


### ----------------------------------------------------------------------------------------- ###

### Classify neurons by their open field activity

### ----------------------------------------------------------------------------------------- ###

```{r}
is_grid_cell <- function(grid_score, grid_threshold){
  if (is.na(grid_score) | is.na(grid_threshold) ) {
    return( "NaN" )  
  } else if( as.numeric(grid_score) > as.numeric(grid_threshold)) {
    return( "1" ) 
  } else {
    return("0")
  }
}

```

```{r}
is_border_cell <- function(border_score, border_threshold){
  if (is.na(border_score) | is.na(border_threshold)) {
    return( "NaN" )  
  } else if( as.numeric(border_score) > as.numeric(border_threshold)) {
    return( "1" ) 
  } else {
    return("0")
  }
}

```

```{r}
is_HD_cell <- function(hd_score, hd_threshold){
  if (is.na(hd_score) | is.na(hd_threshold)) {
    return( "NaN" )  
  } else if( as.numeric(hd_score) > as.numeric(hd_threshold)) {
    return( "1" ) 
  } else {
    return("0")
  }
}

```

```{r}
is_speed_cell <- function(speed_score, speed_threshold){
  if (is.na(speed_score) | is.na(speed_threshold)) {
    return( "NaN" )  
  } else if( as.numeric(speed_score) > as.numeric(speed_threshold)) {
    return( "1" ) 
  } else {
    return("0")
  }
}

```

```{r}
is_spatial_cell <- function(spatial_score, spatial_threshold){
  if (is.na(spatial_score) | is.na(spatial_threshold)) {
    return( "NaN" )  
  } else if( as.numeric(spatial_score) > as.numeric(spatial_threshold)) {
    return( "1" ) 
  } else {
    return("0")
  }
}

```

1. run on all cells
```{r}
spatial_firing <- spatial_firing %>%
  mutate(grid_cell = map2(grid_score, grid_threshold, is_grid_cell)) %>%
  mutate(border_cell = map2(border_score, border_threshold, is_border_cell)) %>%
  mutate(HD_cell = map2(hd_score, hd_threshold, is_HD_cell)) %>%
  mutate(speed_cell = map2(speed_score, spatial_threshold, is_speed_cell)) %>%
  mutate(nongrid_cell = map2(spatial_information_score, spatial_threshold, is_spatial_cell))

```



```{r}
classify_cells <- function(grid_cell, border_cell, HD_cell, nongrid_cell){
  if (is.na(grid_cell) & is.na(border_cell) & is.na(HD_cell) & is.na(nongrid_cell)) {
    return( "NI" )  
  } else if( grid_cell == 1) {
    return( "G" ) 
  } else if( border_cell == 1) {
    return( "B" ) 
  } else if( nongrid_cell == 1) {
    return( "NG" ) 
  } else if( HD_cell == 1) {
    return( "HD" ) 
  } else if( (grid_cell == 0 & border_cell == 0 & HD_cell == 0 & nongrid_cell == 0)) {
    return( "NS" ) 
  } else {
    return("NS")
  }
}

```


1. run on all cells
```{r}
spatial_firing <- spatial_firing %>%
  mutate(classifier = pmap(list(grid_cell, border_cell, HD_cell, nongrid_cell), classify_cells))

```




```{r}
classify_cells2 <- function(classifier){
  if( classifier == "G") {
    return( "Grid" ) 
  } else if( classifier == "B") {
    return( "Border" ) 
  } else if( classifier == "NG") {
    return( "Spatial" ) 
  } else if( classifier == "HD") {
    return( "Pure HD" ) 
  } else if( classifier == "NS") {
    return( "Non-Spatial" ) 
  } else if( classifier == "NI") {
    return( "Not-identified" ) 
  } else {
    return("Non-Spatial")
  }
}

```


1. run on all cells
```{r}
spatial_firing <- spatial_firing %>%
  mutate(classifier2 = map(classifier, classify_cells2))

```


### ----------------------------------------------------------------------------------------- ###

### Find proportion of spatial cells

### ----------------------------------------------------------------------------------------- ###
First, we want to know out of our dataset, how many cells classified as grid, border, pure head direction etc. 

Find number of cells in each spatial catagory (grid, border, HD etc)
```{r}
# Distribution of open arena cell types among positionally modulated ramping neurons
spatial_firing %>%
  filter(final_model_o_b == "P" | final_model_o_b == "PS" | final_model_o_b == "PA" | final_model_o_b == "PSA") %>% 
  filter(cohort == 7) %>% 
  filter(track_category_numeric !=0) %>%
  select(classifier2) %>%
  mutate(classifier2 = unlist(classifier2)) %>%
  unlist() %>%
  table()

# Position modulated ramping neurons  
arena_track_ramp <- spatial_firing %>%
  filter(cohort == 7,
         final_model_o_b == "P" | final_model_o_b == "PS" | final_model_o_b == "PA" | final_model_o_b == "PSA") %>% 
  filter(track_category_numeric !=0) %>%
  select(classifier2, final_model_o_b) %>%
  mutate(classifier2 = unlist(classifier2),
         final_model_o_b = unlist(final_model_o_b)) %>%
  table()
arena_track_ramp <- cbind(arena_track_ramp, total = rowSums(arena_track_ramp))
(arena_track_ramp <- rbind(arena_track_ramp, sum = colSums(arena_track_ramp)))

# All neurons
arena_track_all <- spatial_firing %>%
  filter(track_category_numeric !=0) %>%
  select(classifier2, final_model_o_b) %>%
  mutate(classifier2 = unlist(classifier2),
         final_model_o_b = unlist(final_model_o_b)) %>%
  table()
arena_track_all <- cbind(arena_track_all, total = rowSums(arena_track_all))
(arena_track_all <- rbind(arena_track_all, sum = colSums(arena_track_all)))

```


### ----------------------------------------------------------------------------------- ###

Now we might want to see a plot of this, with proportions split according to type of ramp cell in VR i.e. position ramp, speed ramps, all cells.

The y-axis 'Arena type' shows the proportion of each arena field (e.g. grid border, etc) within each population of the track cells (e.g. positional ramp, other ramp, non-ramp).

1. First find proportions of functional cell types by animal for all cells
```{r}
cell_types_prop <- function(df) {
  df %>% select(joined_id, classifier2) %>%
    mutate(joined_id = unlist(joined_id),
           classifier2 = unlist(classifier2)) %>%
    group_by(joined_id, classifier2) %>%
    summarise(n = n()) %>%
    mutate(proportion = n / sum(n),
           percent = proportion * 100)
}

# Proportions by animal
all_cells_percent <- spatial_firing %>%
  filter(cohort == 7) %>%
  cell_types_prop()

# Summary across animals
all_cells_summary <- all_cells_percent %>%
  group_by(classifier2) %>%
  summarise(avg = mean(proportion), sd = std.error(proportion), min=min(proportion), max=max(proportion))

```


# Proportions separately for postional ramp, other ramp and other cells
```{r}
position_ramp_percent <- spatial_firing %>%
  filter(cohort == 7,
         lm_group_b == "Positive" | lm_group_b == "Negative",
         final_model_o_b == "P" | final_model_o_b == "PS" | final_model_o_b == "PA" | final_model_o_b == "PSA") %>%
  cell_types_prop()

other_ramp_percent <- spatial_firing %>%
  filter(cohort == 7,
         lm_group_b == "Positive" | lm_group_b == "Negative",
         !(final_model_o_b == "P" | final_model_o_b == "PS" | final_model_o_b == "PA" | final_model_o_b == "PSA")) %>%
  cell_types_prop()

other_cells_percent <- spatial_firing %>%
  filter(cohort == 7,
         !(lm_group_b == "Positive" | lm_group_b == "Negative")) %>%
  cell_types_prop()

# check groups are complete (should be TRUR)
sum(position_ramp_percent$n) + sum(other_ramp_percent$n) + sum(other_cells_percent$n)  == sum(all_cells_percent$n)
```
Add group labels and combine
```{r}
position_ramp_percent$group <- "PosRamp"
other_ramp_percent$group <- "OtherRamp"
other_cells_percent$group <- "NonRamp"
df_all <- rbind(position_ramp_percent, other_ramp_percent, other_cells_percent)
```


Make box plot and plot all at the same time
```{r}
ggplot(df_all, aes(x=classifier2, y=percent)) + 
  coord_cartesian(ylim=c(0,100)) +
  #stat_summary(fun.data=mean_sdl, mult=1, geom="pointrange", color="red") +
  geom_boxplot(aes(fill = group), alpha=0.9, outlier.colour="black", outlier.shape=16,
             outlier.size=2, notch=FALSE) +
  scale_fill_manual(values=c("brown2", "darkturquoise", "darkorange","blueviolet", "blue3")) +
  theme_classic() +
  labs(y = "Arena type (%)", x ="") +
  theme(axis.text.x = element_text(angle = 70)) +
  theme(axis.text.x=element_text(hjust=1)) +
  theme(axis.text.x = element_text(size=18),
        axis.text.y = element_text(size=18),
        legend.position="bottom", 
        legend.title = element_blank(),
        text = element_text(size=18), 
        legend.text=element_text(size=18), 
        axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0))) 
ggsave(file = "plots/OFAnalysis_proportionsBOX.png", width = 4.5, height = 5.5)

```


### ----------------------------------------------------------------------------------- ###

### ----------------------------------------------------------------------------------- ###

Make a plot where the y-axis 'Ramp type' shows the proportion of each ramp type(e.g. positional ramp, other ramp, non-ramp) within each population of arena cells (e.g. grid border, etc).

Use 'spatial_firing$track_category_numeric' to identify ramping cells.

track_category_numeric is defined in Figure 1:
Homebound   Outbound    Text label    Numeric label
Positive    Positive    pospos        1
Positive    Negative    posneg        2
Positive    Unlcassified    posnon    3
Negative    Negative    negneg        4
Negative    Positive    negpos        5
Negative    Unclassified    negnon    6
Other                                 0

```{r}
ramp_cat <- function(classifier, final_model_o_b){
  if( classifier != 0 ) {
    if(final_model_o_b == "P" | final_model_o_b == "PSA" | final_model_o_b == "PA" | final_model_o_b == "PS") {
    return( "Ramp_position" ) 
  } else {return( "Ramp_Other" ) 
  }
  } else {return("None")}
}

spatial_firing <- spatial_firing %>%
  mutate(ramp_type = map2(track_category_numeric, final_model_o_b, ramp_cat))
```



```{r}
all_cells_percent <- spatial_firing  %>%
  filter(cohort == 7) %>% 
  select(joined_id, classifier2, ramp_type) %>%
  mutate(joined_id = unlist(joined_id),
         classifier2= unlist(classifier2),
         ramp_type = unlist(ramp_type)) %>%
  group_by(joined_id, classifier2, ramp_type) %>%
  summarise(n = n()) %>%
  mutate(proportion = n / sum(n),
         percent = proportion*100,
         classifier2 = as.character(classifier2),
         ramp_type = as.character(ramp_type))

(all_cells_percent_summary <- all_cells_percent %>%
  group_by(classifier2, ramp_type) %>%
  summarise(avg = mean(proportion),
         sd = std.error(proportion),
         min=min(proportion),
         max=max(proportion)))

summary(aov(proportion ~ factor(ramp_type), data = filter(all_cells_percent, classifier2 == "Border")))
summary(aov(proportion ~ factor(ramp_type), data = filter(all_cells_percent, classifier2 == "Grid")))
summary(aov(proportion ~ factor(ramp_type), data = filter(all_cells_percent, classifier2 == "Non-Spatial")))
summary(aov(proportion ~ factor(ramp_type), data = filter(all_cells_percent, classifier2 == "Pure HD")))
summary(aov(proportion ~ factor(ramp_type), data = filter(all_cells_percent, classifier2 == "Spatial")))
```

Make plot
```{r}
ggplot(data=subset(all_cells_percent, ramp_type != "NULL"), aes(x=classifier2, y=percent,fill = factor(ramp_type))) + 
  #coord_cartesian(ylim=c(0,100)) +
  #stat_summary(fun.data=mean_sdl, mult=1, geom="pointrange", color="red") +
  geom_boxplot(aes(fill = ramp_type), alpha=0.9, outlier.colour="black", outlier.shape=16,
             outlier.size=2, notch=FALSE) +
  scale_fill_manual(values=c("brown2", "darkturquoise", "darkorange","blueviolet", "blue3")) +
  theme_classic() +
  labs(y = "Ramp type (%)", x ="") +
  theme(axis.text.x = element_text(angle = 70)) +
  theme(axis.text.x=element_text(hjust=1)) +
  theme(axis.text.x = element_text(size=18),
        axis.text.y = element_text(size=18),
        legend.position="bottom", 
        legend.title = element_blank(),
        text = element_text(size=18), 
        legend.text=element_text(size=18), 
        axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0))) 
ggsave(file = "plots/OFAnalysis_proportionsBOX_22.png", width = 4.5, height = 5.5)

```

### Now look at speed modulation

```{r}
spatial_firing %>% filter(cohort == 7) %>%
  select(speed_score, joined_id, ramp_type) %>%
  mutate(speed_score = unlist(speed_score),
         joined_id = unlist(joined_id),
         ramp_type = unlist(ramp_type)) %>%
  ggplot(aes(ramp_type, speed_score)) +
  geom_jitter() +
  geom_violin(alpha = 0.5) +
  labs(x = "", y = "Speed score") +
  theme_classic()+
  theme(text = element_text(size=20))

speed_by_ramp <- spatial_firing %>%
  filter(cohort == 7) %>%
  select(speed_score, joined_id, ramp_type) %>%
  mutate(speed_score = unlist(speed_score),
         joined_id = unlist(joined_id),
         ramp_type = unlist(ramp_type))
summary(aov(speed_score ~ ramp_type, speed_by_ramp))

speed_props <- spatial_firing %>%
  filter(cohort == 7) %>%
  select(speed_cell, joined_id, ramp_type) %>%
  mutate(speed_cell = unlist(speed_cell),
         joined_id = unlist(joined_id),
         ramp_type = unlist(ramp_type)) %>%
  group_by(ramp_type, speed_cell, joined_id) %>%
  summarise(n = n()) %>%
  mutate(proportion = n / sum(n),
         percent = proportion*100)

speed_props %>% ggplot(aes(ramp_type, proportion)) +
  geom_boxplot() +
  labs(x = "", y = "Speed score") +
  theme_classic()+
  theme(text = element_text(size=20))


(speed_props_summary <- speed_props %>%
    group_by(speed_cell, ramp_type) %>%
    summarise(avg = mean(proportion),
              sd = std.error(proportion),
              min=min(proportion),
              max=max(proportion)))

```

Compare track speed cells with arena speed cells
```{r}
spatial_firing %>% filter(cohort == 7) %>%
  select(speed_score, joined_id, ramp_type, o_b_mod_coefs_speed) %>%
  filter(ramp_type != "None") %>%
  mutate(speed_score = unlist(speed_score),
         joined_id = unlist(joined_id),
         ramp_type = unlist(ramp_type)) %>%
  ggplot(aes(o_b_mod_coefs_speed, speed_score, colour = ramp_type)) +
  geom_point() +
  geom_smooth(method='lm', formula= y~x)

speed_corr_rp <- spatial_firing %>% 
  filter(cohort == 7) %>%
  select(speed_score, joined_id, ramp_type, o_b_mod_coefs_speed) %>%
  filter(ramp_type == "Ramp_position") %>%
  mutate(speed_score = unlist(speed_score),
         joined_id = unlist(joined_id),
         ramp_type = unlist(ramp_type)) %>%
  group_by(ramp_type)

speed_corr_lm_rp <- lm(speed_score ~ o_b_mod_coefs_speed, speed_corr_rp) 

summary(speed_corr_lm_rp)
  

speed_corr_ro <- spatial_firing %>% 
  filter(cohort == 7) %>%
  select(speed_score, joined_id, ramp_type, o_b_mod_coefs_speed) %>%
  filter(ramp_type == "Ramp_Other") %>%
  mutate(speed_score = unlist(speed_score),
         joined_id = unlist(joined_id),
         ramp_type = unlist(ramp_type)) %>%
  group_by(ramp_type)

speed_corr_lm_ro <- lm(speed_score ~ o_b_mod_coefs_speed, speed_corr_ro) 

summary(speed_corr_lm_ro)
  

speed_corr_s <- spatial_firing %>% 
  filter(cohort == 7) %>%
  select(speed_score, joined_id, ramp_type, o_b_mod_coefs_speed, final_model_o_b) %>%
  filter(ramp_type == "Ramp_Other",
         final_model_o_b == "S") %>%
  mutate(speed_score = unlist(speed_score),
         joined_id = unlist(joined_id),
         ramp_type = unlist(ramp_type)) %>%
  group_by(ramp_type)

speed_corr_lm_s <- lm(speed_score ~ o_b_mod_coefs_speed, speed_corr_s) 

summary(speed_corr_lm_s)
```

### ----------------------------------------------------------------------------------------- ###

Then, we want to see the proportion of spatial cells (grid, border etc) throughout types of ramp cells (++, -- etc)

1. extract neurons ramps and position encoding, remove cells not identified in VR and open field 
```{r}
position_data <- spatial_firing %>%
  filter(lm_group_b == "Positive" | lm_group_b == "Negative")  %>% 
  filter(cohort == 7) %>% 
  filter(final_model_o_b == "P" | final_model_o_b == "PS" | final_model_o_b == "PA"| final_model_o_b == "PSA")
  
```

2. extract proportion of cells that meet each criteria
```{r}
pospos <- subset(position_data, track_category == "pospos")
negneg <- subset(position_data, track_category == "negneg")
posneg <- subset(position_data, track_category == "posneg")
negpos <- subset(position_data, track_category == "negpos")
posnon <- subset(position_data, track_category == "posnon")
negnon <- subset(position_data, track_category == "negnon")

```

3. plot proportion of positive and negative ramps that are grid/non-grid

```{r}
pospos_grid <- nrow(subset(pospos, classifier == "G"))/nrow(pospos)*100
negneg_grid <- nrow(subset(negneg, classifier == "G"))/nrow(negneg)*100
posneg_grid <- nrow(subset(posneg, classifier == "G"))/nrow(posneg)*100
negpos_grid <- nrow(subset(negpos, classifier == "G"))/nrow(negpos)*100
negnon_grid <- nrow(subset(negnon, classifier == "G"))/nrow(negnon)*100
posnon_grid <- nrow(subset(posnon, classifier == "G"))/nrow(posnon)*100

pospos_border <- nrow(subset(pospos, classifier == "B"))/nrow(pospos)*100
negneg_border <- nrow(subset(negneg, classifier == "B"))/nrow(negneg)*100
posneg_border <- nrow(subset(posneg, classifier == "B"))/nrow(posneg)*100
negpos_border <- nrow(subset(negpos, classifier == "B"))/nrow(negpos)*100
negnon_border <- nrow(subset(negnon, classifier == "B"))/nrow(negnon)*100
posnon_border <- nrow(subset(posnon, classifier == "B"))/nrow(posnon)*100

pospos_speed <- nrow(subset(pospos, classifier == "S"))/nrow(pospos)*100
negneg_speed <- nrow(subset(negneg, classifier == "S"))/nrow(negneg)*100
posneg_speed <- nrow(subset(posneg, classifier == "S"))/nrow(posneg)*100
negpos_speed <- nrow(subset(negpos, classifier == "S"))/nrow(negpos)*100
negnon_speed <- nrow(subset(negnon, classifier == "S"))/nrow(negnon)*100
posnon_speed <- nrow(subset(posnon, classifier == "S"))/nrow(posnon)*100

pospos_hd <- nrow(subset(pospos, classifier == "HD"))/nrow(pospos)*100
negneg_hd <- nrow(subset(negneg, classifier == "HD"))/nrow(negneg)*100
posneg_hd <- nrow(subset(posneg, classifier == "HD"))/nrow(posneg)*100
negpos_hd <- nrow(subset(negpos, classifier == "HD"))/nrow(negpos)*100
negnon_hd <- nrow(subset(negnon, classifier == "HD"))/nrow(negnon)*100
posnon_hd <- nrow(subset(posnon, classifier == "HD"))/nrow(posnon)*100

pospos_spatial <- nrow(subset(pospos, classifier == "NG"))/nrow(pospos)*100
negneg_spatial <- nrow(subset(negneg, classifier == "NG"))/nrow(negneg)*100
posneg_spatial <- nrow(subset(posneg, classifier == "NG"))/nrow(posneg)*100
negpos_spatial <- nrow(subset(negpos, classifier == "NG"))/nrow(negpos)*100
negnon_spatial <- nrow(subset(negnon, classifier == "NG"))/nrow(negnon)*100
posnon_spatial <- nrow(subset(posnon, classifier == "NG"))/nrow(posnon)*100

pospos_non <- nrow(subset(pospos, classifier == "NS" | classifier == "NaN"))/nrow(pospos)*100
negneg_non <- nrow(subset(negneg, classifier == "NS" | classifier == "NaN"))/nrow(negneg)*100
posneg_non <- nrow(subset(posneg, classifier == "NS" | classifier == "NaN"))/nrow(posneg)*100
negpos_non <- nrow(subset(negpos, classifier == "NS" | classifier == "NaN"))/nrow(negpos)*100
negnon_non <- nrow(subset(negnon, classifier == "NS" | classifier == "NaN"))/nrow(negnon)*100
posnon_non <- nrow(subset(posnon, classifier == "NS" | classifier == "NaN"))/nrow(posnon)*100

```

4. Put into a tibble 
```{r}
proportions_mixed_ramps <- tibble(
  perc=c(pospos_grid, negneg_grid, posneg_grid, negpos_grid, negnon_grid, posnon_grid, 
         pospos_border, negneg_border, posneg_border, negpos_border, negnon_border, posnon_border,
         pospos_speed, negneg_speed, posneg_speed, negpos_speed, negnon_speed, posnon_speed,
         pospos_hd, negneg_hd, posneg_hd, negpos_hd, negnon_hd, posnon_hd,
         pospos_spatial, negneg_spatial, posneg_spatial, negpos_spatial, negnon_spatial, posnon_spatial,
         pospos_non, negneg_non, posneg_non, negpos_non, negnon_non, posnon_non), 
  ramp_id= c("pospos",  "negneg", "posneg", "negpos", "negnon", "posnon","pospos", "negneg", "posneg", "negpos", "negnon", "posnon","pospos", "negneg", "posneg", "negpos", "negnon", "posnon","pospos", "negneg", "posneg", "negpos", "negnon", "posnon","pospos", "negneg", "posneg", "negpos", "negnon", "posnon","pospos", "negneg", "posneg", "negpos", "negnon", "posnon"),
  ramp_type = c("Grid", "Grid", "Grid", "Grid", "Grid", "Grid", "Border", "Border", "Border", "Border", "Border", "Border", "Speed", "Speed", "Speed", "Speed", "Speed", "Speed", "Pure HD", "Pure HD", "Pure HD", "Pure HD", "Pure HD", "Pure HD", "Spatial", "Spatial", "Spatial", "Spatial", "Spatial", "Spatial", "Non-spatial", "Non-spatial", "Non-spatial", "Non-spatial", "Non-spatial", "Non-spatial"))
```

5. Plot bar graph of proportions
```{r}
ggplot(proportions_mixed_ramps, aes(x= ramp_id, y = perc, fill=factor(ramp_type))) +
  geom_bar(stat="identity",width = 0.9, alpha = .9) +
  labs(y = "Percent", x="") +
  scale_fill_manual(values=c("brown2", "darkturquoise","blueviolet","darkorange", "blue3", "brown2")) +
  #geom_text(aes(label = num), hjust = 1.5, vjust = 0.5, srt=90, size = 6, position = position_dodge(-0.5)) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 70)) +
  theme(axis.text.x=element_text(hjust=1)) +
  theme(axis.text.x = element_text(size=19),
        axis.text.y = element_text(size=20),
        legend.position="right", 
        legend.title = element_blank(),
        text = element_text(size=19), 
        legend.text=element_text(size=19), 
        axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)))
if (save_figures == 1) {
  ggsave(file = "plots/OF_Analysis_proportions_groups_allpositioncells.png", width = 7, height = 4)
}
```



### ----------------------------------------------------------------------------------------- ###

```{r}
border_cells <- nrow(subset(spatial_firing, classifier == "B"))
border <- subset(spatial_firing, classifier == "B")
border_ramps <- subset(border, track_category_numeric != 0 & lm_group_b == "Positive" | lm_group_b == "Negative")
border_p_ramps <- nrow(subset(border_ramps, final_model_o_b == "P" | final_model_o_b == "PS" | final_model_o_b == "PA"| final_model_o_b == "PSA"))

grid_cells <- nrow(subset(spatial_firing, classifier == "G"))
grid <- subset(spatial_firing, classifier == "G")
grid_ramps <- subset(grid, track_category_numeric != 0 & lm_group_b == "Positive" | lm_group_b == "Negative")
grid_p_ramps <- nrow(subset(grid_ramps, final_model_o_b == "P" | final_model_o_b == "PS" | final_model_o_b == "PA"| final_model_o_b == "PSA"))


hd_cells <- nrow(subset(spatial_firing, classifier == "HD"))
hd <- subset(spatial_firing, classifier == "HD")
hd_ramps <- subset(hd, track_category_numeric != 0 & lm_group_b == "Positive" | lm_group_b == "Negative")
hd_p_ramps <- nrow(subset(hd_ramps, final_model_o_b == "P" | final_model_o_b == "PS" | final_model_o_b == "PA"| final_model_o_b == "PSA"))

```

### ----------------------------------------------------------------------------------------- ###


Now we might want to see properties of spatial cells in the open field and VR. 

First, lets ensure all the cells spatial information score is over the shuffled cut off

1. Plot scatter plot of spatial threshold versus spatial information score
```{r}

ggplot() + 
    geom_point(data=spatial_firing,
               aes(x = as.numeric(unlist(spatial_threshold)), 
                   y = as.numeric(unlist(spatial_information_score)), 
                   color=factor(unlist(classifier2)))) +

    coord_cartesian(ylim = c(0,1), xlim = c(0,0.25)) +
    geom_abline(intercept = 0, slope = 1, colour = "grey", linetype = "dashed") +
    xlab("Shuffled data cutoff (bits/spikes)") +
    ylab("Spatial Information (bits/spikes)") +
    theme_classic() +
    scale_color_manual(values=c("brown2", "darkturquoise","blueviolet","darkorange", "blue3", "brown2")) +
    theme(axis.text.x = element_text(size=18),
          axis.text.y = element_text(size=18),
          legend.position="bottom", 
          legend.title = element_blank(),
          text = element_text(size=17), 
          legend.text=element_text(size=16), 
          axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0))) 

if (save_figures == 1) {
 ggsave(file = "plots/Spatialscore_vs_cutoff_groups.png", width = 4, height = 3.5) 
}
```



### ----------------------------------------------------------------------------------------- ###

Now we might want to see if speed scores in the open field are related to the standard coefficient for speed from the linear mixed effect model in VR. 

1. Plot scatter plot of speed score in open field versus speed coefficient in VR
```{r}

speed_data <- spatial_firing %>%
  filter(final_model_o_b == "S" )

ggplot() + 
    geom_point(data=speed_data,
               aes(x = as.numeric(unlist(speed_score)), 
                   y = as.numeric(unlist(o_b_mod_coefs_speed)), 
                   color=factor(unlist(classifier2)))) +

    coord_cartesian(ylim = c(-0.9,0.9)) +
    geom_abline(intercept = 0, slope = 1, colour = "grey", linetype = "dashed") +
    xlab("Speed score (of)") +
    ylab("std coef (speed) (vr)") +
    theme_classic() +
    scale_color_manual(values=c("brown2", "darkturquoise","blueviolet","darkorange", "blue3", "brown2")) +
    theme(axis.text.x = element_text(size=18),
          axis.text.y = element_text(size=18),
          legend.position="bottom", 
          legend.title = element_blank(),
          text = element_text(size=17), 
          legend.text=element_text(size=16), 
          axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0))) 

if (save_figures == 1) {
 ggsave(file = "plots/speedvr_vs_speedof_groups_speedcellsvr.png", width = 4, height = 3.5) 
}
```


```{r}
speed_data <- spatial_firing %>%
  filter(speed_cell == 1 )

ggplot() + 
    geom_point(data=speed_data,
               aes(x = as.numeric(unlist(speed_score)), 
                   y = as.numeric(unlist(o_b_mod_coefs_speed)), 
                   color=factor(unlist(classifier2)))) +

    coord_cartesian(ylim = c(-0.9,0.9)) +
    geom_abline(intercept = 0, slope = 1, colour = "grey", linetype = "dashed") +
    xlab("Speed score (of)") +
    ylab("std coef (speed) (vr)") +
    theme_classic() +
    scale_color_manual(values=c("brown2", "darkturquoise","blueviolet","darkorange", "blue3", "brown2")) +
    theme(axis.text.x = element_text(size=18),
          axis.text.y = element_text(size=18),
          legend.position="bottom", 
          legend.title = element_blank(),
          text = element_text(size=17), 
          legend.text=element_text(size=16), 
          axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0))) 

if (save_figures == 1) {
 ggsave(file = "plots/speedvr_vs_speedof_groups_speedcellsof.png",width = 4, height = 3.5) 
}
```



```{r}
position_data <- spatial_firing %>%
  filter(lm_group_b == "Positive" | lm_group_b == "Negative")  %>% 
  filter(final_model_o_b == "P" | final_model_o_b == "PS" | final_model_o_b == "PA"| final_model_o_b == "PSA")
  
```

```{r}
ggplot() + 
    geom_point(data=position_data,
               aes(x = as.numeric(unlist(asr_b_o_rewarded_fit_slope)), 
                   y = as.numeric(unlist(speed_score)), 
                   color=factor(unlist(classifier2)))) +
    coord_cartesian(ylim = c(-0.5,0.7), xlim = c(-0.5,0.5)) +
    geom_abline(intercept = 0, slope = 1, colour = "grey", linetype = "dashed") +
    ylab("Speed score (of)") +
    xlab("Outbound slope (Hz/cm)") +
    theme_classic() +
    scale_color_manual(values=c("brown2", "darkturquoise","blueviolet","darkorange", "blue3", "brown2")) +
    theme(axis.text.x = element_text(size=18),
          axis.text.y = element_text(size=18),
          legend.position="bottom", 
          legend.title = element_blank(),
          text = element_text(size=17), 
          legend.text=element_text(size=16), 
          axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0))) 

if (save_figures == 1) {
 ggsave(file = "plots/speedvr_vs_slope_groups_position.png", width = 4, height = 3.5) 
}
```


2. Plot scatter plot
```{r}

ggplot() + 
    geom_point(data=position_data,
               aes(x = as.numeric(unlist(asr_b_o_rewarded_fit_slope)), 
                   y = as.numeric(unlist(hd_score)), 
                   color=factor(unlist(classifier2)))) +
    coord_cartesian(ylim = c(0,1), xlim = c(-0.4,0.4)) +
    #geom_abline(intercept = 0, slope = 1, colour = "grey", linetype = "dashed") +
    xlab("Outbound slope (Hz/cm)") +
    ylab("HD score") +
    theme_classic() +
    scale_color_manual(values=c("brown2", "darkturquoise","blueviolet","darkorange", "blue3", "brown2")) +
    theme(axis.text.x = element_text(size=18),
          axis.text.y = element_text(size=18),
          legend.position="bottom", 
          legend.title = element_blank(),
          text = element_text(size=17), 
          legend.text=element_text(size=16), 
          axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0))) 

if (save_figures == 1) {
 ggsave(file = "plots/HDscore_vs_slope_allcells_position.png", width = 4, height = 3.5) 
}
```


2. Plot scatter plot
```{r}

ggplot() + 
    geom_point(data=position_data,
               aes(x = as.numeric(unlist(asr_b_o_rewarded_fit_slope)), 
                   y = as.numeric(unlist(border_score)), 
                   color=factor(unlist(classifier2)))) +
    coord_cartesian(ylim = c(-1,0.8), xlim = c(-0.4,0.4)) +
    #geom_abline(intercept = 0, slope = 1, colour = "grey", linetype = "dashed") +
    xlab("Outbound slope (Hz/cm)") +
    ylab("border score") +
    theme_classic() +
    scale_color_manual(values=c("brown2", "darkturquoise","blueviolet","darkorange", "blue3", "brown2")) +
    theme(axis.text.x = element_text(size=18),
          axis.text.y = element_text(size=18),
          legend.position="bottom", 
          legend.title = element_blank(),
          text = element_text(size=17), 
          legend.text=element_text(size=16), 
          axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0))) 

if (save_figures == 1) {
 ggsave(file = "plots/borderscore_vs_slope_allcells_position.png", width = 4, height = 3.5) 
}
```




2. Plot scatter plot
```{r}
ggplot() + 
    geom_point(data=position_data,
               aes(x = as.numeric(unlist(asr_b_o_rewarded_fit_slope)), 
                   y = as.numeric(unlist(grid_score)), 
                   color=factor(unlist(classifier2)))) +
    coord_cartesian(ylim = c(-0.8,0.8), xlim = c(-0.4,0.4)) +
    #geom_abline(intercept = 0, slope = 1, colour = "grey", linetype = "dashed") +
    xlab("Outbound slope (Hz/cm)") +
    ylab("Grid score") +
    theme_classic() +
    scale_color_manual(values=c("brown2", "darkturquoise","blueviolet","darkorange", "blue3", "brown2")) +
    theme(axis.text.x = element_text(size=18),
          axis.text.y = element_text(size=18),
          legend.position="bottom", 
          legend.title = element_blank(),
          text = element_text(size=17), 
          legend.text=element_text(size=16), 
          axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0))) 

if (save_figures == 1) {
 ggsave(file = "plots/gridscore_vs_slope_allcells_position.png", width = 4, height = 3.5) 
}
```




### ----------------------------------------------------------------------------------------- ###

## firing rate properties

### ----------------------------------------------------------------------------------------- ###


# Label neurons as either excitatory or inhibitory

1.
```{r}
label_cell_type <- function(mean_firing_rate_of){
  if (is.na(mean_firing_rate_of)) {
    return( "NaN" )  
  } else if( as.numeric(mean_firing_rate_of) > 10) {
    return( "Inhibitory" ) 
  } else if( as.numeric(mean_firing_rate_of) < 10) {
    return( "Excitatory" ) 
  } else {
    return("NaN")
  }
}

```


2. run on all cells
```{r}
spatial_firing <- spatial_firing %>%
  mutate(cell_type = map(mean_firing_rate_of, label_cell_type))

```



```{r}
position_data <- spatial_firing %>%
  filter(lm_group_b == "Positive" | lm_group_b == "Negative")  %>% 
  filter(final_model_o_b == "P" | final_model_o_b == "PS" | final_model_o_b == "PA"| final_model_o_b == "PSA")
  
```

2. Plot scatter plot
```{r}

ggplot() + 
    geom_jitter(data=position_data,
               aes(x = as.numeric(unlist(mean_firing_rate_of)), 
                   y = as.numeric(unlist(spike_width)), 
                   color=factor(unlist(classifier2)))) +
    #coord_cartesian(ylim = c(-1,0.8), xlim = c(-0.9,0.9)) +
    ylab("Spike half width (ms)") +
    xlab("Mean firing rate (Hz)") +
    geom_vline(xintercept = 10, color = "grey30", linetype = "longdash") +
    theme_classic() +
    scale_color_manual(values=c("brown2", "darkturquoise","blueviolet","darkorange", "blue3", "brown2")) +
    theme(axis.text.x = element_text(size=18),
          axis.text.y = element_text(size=18),
          legend.position="bottom", 
          legend.title = element_blank(),
          text = element_text(size=17), 
          legend.text=element_text(size=16), 
          axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0))) 

if (save_figures == 1) {
 ggsave(file = "plots/firing_properties_allpositioncells.png", width = 4, height = 3.5) 
}
```

```{r}
position_data$classifier2 <- as.character(position_data$classifier2)

ggplot() + 
    geom_jitter(data=subset(position_data, track_category != "None"),
               aes(x = as.numeric(unlist(mean_firing_rate_of)), 
                   y = as.numeric(unlist(spike_width)),
                   color=factor(unlist(classifier2)))) +
    ylab("Spike half width (ms)") +
    xlab("Mean firing rate (Hz)") +
    geom_vline(xintercept = 10, color = "grey30", linetype = "longdash") +
    facet_wrap(~ classifier2) +
    theme_classic() +
    scale_color_manual(values=c("brown2", "darkturquoise","blueviolet","darkorange", "blue3", "brown2")) +
    theme(axis.text.x = element_text(size=16),
          axis.text.y = element_text(size=16),
          legend.position="bottom", 
          legend.title = element_blank(),
          text = element_text(size=17), 
          legend.text=element_text(size=16), 
          axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)))

if (save_figures == 1) {
 ggsave(file = "plots/firing_properties_allcells_facet_groupbyclassifier.png", width = 7, height = 5) 
}
```


```{r}
data <- spatial_firing %>%
  dplyr::select(track_category, classifier, cell_type, Mouse, Day) %>%
  filter(cell_type != "NaN") %>%
  dplyr::group_by(Mouse,  classifier, cell_type, .drop=FALSE) %>%
  dplyr::summarise(n = n()) %>%
  dplyr::mutate(proportion = round(n / sum(n), 2)) %>%
  group_by(classifier,cell_type) %>%
  summarise(avg = mean(proportion), sd = std.error(proportion))

#data$lm_group_b <- as.character(data$lm_group_b)
```


`

2. Plot scatter plot
```{r}
ggplot() + 
    geom_jitter(data=spatial_firing,
               aes(x = as.numeric(unlist(mean_firing_rate_of)), 
                   y = as.numeric(unlist(spike_width)), 
                   color=factor(unlist(cell_type)))) +
    #coord_cartesian(ylim = c(-1,0.8), xlim = c(-0.9,0.9)) +
    ylab("Spike half width (ms)") +
    xlab("Mean firing rate (Hz)") +
    geom_vline(xintercept = 10, color = "grey30", linetype = "longdash") +
    theme_classic() +
    scale_color_manual(values=c("brown2", "darkturquoise", "darkorange","blueviolet", "blue3", "brown2")) +
    theme(axis.text.x = element_text(size=18),
          axis.text.y = element_text(size=18),
          legend.position="bottom", 
          legend.title = element_blank(),
          text = element_text(size=17), 
          legend.text=element_text(size=16), 
          axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0))) 

if (save_figures == 1) {
 ggsave(file = "plots/firing_properties_allcells_test.png", width = 4, height = 3.5) 
}
```


2. Plot scatter plot
```{r}
ggplot() + 
    geom_jitter(data=position_data,
               aes(x = as.numeric(unlist(mean_firing_rate_of)), 
                   y = as.numeric(unlist(spike_width)), 
                   color=factor(unlist(cell_type)))) +
    #coord_cartesian(ylim = c(-1,0.8), xlim = c(-0.9,0.9)) +
    ylab("Spike half width (ms)") +
    xlab("Mean firing rate (Hz)") +
    geom_vline(xintercept = 10, color = "grey30", linetype = "longdash") +
    theme_classic() +
    scale_color_manual(values=c("brown2", "darkturquoise", "darkorange","blueviolet", "blue3", "brown2")) +
    theme(axis.text.x = element_text(size=18),
          axis.text.y = element_text(size=18),
          legend.position="bottom", 
          legend.title = element_blank(),
          text = element_text(size=17), 
          legend.text=element_text(size=16), 
          axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0))) 

if (save_figures == 1) {
 ggsave(file = "plots/firing_properties_positioncells_test.png", width = 4, height = 3.5) 
}
```

```{r}
#proportion
df <- position_data %>%
  dplyr::select(lm_group_b, cell_type, Mouse, Day) %>%
  filter(cell_type != "NaN", lm_group_b == "Positive") %>%
  dplyr::group_by(cell_type, .drop=FALSE) %>%
  dplyr::summarise(n = n()) %>%
  dplyr::mutate(proportion = round(n / sum(n), 2))
  

```


2. Plot scatter plot
```{r}

ggplot() + 
    geom_jitter(data=subset(position_data, track_category == "pospos" | track_category == "negneg"),
               aes(x = as.numeric(unlist(mean_firing_rate_of)), 
                   y = as.numeric(unlist(spike_width)), 
                   color=factor(unlist(lm_group_b))), alpha=0.8) +
    geom_jitter(data=subset(position_data, track_category == "posneg" | track_category == "negpos"),
               aes(x = as.numeric(unlist(mean_firing_rate_of)), 
                   y = as.numeric(unlist(spike_width)), 
                   color=factor(unlist(lm_group_b))), shape=2, alpha=0.8) +
    geom_jitter(data=subset(position_data, track_category == "posnon" | track_category == "negnon"),
               aes(x = as.numeric(unlist(mean_firing_rate_of)), 
                   y = as.numeric(unlist(spike_width)), 
                   color=factor(unlist(lm_group_b))), shape=3, alpha=0.8) +  
    ylab("Spike half width (ms)") +
    xlab("Mean firing rate (Hz)") +
    geom_vline(xintercept = 10, color = "grey30", linetype = "longdash") +
    theme_classic() +
    scale_color_manual(values=c("violetred2", "chartreuse3", "grey", "grey6")) +
    theme(axis.text.x = element_text(size=18),
          axis.text.y = element_text(size=18),
          legend.position="bottom", 
          legend.title = element_blank(),
          text = element_text(size=17), 
          legend.text=element_text(size=16), 
          axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0))) 

if (save_figures == 1) {
 ggsave(file = "plots/firing_properties_allrampcells.png",width = 4, height = 3.5) 
}
```


2. Plot scatter plot
```{r}
position_data$track_category <- as.character(position_data$track_category)

ggplot() + 
    geom_jitter(data=subset(position_data, track_category != "None"),
               aes(x = as.numeric(unlist(mean_firing_rate_of)), 
                   y = as.numeric(unlist(spike_width)),
                   color=factor(unlist(lm_group_b)))) +
    ylab("Spike half width (ms)") +
    xlab("Mean firing rate (Hz)") +
    geom_vline(xintercept = 10, color = "grey30", linetype = "longdash") +
    facet_wrap(~ track_category) +
    theme_classic() +
    scale_color_manual(values=c("violetred2", "chartreuse3", "grey", "grey6")) +
    theme(axis.text.x = element_text(size=16),
          axis.text.y = element_text(size=16),
          legend.position="bottom", 
          legend.title = element_blank(),
          text = element_text(size=17), 
          legend.text=element_text(size=16), 
          axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)))

if (save_figures == 1) {
 ggsave(file = "plots/firing_properties_allrampcells_facet.png", width = 7, height = 5) 
}
```

```{r}
data <- position_data %>%
  dplyr::select(track_category, cell_type, Mouse) %>%
  filter(cell_type != "NaN", track_category != "None") %>%
  dplyr::group_by( Mouse, track_category, cell_type, .drop=FALSE) %>%
  dplyr::summarise(n = n()) %>%
  dplyr::mutate(proportion = round(n / sum(n), 2)) %>%
  group_by(track_category,cell_type) %>%
  summarise(avg = mean(proportion), sd = std.error(proportion))

#data$lm_group_b <- as.character(data$lm_group_b)
```




2. Plot scatter plot
```{r}
  ggplot(data=subset(spatial_firing,lm_group_b == "Unclassified"), aes(x = unlist(mean_firing_rate_of), fill=as.factor(unlist(classifier2)))) +
  geom_histogram(aes(y=..count..)) +
  coord_cartesian(xlim=c(0,80)) +
  scale_fill_manual(values=c("brown2", "darkturquoise","blueviolet","darkorange", "blue3", "brown2")) +
  scale_y_continuous(breaks = scales::pretty_breaks(n = 3)) +
  labs(y="Count", x="") +
  theme_classic() +
  theme(axis.text.x = element_text(size=13),
        axis.text.y = element_text(size=13),
        legend.position="bottom", 
        legend.title = element_blank(),
        text = element_text(size=13), 
        legend.text=element_text(size=13), 
        axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)))

if (save_figures == 1) {
 ggsave(file = "plots/FR_dist_nonrampcells.png", width = 2.5, height = 2) 
}
```


2. Plot scatter plot
```{r}
spatial_firing$track_category <- as.character(spatial_firing$track_category)

  ggplot(data=subset(spatial_firing,lm_group_b == "Unclassified" & lm_group_b_h == "Unclassified"), aes(x = unlist(mean_firing_rate), fill=as.factor(unlist(classifier2)))) +
  geom_histogram(aes(y=..count..)) +
  coord_cartesian(xlim=c(0,80)) +
  scale_fill_manual(values=c("brown2", "darkturquoise","blueviolet","darkorange", "blue3", "brown2")) +
  scale_y_continuous(breaks = scales::pretty_breaks(n = 3)) +
  labs(y="Count", x="") +
  xlab("Mean firing rate (Hz)") +
  facet_wrap(~ track_category) +
  theme_classic() +
  theme(axis.text.x = element_text(size=16),
        axis.text.y = element_text(size=16),
        legend.position="bottom", 
        legend.title = element_blank(),
        text = element_text(size=17), 
        legend.text=element_text(size=16), 
        axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)))

if (save_figures == 1) {
 ggsave(file = "plots/FRvr_dist_nonrampcells_facet.png",  width = 2.5, height = 2) 
}
```



2. Plot scatter plot
```{r}
position_data$track_category <- as.character(position_data$track_category)

  ggplot(data=subset(position_data,track_category != "None"), aes(x = unlist(mean_firing_rate), fill=as.factor(unlist(classifier2)))) +
  geom_histogram(aes(y=..count..)) +
  coord_cartesian(xlim=c(0,80)) +
  scale_fill_manual(values=c("brown2", "darkturquoise","blueviolet","darkorange", "blue3", "brown2")) +
  scale_y_continuous(breaks = scales::pretty_breaks(n = 3)) +
  labs(y="Count", x="") +
  xlab("Mean firing rate (Hz)") +
  facet_wrap(~ track_category) +
  theme_classic() +
  theme(axis.text.x = element_text(size=16),
        axis.text.y = element_text(size=16),
        legend.position="bottom", 
        legend.title = element_blank(),
        text = element_text(size=17), 
        legend.text=element_text(size=16), 
        axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)))

if (save_figures == 1) {
 ggsave(file = "plots/FRvr_dist_allrampcells_facet.png",  width = 7, height = 5) 
}
```



2. Plot scatter plot
```{r}

ggplot(data=subset(spatial_firing,lm_group_b == "Unclassified"), aes(x = unlist(mean_firing_rate), fill=as.factor(unlist(classifier2)))) +
  geom_histogram(aes(y=..count..)) +
  coord_cartesian(xlim=c(0,80)) +
  scale_fill_manual(values=c("brown2", "darkturquoise","blueviolet","darkorange", "blue3", "brown2")) +
  scale_y_continuous(breaks = scales::pretty_breaks(n = 3)) +
  labs(y="Count", x="") +
  theme_classic() +
  theme(axis.text.x = element_text(size=13),
        axis.text.y = element_text(size=13),
        legend.position="bottom", 
        legend.title = element_blank(),
        text = element_text(size=13), 
        legend.text=element_text(size=13), 
        axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)))

if (save_figures == 1) {
 ggsave(file = "plots/FRvr_dist_nonrampcells.png", width = 2.5, height = 2) 
}
```


```{r}

ggplot(data=position_data, aes(x = unlist(mean_firing_rate_of), fill=as.factor(unlist(classifier2)))) +
  geom_histogram(aes(y=..count..)) +
  coord_cartesian(xlim=c(0,80), ylim=c(0,100)) +
  scale_fill_manual(values=c("brown2", "darkturquoise","blueviolet","darkorange", "blue3", "brown2")) +
  scale_y_continuous(breaks = scales::pretty_breaks(n = 3)) +
  labs(y="Count", x="") +
  theme_classic() +
  theme(axis.text.x = element_text(size=13),
        axis.text.y = element_text(size=13),
        legend.position="bottom", 
        legend.title = element_blank(),
        text = element_text(size=13), 
        legend.text=element_text(size=13), 
        axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)))

if (save_figures == 1) {
 ggsave(file = "plots/FR_dist_allrampcells.png",width = 2.5, height = 2) 
}
```



```{r}

ggplot(data=subset(position_data,track_category != "None"), aes(x = unlist(mean_firing_rate_of), fill=as.factor(unlist(classifier2)))) +
  geom_histogram(aes(y=..count..)) +
  coord_cartesian(xlim=c(0,80)) +
  scale_fill_manual(values=c("brown2", "darkturquoise","blueviolet","darkorange", "blue3", "brown2")) +
  scale_y_continuous(breaks = scales::pretty_breaks(n = 3)) +
  labs(y="Count", x="") +
  xlab("Mean firing rate (Hz) (open field)") +
  facet_wrap(~ track_category) +
  theme_classic() +
  theme(axis.text.x = element_text(size=16),
        axis.text.y = element_text(size=16),
        legend.position="bottom", 
        legend.title = element_blank(),
        text = element_text(size=17), 
        legend.text=element_text(size=16), 
        axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)))
if (save_figures == 1) {
 ggsave(file = "plots/FR_dist_allrampcells_facet.png", width = 2.5, height = 2) 
}
```


```{r}

ggplot(data=position_data, aes(x = unlist(mean_firing_rate), fill=as.factor(unlist(classifier2)))) +
  geom_histogram(aes(y=..count..)) +
  coord_cartesian(xlim=c(0,80)) +
  scale_fill_manual(values=c("brown2", "darkturquoise","blueviolet","darkorange", "blue3", "brown2")) +
  scale_y_continuous(breaks = scales::pretty_breaks(n = 3)) +
  labs(y="Count", x="") +
  theme_classic() +
  theme(axis.text.x = element_text(size=13),
        axis.text.y = element_text(size=13),
        legend.position="bottom", 
        legend.title = element_blank(),
        text = element_text(size=13), 
        legend.text=element_text(size=13), 
        axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)))

if (save_figures == 1) {
 ggsave(file = "plots/FRvr_dist_allrampcells.png", width = 2.5, height = 2) 
}

```



```{r}

ggplot(data=subset(spatial_firing,lm_group_b == "Unclassified"), aes(x = (unlist(mean_firing_rate)-unlist(mean_firing_rate_of)), fill=as.factor(unlist(classifier2)))) +
  geom_histogram(aes(y=..count..)) +
  coord_cartesian(xlim = c(-50,50)) +
  scale_fill_manual(values=c("brown2", "darkturquoise","blueviolet","darkorange", "blue3", "brown2")) +
  scale_y_continuous(breaks = scales::pretty_breaks(n = 3)) +
  labs(y="Count", x="") +
  theme_classic() +
  theme(axis.text.x = element_text(size=13),
        axis.text.y = element_text(size=13),
        legend.position="bottom", 
        legend.title = element_blank(),
        text = element_text(size=13), 
        legend.text=element_text(size=13), 
        axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)))

if (save_figures == 1) {
 ggsave(file = "plots/FRdiff_dist_nonrampcells.png", width = 2.5, height = 2) 
}

```


```{r}

ggplot(data=position_data, aes(x = (unlist(mean_firing_rate)-unlist(mean_firing_rate_of)), fill=as.factor(unlist(classifier2)))) +
  geom_histogram(aes(y=..count..)) +
  coord_cartesian(xlim = c(-50,50)) +
  scale_fill_manual(values=c("brown2", "darkturquoise","blueviolet","darkorange", "blue3", "brown2")) +
  scale_y_continuous(breaks = scales::pretty_breaks(n = 3)) +
  labs(y="Count", x="") +
  theme_classic() +
  theme(axis.text.x = element_text(size=13),
        axis.text.y = element_text(size=13),
        legend.position="bottom", 
        legend.title = element_blank(),
        text = element_text(size=13), 
        legend.text=element_text(size=13), 
        axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)))

if (save_figures == 1) {
 ggsave(file = "plots/FRdiff_dist_allrampcells.png", width = 2.5, height = 2) 
}

```



# Does ramp score / slope correlate with mean firing rate?

We consider this question for neurons with negative ramp slopes before the reward zone as a reasonable proportion have mean firing rates > 10 Hz.
```{r}
ggplot() + 
    geom_jitter(data=subset(position_data, track_category != "None"),
               aes(x = as.numeric(unlist(mean_firing_rate_of)), 
                   y = as.numeric(unlist(asr_b_o_rewarded_fit_slope)),
                   color=factor(unlist(lm_group_b)))) +
    ylab("Slope") +
    xlab("Mean firing rate (Hz)") +
    geom_vline(xintercept = 10, color = "grey30", linetype = "longdash") +
    facet_wrap(~ track_category) +
    theme_classic() +
    scale_color_manual(values=c("violetred2", "chartreuse3", "grey", "grey6")) +
    theme(axis.text.x = element_text(size=16),
          axis.text.y = element_text(size=16),
          legend.position="bottom", 
          legend.title = element_blank(),
          text = element_text(size=17), 
          legend.text=element_text(size=16), 
          axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)))

if (save_figures == 1) {
 ggsave(file = "plots/firing_properties_allrampcells_facet.png", width = 7, height = 5) 
}
```







## Save output to manually find examples

2. take only columns we need for the rest of the analysis
```{r}
spatial_firing_save <- select(spatial_firing, session_id, cluster_id, unique_id, classifier2, hd_score,border_score,grid_score, speed_score,spatial_information_score, o_b_mod_coefs_accel, final_model_o_b, lm_group_b) %>%
  unnest(cols = c(unique_id, classifier2, hd_score,border_score,grid_score, speed_score, spatial_information_score, o_b_mod_coefs_accel, final_model_o_b, lm_group_b)) %>%
  as.tibble()

```

3. save to csv file _this is for matching to plots from python_
```{r}
write_csv2(spatial_firing_save, "all_results_openfield_matching2.csv")
```

