---
title: "Figure7"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



### --------------------------------------------------------------------------------------- ###

## Differences in the positional dependance of firing between rewarded trials, run through trials and trials where the animal "tries" 


trial types :
1. rewarded = animal recieves a reward
2. try = speed in the reward zone is within the 95% confidence interval of speed in the reward zone in
rewarded trials
3. run through = speed in the reward zone is outside the 95% confidence interval of speed in the reward zone in rewarded trials


### --------------------------------------------------------------------------------------- ###


## To address low trial numbers in run through and try catagories, first lets create a new dataset with only high trial numbers. 

First extract number of trials for each type
```{r}
trial_adder <- function(df) {
  df <-
  tibble(
    Rates = as.numeric(df[[1]]),
    Position = as.numeric(df[[3]]),
    Trials = as.numeric(df[[4]])
  )
  
  trials <- length(unique(df$Trials))
  return(trials)
}


spatial_firing <- spatial_firing %>%
  mutate(try_trials_number = map(spikes_in_time_try,trial_adder),
         run_trials_number = map(spikes_in_time_run,trial_adder),
         hit_trials_number = map(spikes_in_time_reward,trial_adder))

```


### --------------------------------------------------------------------------------------- ###

Then combine hit and miss trials together with an indicator of trial type (hit, try, run)

First, function that extracts data into a tibble, saves space in the function below

```{r}
extract_to_tibble <- function(df) {
  df <-
  tibble(
    Rates = as.numeric(Re(df[[1]])),
    Position = as.numeric(Re(df[[3]])),
    Trials = as.numeric(Re(df[[4]]))
  )
  return (df)
}

```

Function to join firing rates from different trial types and add indicator of the type of trial
```{r}

join_rates <- function(hit, run, try, session_id, cluster_id) {
  if (any(is.na(hit)) | any(is.na(run)) | any(is.na(try))) { 
    return(NA)
  }
  
  hit_df <- extract_to_tibble(hit)
  run_df <- extract_to_tibble(run)
  try_df <- extract_to_tibble(try)
 
  df <- tibble(Rates = c(hit_df$Rates, 
                         run_df$Rates,
                         try_df$Rates), 
               Reward_indicator = c(rep("Rewarded", times=nrow(hit_df)), 
                                    rep("Run", times=nrow(run_df)), 
                                    rep("Try", times=nrow(try_df))), 
               Position = c(hit_df$Position, 
                            run_df$Position, 
                            try_df$Position), 
               Trials = c(hit_df$Trials,
                          run_df$Trials,
                          try_df$Trials))

  return (df)
}

```

1. Generate firing rate tibble for each cell
```{r}
spatial_firing <- spatial_firing %>%
  mutate(both_asr_b_by_trial = pmap(list(spikes_in_time_reward, spikes_in_time_run, spikes_in_time_try, session_id, cluster_id), join_rates))

```


Function to run linear model that takes trial type (hit, try, run) into account and use the car package to extract slope significance
```{r}
compare_models_slope_lm <- function(df, run,try){
  tryCatch({
    if (any(is.na(run)) | any(is.na(try)) | any(is.na(df))) { 
      return(NA)
    }
    if (length(df) == 1 | nrow(df) < 6)
      return(NA)
    
    df <- df %>%
    filter(Position >= 30, Position <= 90)
    fit <- lme4::lmer(Rates ~ scale(Position) * Reward_indicator + (1+scale(Position) | Trials), data = df, na.action=na.omit)
    modelAnova <- car::Anova(fit)
    to_return <- modelAnova$"Pr(>Chisq)"[[3]]
    },
   error=function(e){cat("ERROR :",conditionMessage(e), "\n")})
}
```

2. Run linear model on all cells and extract pval
To test just use the first two rows
```{r}
spatial_firing <- spatial_firing %>%
  mutate(pval_slope = pmap(list(both_asr_b_by_trial, Avg_FiringRate_RunTrials, Avg_FiringRate_TryTrials), compare_models_slope_lm))
```

Now we can classify cells based on their significance in the above model

First make function to classify neurons
```{r}
mark_neurons_sig <- function(pval){
  tryCatch({
    if (is.na(pval)) {
      return(NA)
    }
    if (pval == "NULL") {
      return(NA)
    }
    if( pval < 0.01) {
      return( "Significant" )
    } else if( pval >= 0.01) {
      return( "Not-Significant" )
    } else {
      return("None")
    }
    },
   error=function(e){cat("ERROR :",conditionMessage(e), "\n")})

}
```

3. Make new column to identify whether cells are significant
```{r}
spatial_firing <- spatial_firing %>%
  mutate(reward_interaction_id = map(pval_slope, mark_neurons_sig))
```


### ----------------------------------------------------------------------------- ###

We also want to run a simple linear model for each trial type separately so we can extract the coefficients for each variable. 

First, add position to each of the firing rates individually (before we put them all in one tibble, here we make a seperate one for each and add it back into the dataframe)


Function to add position for individual trial type, returns NAs if those trials are not present 
```{r}
add_position <- function(df, session_id, cluster_id) {
  if(all(is.na(df))){
    #print(paste0("All NAs. Session: ", session_id, ". Cluster:", cluster_id))
    df <- tibble(Rates = rep(NA, times=200), 
                 Position = rep(NA, times=200))
    return(df)
    }
  df <- tibble(Rates = unlist(df), Position = rep(1:200)) 
  return(df)
}
```

1. Run this on all animals for try and run through trials (we already have coefficients for rewarded data from Figure 2)
```{r}
spatial_firing <- spatial_firing %>%
  mutate(asr_nb_try = pmap(list(Avg_FiringRate_TryTrials_nb, session_id, cluster_id), add_position),
         asr_nb_run = pmap(list(Avg_FiringRate_RunTrials_nb, session_id, cluster_id), add_position)
         )
```

2. run lm on all cells.
Removes any previously generated results (select), fits the data (mutate) and then adds model outputs as columns to spatial firing (unnest_wider).
```{r}
spatial_firing <- spatial_firing %>%
  select(-contains('asr_nb_try_fit_')) %>%
  select(-contains('asr_nb_run_fit_')) %>%
  mutate(asr_nb_try_fit = pmap(list(asr_nb_try, 30, 90), lm_helper)) %>%
  mutate(asr_nb_run_fit = pmap(list(asr_nb_run, 30, 90), lm_helper)) %>%
  unnest_wider(asr_nb_try_fit, names_sep = "_", names_repair = "universal") %>%
  unnest_wider(asr_nb_run_fit, names_sep = "_", names_repair = "universal")

```

Linear model results are stored in:
spatial_firing$asr_b_try_fit_pval
spatial_firing$asr_b_try_fit_slope
spatial_firing$asr_b_try_fit_r.squared




### ----------------------------------------------------------------------------- ###

## Calculate offset for run and try trials

We want to find out if within the position and speed groups - is their firing rate reset or continue across the reward region?

To do this, we will predict the firing rate on the homebound zone from the activity in the outbound. Then find the difference between the predicted and real data to determine if cells have reset or continued. 

First, normalise firing rates. 

1. make function to load rates and normalise
```{r}
normalise_rates <- function(df){
  df <- tibble(Rates = unlist(df), Position = rep(1:200))
  x <- scale(df$Rates, center=TRUE, scale=TRUE)
  return(x)
}

```

2. run on all cells
```{r}
spatial_firing <- spatial_firing %>%
  mutate(normalised_rates_try = map(Avg_FiringRate_TryTrials_nb, normalise_rates), 
         normalised_rates_hit = map(Avg_FiringRate_HitTrials_nb, normalise_rates),
         normalised_rates_run = map(Avg_FiringRate_RunTrials_nb, normalise_rates))
```

Then, predict firing rate in homebound region based on fit from real data in outbound region

Predict mean and confidence intervals for firing rate at the start of the homebound zone (track positions 110 to 115 cm) based on firing in the outbound zone (30 to 90 cm).

```{r}
predict_homebound <- function(df, fit_start = 30, fit_end = 90, predict_start = 110, predict_end = 115){
  # check for NAs
  if(all(is.na(df))) 
    return(NA)
  # Make track column
  df <- tibble(Rates = unlist(df), Position=rep(1:200))
  # fit
  model <- lm(Rates ~ Position, data = filter(df, Position >= fit_start, Position <= fit_end))
  # predict
  homebound_prediction_pos <- tibble(Position = rep(1:200))
  homebound_prediction <- predict(model, newdata = homebound_prediction_pos, interval = "prediction", level = 0.99) 
  as.tibble(homebound_prediction)
}


```
2. Run on all neurons
```{r}
spatial_firing <- spatial_firing %>%
  select(-contains('predict_params_try_')) %>%
  select(-contains('predict_params_run_')) %>%
  mutate(predict_params_try = map(normalised_rates_try, predict_homebound),
         predict_params_run = map(normalised_rates_run, predict_homebound)) %>%
  unnest_wider(predict_params_try, names_sep = "_", names_repair = "universal") %>%
  unnest_wider(predict_params_run, names_sep = "_", names_repair = "universal") 

spatial_firing <- spatial_firing %>%
  mutate(
         predict_diff_try = map2_dbl(normalised_rates_try, predict_params_try_fit, calc_predict_diff),
         predict_diff_hit = map2_dbl(normalised_rates_hit, predict_params_hit_fit, calc_predict_diff),
         predict_diff_run = map2_dbl(normalised_rates_run, predict_params_run_fit, calc_predict_diff))

```


### ----------------------------------------------------------------------------- ###


### ----------------------------------------------------------------------------------------- ###


Now we want to examine if there are differences in the reset activity between trial types (hit, try, run). To do this, we can plot population rate for rewarded and failed trials across whole track. 

Function to join firing rates from different trial types and add indicator of the type of trial

First combine hit and miss trials together with an indicator of trial type (hit, try, run)

Function to join firing rates from different trial types and add indicator of the type of trial
```{r}
join_average_rates <- function(hit, run, try, session_id, cluster_id) {
  if (any(is.na(hit)) | any(is.na(run)) | any(is.na(try))) { 
    return(
      df <- tibble(Rates = rep(NA, times=600), 
               Position = rep(NA, times=600),
               Reward_indicator = c(rep("Rewarded", times=200), rep("Run Through", times=200), rep("Try", times=200)))
    )
  }
  df <- tibble(Rates = c(unlist(hit), unlist(run), unlist(try)), Reward_indicator = c(rep("Rewarded", times=200), rep("Run Through", times=200), rep("Try", times=200)), Position = c(rep(-30:169), rep(-30:169), rep(-30:169)))
  return (df)
}
```

1. Generate firing rate tibble for each cell
```{r}
spatial_firing <- spatial_firing %>%
  mutate(avg_both_asr_b = pmap(list(normalised_rates_hit, normalised_rates_run, normalised_rates_try, session_id, cluster_id), join_average_rates))
  #mutate(avg_both_asr_b = pmap(list(Avg_FiringRate_HitTrials, Avg_FiringRate_RunTrials, Avg_FiringRate_TryTrials, session_id, cluster_id), join_average_rates))

```


Generic function to plot firing rate ± SEM as a function of position and colour coded according to trial outcome. The function expects to receive the unnested mean firing rates for all neurons that are to be plotted. Conditions for selection should be given before calling the function. Column names of the input data frame should be 'Rates', 'Position' and 'Reward_indicator'.
```{r}
mean_SEM_plots_by_Outcome <- function(df, x_start = -30, x_end = 170) {
  df$Rates <- as.double(df$Rates)

 df <- df %>%
   group_by(Position, Reward_indicator) %>%
   dplyr::summarise(mean_b = mean(Rates, na.rm = TRUE),
             se_b = std.error(Rates, na.rm = TRUE))
 
 ggplot(data=df) +
  annotate("rect", xmin=-30, xmax=0, ymin=-2,ymax=Inf, alpha=0.2, fill="Grey60") +
  annotate("rect", xmin=140, xmax=170, ymin=-2,ymax=Inf, alpha=0.2, fill="Grey60") +
  annotate("rect", xmin=60, xmax=80, ymin=-2,ymax=Inf, alpha=0.2, fill="Chartreuse4") +
  geom_ribbon(aes(x=Position, y=mean_b, ymin = mean_b - se_b, ymax = mean_b + se_b,
                  fill=factor(Reward_indicator)), alpha=0.1) +
  geom_line(aes(y=mean_b, x=Position, color=factor(Reward_indicator)), alpha=0.5) +
  scale_fill_manual(values=c("black", "red", "blue")) +
  scale_color_manual(values=c("black", "red", "blue")) +
  #labs(y = "Mean firing rate (Hz)", x = "Location (cm)") +
  labs(y = "Z-scored firing rate", x = "Location (cm)") +
  #xlim(-30, 170) +
  theme_classic() +
  scale_x_continuous(breaks=seq(-30,170,100), expand = c(0, 0)) +
  theme(axis.text.x = element_text(size=14),
        axis.text.y = element_text(size=14),
        legend.title = element_blank(),
        legend.position="none", 
        text = element_text(size=14),
        plot.margin = margin(21, 25, 5, 20))
}
```


_plots for all position encoding neurons (P, PA, PS, PSA)_

1. Split data based on cue independant/cue dependant (Figure 5) and encoding group (Figure 3) as we are only interested in position neurons here
```{r}
#position_neurons <- filter(spatial_firing, lm_group_b == "Positive" | lm_group_b == "Negative", final_model_o_b == "P" | final_model_o_b == "PS" | final_model_o_b == "PA"| final_model_o_b == "PSA")
```

```{r}
position_neurons <- filter(spatial_firing, lm_group_b == "Positive" | lm_group_b == "Negative", final_model_o_b == "PS" | final_model_o_b == "PA" | final_model_o_b == "PSA")
```


3. Subset data by group then average rates for plotting          **Negative Negative Reset**
```{r}
(NegNegR_plot <- position_neurons %>%
  filter(lm_group_p == "Negative",
         lm_group_p_h == "Negative") %>%
  select(avg_both_asr_b) %>%
  unnest(c(avg_both_asr_b)) %>%
  mean_SEM_plots_by_Outcome(-29,171))

if (save_figures==1) {
 ggsave(file = "plots/TrialOutcome_NegNeg_allpositionBUTP_NONBEACONED.png", width = 3.6, height = 2.9) 
}

```


5. Subset data by group then average rates for plotting          **Positive Positive Reset**
```{r}
(PosPosR_plot <- position_neurons %>%
  filter(lm_group_p == "Positive",
         lm_group_p_h == "Positive") %>%
  select(avg_both_asr_b) %>%
  unnest(c(avg_both_asr_b)) %>%
  mean_SEM_plots_by_Outcome(-30,170))

if (save_figures==1) {
  ggsave(file = "plots/TrialOutcome_PosPos_allpositionBUTP_NONBEACONED.png", width = 3.6, height = 2.9)
}

```

6. Subset data by group then average rates for plotting          **Positive Unclassified**
```{r}
(PosUC_plot <- position_neurons %>%
  filter(lm_group_p == "Positive",
         lm_group_p_h == "Negative") %>%
  select(avg_both_asr_b) %>%
  unnest(c(avg_both_asr_b)) %>%
  mean_SEM_plots_by_Outcome(-30,170))


if (save_figures==1) {
  ggsave(file = "plots/TrialOutcome_PosNeg_allpositionBUTP_NONBEACONED.png", width = 3.6, height = 2.9)
}

```

7. Subset data by group then average rates for plotting          **Positive Unclassified**
```{r}
(NegUC_plot <- position_neurons %>%
  filter(lm_group_p == "Negative",
         lm_group_p_h == "Positive") %>%
  select(avg_both_asr_b) %>%
  unnest(c(avg_both_asr_b)) %>%
  mean_SEM_plots_by_Outcome(-30,170))



if (save_figures==1) {
  ggsave(file = "plots/TrialOutcome_NegPos_allpositionBUTP_NONBEACONED.png", width = 3.6, height = 2.9)
}

```



_plots for pure position encoding neurons (P)_

Repeat above for just position neurons

1. Split data based on cue independant/cue dependant (Figure 5) and encoding group (Figure 3) as we are only interested in position neurons here
```{r}
position_neurons <- filter(spatial_firing, lm_group_b == "Positive" | lm_group_b == "Negative", final_model_o_b == "P")
```


3. Subset data by group then average rates for plotting          **Negative Negative**
```{r}
(NegNegR_plot <- position_neurons %>%
  filter(lm_group_p == "Negative",
         lm_group_p_h == "Negative") %>%
  select(avg_both_asr_b) %>%
  unnest(c(avg_both_asr_b)) %>%
  mean_SEM_plots_by_Outcome(-30,170))

if (save_figures==1) {
 ggsave(file = "plots/TrialOutcome_NegNeg_justposition_NONBEACONED.png", width = 3.6, height = 2.9) 
}

```

4. Subset data by group then average rates for plotting          **Positive Positive**
```{r}
(PosPosC_plot <- position_neurons %>%
  filter(lm_group_p == "Positive",
         lm_group_p_h == "Positive") %>%
  select(avg_both_asr_b) %>%
  unnest(c(avg_both_asr_b)) %>%
  mean_SEM_plots_by_Outcome(-30,170))


if (save_figures==1) {
  ggsave(file = "plots/TrialOutcome_PosPos_justposition_NONBEACONED.png", width = 3.6, height = 2.9)
}

```


6. Subset data by group then average rates for plotting          **Positive Negative**
```{r}
(PosUC_plot <- position_neurons %>%
  filter(lm_group_p == "Positive",
         lm_group_p_h == "Negative") %>%
  select(avg_both_asr_b) %>%
  unnest(c(avg_both_asr_b)) %>%
  mean_SEM_plots_by_Outcome(-30,170))


if (save_figures==1) {
  ggsave(file = "plots/TrialOutcome_PosNeg_justposition_NONBEACONED.png", width = 3.6, height = 2.9)
}

```

7. Subset data by group then average rates for plotting          **Negative Positive**
```{r}
(NegUC_plot <- position_neurons %>%
  filter(lm_group_p == "Negative",
         lm_group_p_h == "Positive") %>%
  select(avg_both_asr_b) %>%
  unnest(c(avg_both_asr_b)) %>%
  mean_SEM_plots_by_Outcome(-30,170))



if (save_figures==1) {
  ggsave(file = "plots/TrialOutcome_NegPos_justposition_NONBEACONED.png", width = 3.6, height = 2.9)
}

```




_plots for pure speed encoding neurons (S) with POSITIVE or NEGATIVE slopes_


Repeat above plots but for speed encoding neurons

1. Split data based on positive/negative slope (Figure2) and speed encoding group (Figure 3) as we are only interested in these neurons here
```{r}
speed_neurons <- filter(spatial_firing, final_model_o_b == "S" | final_model_o_b == "SA")
```

2.seperate based on whether they have a positive or negative relationship with speed
```{r}
speed_neurons_pospos <- filter(speed_neurons, lm_group_p == "Positive" & lm_group_p_h == "Positive")
speed_neurons_negneg <- filter(speed_neurons, lm_group_p == "Negative" & lm_group_p_h == "Negative")
speed_neurons_posneg <- filter(speed_neurons, lm_group_p == "Positive" & lm_group_p_h == "Negative")
speed_neurons_negpos <- filter(speed_neurons, lm_group_p == "Negative" & lm_group_p_h == "Positive")

```


3. Subset data by group then average rates for plotting          **Negative coefficient with speed**
```{r}
(Speed_Neg_plot <- speed_neurons_negneg %>%
  #filter(o_b_mod_coefs_speed < 0) %>%
  select(avg_both_asr_b) %>%
  unnest(c(avg_both_asr_b)) %>%
  mean_SEM_plots_by_Outcome(-30,170))

if (save_figures==1) {
  ggsave(file = "plots/TrialOutcome_NegNeg_SandSA_NONBEACONED.png", width = 3.6, height = 2.9)
}

```


3. Subset data by group then average rates for plotting          **Positive coefficient with speed**
```{r}
(Speed_Pos_plot <- speed_neurons_negpos %>%
  #filter(o_b_mod_coefs_speed > 0) %>%
  select(avg_both_asr_b) %>%
  unnest(c(avg_both_asr_b)) %>%
  mean_SEM_plots_by_Outcome(-30,170))

if (save_figures==1) {
  ggsave(file = "plots/TrialOutcome_NegPos_SandSA_NONBEACONED.png", width = 3.6, height = 2.9)
}
```


3. Subset data by group then average rates for plotting          **Positive coefficient with speed**
```{r}
(Speed_Pos_plot <- speed_neurons_pospos %>%
  filter(o_b_mod_coefs_speed < 0) %>%
  select(avg_both_asr_b) %>%
  unnest(c(avg_both_asr_b)) %>%
  mean_SEM_plots_by_Outcome(-30,170))

if (save_figures==1) {
  ggsave(file = "plots/TrialOutcome_PosPos_SandSA_NONBEACONED.png", width = 3.6, height = 2.9)
}
```



3. Subset data by group then average rates for plotting          **Positive coefficient with speed**
```{r}
(Speed_Pos_plot <- speed_neurons_posneg %>%
  #filter(o_b_mod_coefs_speed < 0) %>%
  select(avg_both_asr_b) %>%
  unnest(c(avg_both_asr_b)) %>%
  mean_SEM_plots_by_Outcome(-30,170))

if (save_figures==1) {
  ggsave(file = "plots/TrialOutcome_PosNeg_SandSA_NONBEACONED.png", width = 3.6, height = 2.9)
}
```


