---
title: "Figure7"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



### --------------------------------------------------------------------------------------- ###

## Differences in spatial firing between hit/rewarded and miss/unrewarded trials

We might want to see differences in the relationship between firing rate and position along the track between rewarded and non rewarded trials (i.e. hit and miss trials)


### --------------------------------------------------------------------------------------- ###

# 1st method : Trial by trial 
Here we combine hit and miss trials in a dataframe and mark by reward. Then run a linear mixed effect model which accounts for reward indicator and variation over trials

1. Write function to combine hit and miss trials in a dataframe and mark by reward 
```{r}
join_rates <- function(hit, miss, session_id, cluster_id) {
  if (ncol(miss) <= 2) { 
    print(paste0("No failed trials. Session: ", session_id, ". Cluster:", cluster_id))
    return(
      df <- tibble(Rates = NA, 
               Position = NA,
               Reward_indicator = NA,
               Trials = NA)
    )
  }
  df <- tibble(Rates = c(as.vector(hit), 
                         as.vector(miss)), 
               Position = c(rep(1:200, times = ncol(hit)), 
                            rep(1:200, times = ncol(miss))),
               Reward_indicator = c(rep(1, times=ncol(hit)*nrow(hit)), 
                                    rep(0, times=ncol(miss)*nrow(miss))),
               Trials = c(rep(1:ncol(hit), times = 200),
                         rep(1:ncol(miss), times = 200))
               )
  
  return (df)
}

```

2. run on all cells _just beaconed trials_
```{r}
spatial_firing <- spatial_firing %>%
  mutate(both_asr_b = pmap(list(Firing_rate_rewarded_b, Firing_rate_failed_b, session_id, cluster_id), join_rates))
```

3. Run lmer and extract slope significance / pvals using car Anova package.
_here we are looking to see if the slope is significantly different between rewarded and non rewarded trials_
```{r}
return_slope_interaction <- function(df, miss) {
 # Check for NAs
  if (any(is.na(df$Rates))) {
    return(NA)
  }
  if (ncol(miss) <= 2) { # check if there is 2 or less failed trials
    return(NA)
  }
  df <- df %>%
    subset(Position >= 30 & Position <= 90)
  fit <- lme4::lmer(Rates ~ Position * Reward_indicator + (Position||Reward_indicator) + (1|Trials), data = df, na.action = na.omit, REML = FALSE) 
  prtAnova <- car::Anova(fit, type="II")
  return(prtAnova$"Pr(>Chisq)"[3][1])
}

```

4. Run lm on all cells  & extract pvql for slope 
```{r}
spatial_firing <- spatial_firing %>%
  mutate(pval_slope_interaction = map2(both_asr_b, Firing_rate_failed_b, return_slope_interaction))

```

5. Run lmer and extract intercept significance / pvals using car Anova package.
_here we are looking to see if the intercept is significantly different between rewarded and non rewarded trials_
```{r}
return_intercept_interaction <- function(df, miss) {
 # Check for NAs
  if (any(is.na(df$Rates))) {
    return(NA)
  }
  if (ncol(miss) <= 2) { # check if there is 2 or less failed trials
    return(NA)
  }
  # Run lmer
  df <- df %>%
    subset(Position >= 30 & Position <= 90)
  fit <- lme4::lmer(Rates ~ Position * Reward_indicator + (Position||Reward_indicator)+ (1|Trials), data = df, na.action = na.omit, REML = FALSE) 
  prtAnova <- car::Anova(fit, type="II")
  return(prtAnova$"Pr(>Chisq)"[2][1])
}
```

6. Run lm on all cells & extract pvql for intercept 
```{r}
spatial_firing <- spatial_firing %>%
  mutate(pval_intercept_interaction = map2(both_asr_b, Firing_rate_failed_b, return_intercept_interaction))

```


### Classify cells based on significance
Now we want to see which cells have significantly different firing rates between rewarded/notrewarded trials. Taking into account slope and intercept significance 

1. make function
```{r}
mark_significance <- function(pval){
 # Check for NAs
  if (is.na(pval)) {
    return(NA)
  }

    if( pval < 0.05) {
    return( "Significant" )
  } else if( pval >= 0.05) {
    return( "Not-Significant" )
  } else {
    return("None")
  }
}

```

2. run on all neurons
```{r}
spatial_firing <- spatial_firing %>%
  mutate(sig_slope = map(pval_slope_interaction, mark_significance)) %>%
  mutate(sig_intercept = map(pval_intercept_interaction, mark_significance))

```


### -------------------------------------------------------------------------------------------- ###


## Plot distribution of slopes of significant and non signifncant ramps

1. First extract significant ramps
```{r}
ramps <- subset(spatial_firing, lm_group_b == "Negative" | lm_group_b == "Positive")
significant_ramps <- subset(ramps, sig_slope == "Significant" | sig_intercept == "Significant")

```

2. extract data for all ramp cells in a tibble

```{r}
lm_results <- tibble(Ramp_type = as.character(ramps$lm_group_b),
    Slopes = ramps$asr_b_o_rewarded_fit_slope, 
    r2 = ramps$asr_b_o_rewarded_fit_r.squared, 
    id = ramps$cluster_id)
```

3. do the same for significant ramps
```{r}
lm_results_ramps <- tibble(Ramp_type = as.character(significant_ramps$lm_group_b),
    Slopes = significant_ramps$asr_b_o_rewarded_fit_slope, 
    r2 = significant_ramps$asr_b_o_rewarded_fit_r.squared, 
    id = significant_ramps$cluster_id)
```

4. Plot distribution of slope and r.squared values for all data, marked by whether the cells are significantly influenced by reward
```{r}
lm_plot_end <- ggplot(data=lm_results_ramps, aes(x = Slopes, y = r2, color=factor(Ramp_type))) + 
    coord_cartesian(xlim = c(-0.6,0.6), ylim = c(0,1)) +
    geom_point() +
    geom_point(data=lm_results, aes(x = Slopes, y = r2), color='grey') +
    geom_point(data=lm_results_ramps, aes(x = Slopes, y = r2, color=factor(Ramp_type))) +
    xlab("\nslope") +
    ylab("R2") +
    theme_classic() +
    scale_color_manual(values=c("red", "red", "red")) +
    theme(axis.text.x = element_text(size=16),
          axis.text.y = element_text(size=16),
          legend.position="bottom", 
          legend.title = element_blank(),
          text = element_text(size=16), 
          legend.text=element_text(size=16), 
          axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0))) 
ggsave(file = "plots/lm_plot_rewards.png", width = 5, height = 6)
```


## Find proportions for above - significiant and non-significant 

1. extract outbound ramps
```{r}
# extracting diff models 
pos <-subset(spatial_firing, lm_group_b == "Positive")
neg <-subset(spatial_firing, lm_group_b == "Negative")
none <-subset(spatial_firing, lm_group_b == "Unclassified")

```

2. extract significant ramps
```{r}
sig_positive<- nrow(subset(pos, sig_slope == "Significant" |  sig_intercept == "Significant"))/nrow(pos)*100
notsig_positive <- nrow(subset(pos, sig_slope != "Significant" &  sig_intercept != "Significant" ))/nrow(pos)*100

sig_negative <- nrow(subset(neg, sig_slope == "Significant" |  sig_intercept == "Significant" ))/nrow(neg)*100
notsig_negative <- nrow(subset(neg, sig_slope != "Significant" &  sig_intercept != "Significant" ))/nrow(neg)*100
```

3. Put in tibble
```{r}
proportions_mixed_ramps <- tibble(perc=c(sig_negative, notsig_negative, sig_positive, notsig_positive), ramp_id= c("Sig", "Not", "Sig", "Not"),ramp_type = c("Negative", "Negative", "Positive", "Positive"))

```

4. Plot results
```{r}
ggplot(proportions_mixed_ramps, aes(x= ramp_type, y = perc, fill=factor(ramp_id))) +
  coord_cartesian(ylim = c(0,100), xlim=(NULL)) +
  geom_bar(stat="identity",width = 0.9, alpha = .4) +
  labs(y = "Percent") +
  scale_fill_manual(values=c("grey62", "red")) +
  theme_classic() +
  theme(axis.text.x = element_text(size=18),
        axis.text.y = element_text(size=18),
        legend.position="bottom", 
        legend.title = element_blank(),
        text = element_text(size=18), 
        legend.text=element_text(size=18), 
        axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0))) +
ggsave(file = "plots/LMStart_cellproportions_hitmiss.png", width = 3, height = 6)

```


## plot same as above, but with cells colored by their group (P, PA etc)
1. subset by encoding models 
```{r}
pos <-subset(spatial_firing, final_model_o_b == "P")
speed <-subset(spatial_firing, final_model_o_b == "S")
ccel<-subset(spatial_firing, final_model_o_b == "A")
posspeed <-subset(spatial_firing, final_model_o_b == "PS")
posaccel <-subset(spatial_firing, final_model_o_b == "PA")
speedaccel <-subset(spatial_firing, final_model_o_b == "SA")
posspeedaccel <-subset(spatial_firing, final_model_o_b == "PSA")

```

2. find proportions.
```{r}
sig_p <- nrow(subset(pos, sig_slope == "Significant" |  sig_intercept == "Significant" ))/nrow(pos)*100
sig_s <- nrow(subset(speed, sig_slope == "Significant" |  sig_intercept == "Significant" ))/nrow(speed)*100
sig_a <- nrow(subset(ccel, sig_slope == "Significant" |  sig_intercept == "Significant" ))/nrow(ccel)*100
sig_ps <- nrow(subset(posspeed,sig_slope == "Significant" |  sig_intercept == "Significant" ))/nrow(posspeed)*100
sig_pa <- nrow(subset(posaccel, sig_slope == "Significant" |  sig_intercept == "Significant" ))/nrow(posaccel)*100
sig_sa <- nrow(subset(speedaccel, sig_slope == "Significant" |  sig_intercept == "Significant" ))/nrow(speedaccel)*100
sig_psa <- nrow(subset(posspeedaccel,sig_slope == "Significant" |  sig_intercept == "Significant" ))/nrow(posspeedaccel)*100

notsig_p <- nrow(subset(pos, sig_slope != "Significant" &  sig_intercept != "Significant"))/nrow(pos)*100
notsig_s <- nrow(subset(speed, sig_slope != "Significant" &  sig_intercept != "Significant"))/nrow(speed)*100
notsig_a <- nrow(subset(ccel, sig_slope != "Significant" &  sig_intercept != "Significant"))/nrow(ccel)*100
notsig_ps <- nrow(subset(posspeed, sig_slope != "Significant" &  sig_intercept != "Significant"))/nrow(posspeed)*100
notsig_pa <- nrow(subset(posaccel, sig_slope != "Significant" &  sig_intercept != "Significant"))/nrow(posaccel)*100
notsig_sa <- nrow(subset(speedaccel,sig_slope != "Significant" &  sig_intercept != "Significant"))/nrow(speedaccel)*100
notsig_psa <- nrow(subset(posspeedaccel, sig_slope != "Significant" &  sig_intercept != "Significant"))/nrow(posspeedaccel)*100

```

3. put into tibble
```{r}
mixed_ramps <- tibble(perc=c(sig_p,notsig_p,sig_s, notsig_s, sig_a,notsig_a,  sig_ps, notsig_ps, sig_pa, notsig_pa, sig_sa, notsig_sa, sig_psa,notsig_psa), 
                      
                      ramp_id= c("P","P", 
                                 "S", "S", 
                                 "A", "A",
                                 "PS", "PS", 
                                 "PA", "PA", 
                                 "SA", "SA", 
                                 "PAS", "PAS"), 
                      ramp_type= c("Sig", "Not Sig","Sig", "Not Sig", "Sig", "Not Sig","Sig", "Not Sig","Sig", "Not Sig","Sig", "Not Sig", "Sig", "Not Sig" ))


```

4. Plot model results
```{r}
# plot data
level_order <- c("P", "S", "A", "PS", "PA", "SA", "PAS", "None")
ggplot(mixed_ramps, aes(x= factor(ramp_id, level = level_order), y = perc, fill=factor(ramp_type))) +
  geom_bar(stat="identity",width = 0.9, alpha = .7) +
  labs(y = "Percent of neurons identified using LM") +
  scale_fill_manual(values=c("grey","red")) +
  theme_classic() +
  theme(axis.text.x = element_text(size=12),
        axis.text.y = element_text(size=12),
        legend.position="bottom", 
        legend.title = element_blank(),
        text = element_text(size=12), 
        legend.text=element_text(size=12), 
        axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0))) +
ggsave(file = "plots/cell_proportions-lmmodel_signeurons.png", width = 3, height =5)


```


### -------------------------------------------------------------------------------------------- ###



We might also want to visualise the coefficients for the significant and non significant datasets as a histogram.

1. First seperate significant and non significant ramps
```{r}
ramps <- subset(spatial_firing, lm_group_b == "Negative" | lm_group_b == "Positive")
significant_ramps <- subset(ramps, sig_slope == "Significant" | sig_intercept == "Significant")
nonsignificant_ramps <- subset(ramps, sig_slope != "Significant" & sig_intercept != "Significant")

```

2. Then make stacked histogram of slope values for significant dataset
```{r}
ggplot(data=significant_ramps, aes(x= asr_b_o_rewarded_fit_slope, fill="red")) +
  coord_cartesian(xlim = c(-0.6,0.6)) +
  geom_histogram(aes(y=..count../sum(..count..)), binwidth=0.01) +
  ylab("Proportion") +
  theme_classic() +
  theme(axis.text.x = element_text(size=14),
        axis.text.y = element_text(size=14),
        legend.title = element_blank(),
        legend.position = "none",
        text = element_text(size=14),
        legend.text=element_text(size=14),
        axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0))) +
ggsave(file = "plots/Histogram_sig_slopes.png", width = 4.5, height = 2)

```

3. same as above but for not significant datasets
```{r}
ggplot(data=nonsignificant_ramps, aes(x= asr_b_o_rewarded_fit_slope, fill="grey")) +
  coord_cartesian(xlim = c(-0.6,0.6)) +
  geom_histogram(aes(y=..count../sum(..count..)), binwidth=0.01, fill="Grey") +
  ylab("Proportion") +
  theme_classic() +
  theme(axis.text.x = element_text(size=14),
        axis.text.y = element_text(size=14),
        legend.title = element_blank(),
        legend.position = "none",
        text = element_text(size=14),
        legend.text=element_text(size=14),
        axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)))
ggsave(file = "plots/Histogram_notsig_slopes.png", width = 4.5, height = 2)
```


4. Make stacked histogram of rsquared values for significant dataset
```{r}
ggplot(data=significant_ramps, aes(x= asr_b_o_rewarded_fit_r.squared, fill="red")) +
  coord_cartesian(xlim = c(0,1)) +
  geom_histogram(aes(y=..count../sum(..count..)), binwidth=0.01) +
  ylab("Proportion") +
  theme_classic() +
  theme(axis.text.x = element_text(size=14),
        axis.text.y = element_text(size=14),
        legend.title = element_blank(),
        legend.position = "none",
        text = element_text(size=14),
        legend.text=element_text(size=14),
        axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0))) +
ggsave(file = "plots/sig_r2_histogram.png", width = 4.5, height = 2)


```

4. Same as above but for shuffled datasets

```{r}
ggplot(data=nonsignificant_ramps, aes(x= asr_b_o_rewarded_fit_r.squared, fill="Grey")) +
  coord_cartesian(xlim = c(0,1)) +
  geom_histogram(aes(y=..count../sum(..count..)), binwidth=0.01, fill="Grey") +
  ylab("Proportion") +
  theme_classic() +
  theme(axis.text.x = element_text(size=14),
        axis.text.y = element_text(size=14),
        legend.title = element_blank(),
        legend.position = "none",
        text = element_text(size=14),
        legend.text=element_text(size=14),
        axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0))) +
ggsave(file = "plots/nonsig_r2_histogram.png", width = 4.5, height = 2)
```


### -------------------------------------------------------------------------------------------- ###

### -------------------------------------------------------------------------------------------- ###



## Method 2 : Run average rates and compare hit and miss via an anova 


1. Combine hit and miss trials
```{r}
join_rates <- function(hit, miss, session_id, cluster_id) {
  if (any(is.na(miss))) { 
    #print(paste0("No failed trials. Session: ", session_id, ". Cluster:", cluster_id))
    return(
      df <- tibble(Rates = NA, 
               Position = NA,
               Reward_indicator = NA)
    )
  }
  df <- tibble(Rates = c(unlist(hit[31:90]), unlist(miss[31:90])), Reward_indicator = c(rep(1, times=60), rep(0, times=60)), Position = c(rep(31:90), rep(31:90)))
  return (df)
}

spatial_firing <- spatial_firing %>%
  mutate(avg_both_asr_b = pmap(list(Rates_averaged_rewarded_b,Rates_averaged_failed_b, session_id, cluster_id), join_rates))

```

2. Run lm and compare models without reward to models with via anova
_extract both slope and intercept significance_
```{r}
compare_models_slope <- function(df, miss){
 # Check for NAs
  if (any(is.na(miss))) {
    return(NA)
  }
  fit <- lme4::lmer(Rates ~ Position * Reward_indicator + (Position||Reward_indicator), data = df, na.action = na.omit, REML = FALSE) # more complicated model
  prtAnova <- car::Anova(fit, type="II")
  return (prtAnova$"Pr(>Chisq)"[3][1])
}

compare_models_intercept <- function(df, miss){
   # Check for NAs
  if (any(is.na(miss))) {
    return(NA)
  }
  fit <- lme4::lmer(Rates ~ Position * Reward_indicator + (Position||Reward_indicator), data = df, na.action = na.omit, REML = FALSE) # more complicated model
  prtAnova <- car::Anova(fit, type="II")
  return (prtAnova$"Pr(>Chisq)"[2][1])
}
```

3. Run lm on all cells and extract anova pval
```{r}
spatial_firing <- spatial_firing %>%
  mutate(avg_pval_slope = map2(avg_both_asr_b, Rates_averaged_failed_b, compare_models_slope)) %>%
  mutate(avg_pval_intercept = map2(avg_both_asr_b, Rates_averaged_failed_b, compare_models_intercept))

```


### tag cells based on significance
1. make function
```{r}
mark_neurons_sig <- function(pval){
  if (any(is.na(pval))) {
    return(NA)
  }
  if( pval < 0.05) {
    return( "Significant" )
  } else if( pval >= 0.05) {
    return( "Not-Significant" )
  } else {
    return("None")
  }
}
```

2. run on all neurons
```{r}
spatial_firing <- spatial_firing %>%
  mutate(avg_sig_slope = map(avg_pval_slope, mark_neurons_sig)) %>%
  mutate(avg_sig_intercept = map(avg_pval_intercept, mark_neurons_sig))

```


### --------------------------------------------------------------------------------------------- ###

## Plot distribution of slopes of significant and non signifncant ramps

1. First extract significant ramps
```{r}
ramps <- subset(spatial_firing, lm_group_b == "Negative" | lm_group_b == "Positive")
significant_ramps <- subset(ramps, avg_sig_slope == "Significant" | sig_intercept == "Significant")

```

2. extract data for all ramp cells in a tibble

```{r}
lm_results <- tibble(Ramp_type = as.character(ramps$lm_group_b),
    Slopes = ramps$asr_b_o_rewarded_fit_slope, 
    r2 = ramps$asr_b_o_rewarded_fit_r.squared, 
    id = ramps$cluster_id)
```

3. do the same for significant ramps
```{r}
lm_results_ramps <- tibble(Ramp_type = as.character(significant_ramps$lm_group_b),
    Slopes = significant_ramps$asr_b_o_rewarded_fit_slope, 
    r2 = significant_ramps$asr_b_o_rewarded_fit_r.squared, 
    id = significant_ramps$cluster_id)
```

4. Plot distribution of slope and r.squared values for all data, marked by whether the cells are significantly influenced by reward
```{r}
lm_plot_end <- ggplot(data=lm_results_ramps, aes(x = Slopes, y = r2, color=factor(Ramp_type))) + 
    coord_cartesian(xlim = c(-0.6,0.6), ylim = c(0,1)) +
    geom_point() +
    geom_point(data=lm_results, aes(x = Slopes, y = r2), color='grey') +
    geom_point(data=lm_results_ramps, aes(x = Slopes, y = r2, color=factor(Ramp_type))) +
    xlab("\nslope") +
    ylab("R2") +
    theme_classic() +
    scale_color_manual(values=c("red", "red", "red")) +
    theme(axis.text.x = element_text(size=16),
          axis.text.y = element_text(size=16),
          legend.position="bottom", 
          legend.title = element_blank(),
          text = element_text(size=16), 
          legend.text=element_text(size=16), 
          axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0))) 
ggsave(file = "plots/lm_plot_rewards_m2.png", width = 5, height = 6)
```


## Find proportions for above - significiant and non-significant 

1. extract outbound ramps
```{r}
# extracting diff models 
pos <-subset(spatial_firing, lm_group_b == "Positive")
neg <-subset(spatial_firing, lm_group_b == "Negative")
none <-subset(spatial_firing, lm_group_b == "Unclassified")

```

2. extract significant ramps
```{r}
sig_positive<- nrow(subset(pos, avg_sig_slope == "Significant" |  avg_sig_intercept == "Significant"))/nrow(pos)*100
notsig_positive <- nrow(subset(pos, avg_sig_slope != "Significant" &  avg_sig_intercept != "Significant" ))/nrow(pos)*100

sig_negative <- nrow(subset(neg, avg_sig_slope == "Significant" |  avg_sig_intercept == "Significant" ))/nrow(neg)*100
notsig_negative <- nrow(subset(neg, avg_sig_slope != "Significant" &  avg_sig_intercept != "Significant" ))/nrow(neg)*100
```

3. Put in tibble
```{r}
proportions_mixed_ramps <- tibble(perc=c(sig_negative, notsig_negative, sig_positive, notsig_positive), ramp_id= c("Sig", "Not", "Sig", "Not"),ramp_type = c("Negative", "Negative", "Positive", "Positive"))

```

4. Plot results
```{r}
ggplot(proportions_mixed_ramps, aes(x= ramp_type, y = perc, fill=factor(ramp_id))) +
  coord_cartesian(ylim = c(0,100), xlim=(NULL)) +
  geom_bar(stat="identity",width = 0.9, alpha = .4) +
  labs(y = "Percent") +
  scale_fill_manual(values=c("grey62", "red")) +
  theme_classic() +
  theme(axis.text.x = element_text(size=18),
        axis.text.y = element_text(size=18),
        legend.position="bottom", 
        legend.title = element_blank(),
        text = element_text(size=18), 
        legend.text=element_text(size=18), 
        axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0))) +
ggsave(file = "plots/LMStart_cellproportions_hitmiss_m2.png", width = 3, height = 6)

```


## plot same as above, but with cells colored by their group (P, PA etc)
1. subset by encoding models 
```{r}
pos <-subset(spatial_firing, final_model_o_b == "P")
speed <-subset(spatial_firing, final_model_o_b == "S")
ccel<-subset(spatial_firing, final_model_o_b == "A")
posspeed <-subset(spatial_firing, final_model_o_b == "PS")
posaccel <-subset(spatial_firing, final_model_o_b == "PA")
speedaccel <-subset(spatial_firing, final_model_o_b == "SA")
posspeedaccel <-subset(spatial_firing, final_model_o_b == "PSA")

```

2. find proportions.
```{r}
sig_p <- nrow(subset(pos, avg_sig_slope == "Significant" |  avg_sig_intercept == "Significant" ))/nrow(pos)*100
sig_s <- nrow(subset(speed, avg_sig_slope == "Significant" |  avg_sig_intercept == "Significant" ))/nrow(speed)*100
sig_a <- nrow(subset(ccel, avg_sig_slope == "Significant" |  avg_sig_intercept == "Significant" ))/nrow(ccel)*100
sig_ps <- nrow(subset(posspeed,avg_sig_slope == "Significant" |  avg_sig_intercept == "Significant" ))/nrow(posspeed)*100
sig_pa <- nrow(subset(posaccel, avg_sig_slope == "Significant" |  avg_sig_intercept == "Significant" ))/nrow(posaccel)*100
sig_sa <- nrow(subset(speedaccel, avg_sig_slope == "Significant" |  avg_sig_intercept == "Significant" ))/nrow(speedaccel)*100
sig_psa <- nrow(subset(posspeedaccel,avg_sig_slope == "Significant" |  avg_sig_intercept == "Significant" ))/nrow(posspeedaccel)*100

notsig_p <- nrow(subset(pos, avg_sig_slope != "Significant" &  avg_sig_intercept != "Significant"))/nrow(pos)*100
notsig_s <- nrow(subset(speed, avg_sig_slope != "Significant" &  avg_sig_intercept != "Significant"))/nrow(speed)*100
notsig_a <- nrow(subset(ccel, avg_sig_slope != "Significant" &  avg_sig_intercept != "Significant"))/nrow(ccel)*100
notsig_ps <- nrow(subset(posspeed, avg_sig_slope != "Significant" &  avg_sig_intercept != "Significant"))/nrow(posspeed)*100
notsig_pa <- nrow(subset(posaccel, avg_sig_slope != "Significant" &  avg_sig_intercept != "Significant"))/nrow(posaccel)*100
notsig_sa <- nrow(subset(speedaccel,avg_sig_slope != "Significant" &  avg_sig_intercept != "Significant"))/nrow(speedaccel)*100
notsig_psa <- nrow(subset(posspeedaccel, avg_sig_slope != "Significant" &  avg_sig_intercept != "Significant"))/nrow(posspeedaccel)*100

```

3. put into tibble
```{r}
mixed_ramps <- tibble(perc=c(sig_p,notsig_p,sig_s, notsig_s, sig_a,notsig_a,  sig_ps, notsig_ps, sig_pa, notsig_pa, sig_sa, notsig_sa, sig_psa,notsig_psa), 
                      
                      ramp_id= c("P","P", 
                                 "S", "S", 
                                 "A", "A",
                                 "PS", "PS", 
                                 "PA", "PA", 
                                 "SA", "SA", 
                                 "PAS", "PAS"), 
                      ramp_type= c("Sig", "Not Sig","Sig", "Not Sig", "Sig", "Not Sig","Sig", "Not Sig","Sig", "Not Sig","Sig", "Not Sig", "Sig", "Not Sig" ))


```

4. Plot model results
```{r}
# plot data
level_order <- c("P", "S", "A", "PS", "PA", "SA", "PAS", "None")
ggplot(mixed_ramps, aes(x= factor(ramp_id, level = level_order), y = perc, fill=factor(ramp_type))) +
  geom_bar(stat="identity",width = 0.9, alpha = .7) +
  labs(y = "Percent of neurons identified using LM") +
  scale_fill_manual(values=c("grey","red")) +
  theme_classic() +
  theme(axis.text.x = element_text(size=12),
        axis.text.y = element_text(size=12),
        legend.position="bottom", 
        legend.title = element_blank(),
        text = element_text(size=12), 
        legend.text=element_text(size=12), 
        axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0))) +
ggsave(file = "plots/cell_proportions-lmmodel_signeurons_m2.png", width = 3, height =5)


```


### -------------------------------------------------------------------------------------------- ###



We might also want to visualise the coefficients for the significant and non significant datasets as a histogram.

1. First seperate significant and non significant ramps
```{r}
ramps <- subset(spatial_firing, lm_group_b == "Negative" | lm_group_b == "Positive")
significant_ramps <- subset(ramps, avg_sig_slope == "Significant" | avg_sig_intercept == "Significant")
nonsignificant_ramps <- subset(ramps, avg_sig_slope != "Significant" & avg_sig_intercept != "Significant")

```

2. Then make stacked histogram of slope values for significant dataset
```{r}
ggplot(data=significant_ramps, aes(x= asr_b_o_rewarded_fit_slope, fill="red")) +
  coord_cartesian(xlim = c(-0.6,0.6)) +
  geom_histogram(aes(y=..count../sum(..count..)), binwidth=0.01) +
  ylab("Proportion") +
  theme_classic() +
  theme(axis.text.x = element_text(size=14),
        axis.text.y = element_text(size=14),
        legend.title = element_blank(),
        legend.position = "none",
        text = element_text(size=14),
        legend.text=element_text(size=14),
        axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0))) +
ggsave(file = "plots/Histogram_sig_slopes_m2.png", width = 4.5, height = 2)

```

3. same as above but for not significant datasets
```{r}
ggplot(data=nonsignificant_ramps, aes(x= asr_b_o_rewarded_fit_slope, fill="grey")) +
  coord_cartesian(xlim = c(-0.6,0.6)) +
  geom_histogram(aes(y=..count../sum(..count..)), binwidth=0.01, fill="Grey") +
  ylab("Proportion") +
  theme_classic() +
  theme(axis.text.x = element_text(size=14),
        axis.text.y = element_text(size=14),
        legend.title = element_blank(),
        legend.position = "none",
        text = element_text(size=14),
        legend.text=element_text(size=14),
        axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)))
ggsave(file = "plots/Histogram_notsig_slopes_m2.png", width = 4.5, height = 2)
```


4. Make stacked histogram of rsquared values for significant dataset
```{r}
ggplot(data=significant_ramps, aes(x= asr_b_o_rewarded_fit_r.squared, fill="red")) +
  coord_cartesian(xlim = c(0,1)) +
  geom_histogram(aes(y=..count../sum(..count..)), binwidth=0.01) +
  ylab("Proportion") +
  theme_classic() +
  theme(axis.text.x = element_text(size=14),
        axis.text.y = element_text(size=14),
        legend.title = element_blank(),
        legend.position = "none",
        text = element_text(size=14),
        legend.text=element_text(size=14),
        axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0))) +
ggsave(file = "plots/sig_r2_histogram_m2.png", width = 4.5, height = 2)


```

4. Same as above but for shuffled datasets

```{r}
ggplot(data=nonsignificant_ramps, aes(x= asr_b_o_rewarded_fit_r.squared, fill="Grey")) +
  coord_cartesian(xlim = c(0,1)) +
  geom_histogram(aes(y=..count../sum(..count..)), binwidth=0.01, fill="Grey") +
  ylab("Proportion") +
  theme_classic() +
  theme(axis.text.x = element_text(size=14),
        axis.text.y = element_text(size=14),
        legend.title = element_blank(),
        legend.position = "none",
        text = element_text(size=14),
        legend.text=element_text(size=14),
        axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0))) +
ggsave(file = "plots/nonsig_r2_histogram_m2.png", width = 4.5, height = 2)
```



