---
title: "Figure7"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



### -------------------------------------------------------------------------------------------------------------------------------------------------- ###

## Differences in spatial firing between hit/rewarded and miss/unrewarded trials

We might want to see differences in the relationship between firing rate and position along the track between rewarded and non rewarded trials (i.e. hit and miss trials)


### --------------------------------------------------------------------------------------- ###

## Are neurons influenced by reward?

1. Combine hit and miss trials
```{r}
join_rates <- function(hit, miss) {
  df <- tibble(Rates = c(unlist(hit[31:90]), unlist(miss[31:90])), Reward_indicator = c(rep(1, times=60), rep(0, times=60)), Position = c(rep(31:90), rep(31:90)))
  return (df)
}
spatial_firing <- spatial_firing %>%
  mutate(both_asr_b = map2(Rates_averaged_rewarded_b,Rates_averaged_failed_b, join_rates))%>%
  mutate(both_asr_p = map2(Rates_averaged_rewarded_p,Rates_averaged_failed_p, join_rates))

```

2. Run lm and compare models without reward to models with via anova

```{r}

return_slope <- function(df) {
 # Check for NAs
  if (any(is.na(df$Rates))) {
    return(NA)
  }

  fit <- lme4::lmer(Rates ~ Position * Reward_indicator + (Position||Reward_indicator), data = df, na.action = na.omit) 
  prtAnova <- car::Anova(fit, type="II")
  return(prtAnova$"Pr(>Chisq)"[3][1])
}

return_intercept <- function(df) {
 # Check for NAs
  if (any(is.na(df$Rates))) {
    return(
          NA)
  }

  fit <- lme4::lmer(Rates ~ Position * Reward_indicator + (Position||Reward_indicator), data = df, na.action = na.omit) 
  prtAnova <- car::Anova(fit, type="II")
  return(prtAnova$"Pr(>Chisq)"[2][1])
}
```


3. Run lm on all cells and extract anova pval

```{r}
spatial_firing <- spatial_firing %>%
  mutate(pval_slope = map(both_asr_b, return_slope)) %>%
  mutate(pval_intercept = map(both_asr_b, return_intercept))

```

### tag cells based on significance
1. make function
```{r}
mark_significance <- function(pval){
 # Check for NAs
  if (is.na(pval)) {
    return(NA)
  }

    if( pval < 0.05) {
    return( "Significant" )
  } else if( pval >= 0.05) {
    return( "Not-Significant" )
  } else {
    return("None")
  }
}

```

2. run on all neurons
```{r}
spatial_firing <- spatial_firing %>%
  mutate(sig_slope = map(pval_slope, mark_significance)) %>%
  mutate(sig_intercept = map(pval_intercept, mark_significance))

```


### -------------------------------------------------------------------------------------------------------------------------------------------------- ###

5. Plot distribution of slopes with significant and non signifncant ramps


4. extract significant ramps
```{r}
ramps <- subset(spatial_firing, lm_group_b == "Negative" | lm_group_b == "Positive")
outbound_ramps_sig <- subset(ramps, sig_slope == "Significant"| sig_intercept == "Significant")

```


```{r}

lm_results <- tibble(Ramp_type = as.character(ramps$lm_result_o_rewarded),
    Slopes = ramps$asr_b_rewarded_slope_o, 
    r2 = ramps$asr_b_rewarded_r2_o, 
    id = ramps$cluster_id)

lm_results_ramps <- tibble(Ramp_type = as.character(outbound_ramps_rewards$lm_result_o_rewarded),
    Slopes = outbound_ramps_rewards$asr_b_rewarded_slope_o, 
    r2 = outbound_ramps_rewards$asr_b_rewarded_r2_o, 
    id = outbound_ramps_rewards$cluster_id)


lm_plot_end <- ggplot(data=lm_results_ramps, aes(x = Slopes, y = r2, color=factor(Ramp_type))) + 
    coord_cartesian(xlim = c(-1,1), ylim = c(0,1)) +
    geom_point() +
    geom_point(data=lm_results, aes(x = Slopes, y = r2), color='grey') +
    geom_point(data=lm_results_ramps, aes(x = Slopes, y = r2, color=factor(Ramp_type))) +
    xlab("\nslope") +
    ylab("R2") +
    theme_classic() +
    scale_color_manual(values=c("red", "red", "red")) +
    theme(axis.text.x = element_text(size=16),
          axis.text.y = element_text(size=16),
          legend.position="bottom", 
          legend.title = element_blank(),
          text = element_text(size=16), 
          legend.text=element_text(size=16), 
          axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0))) 

ggsave(file = "plots/b_lm_plot_start_rewards.png", width = 5, height = 6)
```


6. find proportions for above.

```{r}
# extracting diff models 
pos <-subset(spatial_firing, lm_result_o_rewarded == "Positive")
neg <-subset(spatial_firing, lm_result_o_rewarded == "Negative")
none <-subset(spatial_firing, lm_result_o_rewarded == "None")

sig_toreward <- nrow(subset(pos, pval < 0.001 ))/nrow(pos)*100
notsig_toreward <- nrow(subset(pos, pval >= 0.001 ))/nrow(pos)*100

sig_start <- nrow(subset(neg, pval < 0.001 ))/nrow(neg)*100
notsig_start <- nrow(subset(neg, pval >= 0.001 ))/nrow(neg)*100

proportions_mixed_ramps <- tibble(perc=c(sig_start, notsig_start, sig_toreward, notsig_toreward), ramp_id= c("Sig", "Not", "Sig", "Not"),ramp_type = c("Negative", "Negative", "Positive", "Positive"))

```

7. Plot results

```{r}
ggplot(proportions_mixed_ramps, aes(x= ramp_type, y = perc, fill=factor(ramp_id))) +
  coord_cartesian(ylim = c(0,100), xlim=(NULL)) +
  geom_bar(stat="identity",width = 0.9, alpha = .4) +
  labs(y = "Percent") +
  scale_fill_manual(values=c("grey62", "red")) +
  theme_classic() +
  theme(axis.text.x = element_text(size=18),
        axis.text.y = element_text(size=18),
        legend.position="bottom", 
        legend.title = element_blank(),
        text = element_text(size=18), 
        legend.text=element_text(size=18), 
        axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0))) +
ggsave(file = "plots/LMStart_cellproportions_hitmiss.png", width = 3, height = 6)

```


## plot same as above, but with cells colored by their group (P, PA etc)



```{r}

lm_results <- tibble(Ramp_type = as.character(ramps$lm_result_o_b),
    Slopes = ramps$asr_b_slope_o, 
    r2 = ramps$asr_b_r2_o, 
    id = ramps$cluster_id)

lm_results_ramps <- tibble(Ramp_type = as.character(outbound_ramps_rewards$final_model_o_b),
    Slopes = outbound_ramps_rewards$asr_b_slope_o, 
    r2 = outbound_ramps_rewards$asr_b_r2_o, 
    id = outbound_ramps_rewards$cluster_id)


lm_plot_end <- ggplot(data=lm_results_ramps, aes(x = Slopes, y = r2, color=factor(Ramp_type))) + 
    coord_cartesian(xlim = c(-0.65,0.65), ylim = c(0,1)) +
    geom_point() +
    geom_point(data=lm_results_ramps, aes(x = Slopes, y = r2, color=factor(Ramp_type))) +
    xlab("\nslope") +
    ylab("R2") +
    theme_classic() +
    scale_color_manual(values=c("deeppink1","indianred3", "steelblue3", "darkred", "orchid", "lightseagreen", "darkgreen", "grey32", "grey32")) +
    theme(axis.text.x = element_text(size=16),
          axis.text.y = element_text(size=16),
          legend.position="bottom", 
          legend.title = element_blank(),
          text = element_text(size=16), 
          legend.text=element_text(size=16), 
          axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0))) 

ggsave(file = "plots/b_lm_plot_start_rewards_groups.png", width = 5, height = 6)
```


6. find proportions for above.

```{r}
# extracting diff models 
pos <-subset(spatial_firing, final_model_o_b == "P")
speed <-subset(spatial_firing, final_model_o_b == "S")
ccel<-subset(spatial_firing, final_model_o_b == "A")
posspeed <-subset(spatial_firing, final_model_o_b == "PS")
posaccel <-subset(spatial_firing, final_model_o_b == "PA")
speedaccel <-subset(spatial_firing, final_model_o_b == "SA")
posspeedaccel <-subset(spatial_firing, final_model_o_b == "PSA")


sig_p <- nrow(subset(pos, pval < 0.01))/nrow(pos)*100
sig_s <- nrow(subset(speed, pval < 0.01))/nrow(speed)*100
sig_a <- nrow(subset(ccel, pval < 0.01))/nrow(ccel)*100
sig_ps <- nrow(subset(posspeed, pval < 0.01))/nrow(posspeed)*100
sig_pa <- nrow(subset(posaccel, pval < 0.01))/nrow(posaccel)*100
sig_sa <- nrow(subset(speedaccel, pval < 0.01))/nrow(speedaccel)*100
sig_psa <- nrow(subset(posspeedaccel, pval < 0.01))/nrow(posspeedaccel)*100

notsig_p <- nrow(subset(pos, pval > 0.01))/nrow(pos)*100
notsig_s <- nrow(subset(speed, pval > 0.01))/nrow(speed)*100
notsig_a <- nrow(subset(ccel, pval > 0.01))/nrow(ccel)*100
notsig_ps <- nrow(subset(posspeed, pval > 0.01))/nrow(posspeed)*100
notsig_pa <- nrow(subset(posaccel, pval > 0.01))/nrow(posaccel)*100
notsig_sa <- nrow(subset(speedaccel, pval > 0.01))/nrow(speedaccel)*100
notsig_psa <- nrow(subset(posspeedaccel, pval > 0.01))/nrow(posspeedaccel)*100

mixed_ramps <- tibble(perc=c(sig_p,notsig_p,sig_s, notsig_s, sig_a,notsig_a,  sig_ps, notsig_ps, sig_pa, notsig_pa, sig_sa, notsig_sa, sig_psa,notsig_psa), 
                      
                      ramp_id= c("P","P", 
                                 "S", "S", 
                                 "A", "A",
                                 "PS", "PS", 
                                 "PA", "PA", 
                                 "SA", "SA", 
                                 "PAS", "PAS"), 
                      ramp_type= c("Sig", "Not Sig","Sig", "Not Sig", "Sig", "Not Sig","Sig", "Not Sig","Sig", "Not Sig","Sig", "Not Sig", "Sig", "Not Sig" ))


```


7. Plot model results

```{r}
# plot data
level_order <- c("P", "S", "A", "PS", "PA", "SA", "PAS", "None")
ggplot(mixed_ramps, aes(x= factor(ramp_id, level = level_order), y = perc, fill=factor(ramp_type))) +
  geom_bar(stat="identity",width = 0.9, alpha = .7) +
  labs(y = "Percent of neurons identified using LM") +
  scale_fill_manual(values=c("grey","red")) +
  #scale_fill_brewer(palette= "RdYlBu") +
  theme_classic() +
  theme(axis.text.x = element_text(size=12),
        axis.text.y = element_text(size=12),
        legend.position="bottom", 
        legend.title = element_blank(),
        text = element_text(size=12), 
        legend.text=element_text(size=12), 
        axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0))) +
ggsave(file = "plots/cell_proportions-lmmodel_signeurons.png", width = 3, height =5)


```

