---
title: "Figure3_Analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

---
title: "Figure3_Analysis"
author: "Sarah Tennant"
date: "18/11/2020"
output: html_document
---



## Run mixed effect model which examines contribution of speed, acceleration and position on firing rate

1. Load functions to perform linear mixed effect model
```{r}
source("Functions_Outbound_LMER.R")

```

2. Run on all cells 
```{r}
spatial_firing <- spatial_firing  %>%
  mutate(o_pos_b = map(spikes_in_time, car_pos_b)) %>%
  mutate(o_speed_b = map(spikes_in_time, car_speed_b)) %>%
  mutate(o_accel_b = map(spikes_in_time, car_accel_b)) %>%
  mutate(o_pos_nb = map(spikes_in_time, car_pos_nb)) %>%
  mutate(o_speed_nb = map(spikes_in_time, car_speed_nb)) %>%
  mutate(o_accel_nb = map(spikes_in_time, car_accel_nb)) %>%
  mutate(o_pos_p = map(spikes_in_time, car_pos_p)) %>%
  mutate(o_speed_p = map(spikes_in_time, car_speed_p)) %>%
  mutate(o_accel_p = map(spikes_in_time, car_accel_p))
```


### ----------------------------------------------------------------------------------------- ###


## Select best model 

1. Write function to perform model selection
```{r}

model_comparison <- function(null_pos, null_speed, null_accel){
  pval <- 0.01
  if( is.na(null_pos) & is.na(null_accel)) {
    return( "None" )
  
  } else if( null_pos < pval & null_accel > pval & null_speed > pval) {
    return( "P" )
    
  } else if( null_pos > pval & null_accel > pval & null_speed < pval) {
    return( "S" ) 
    
  } else if( null_pos > pval & null_accel < pval & null_speed > pval) {
    return( "A" )
    
  } else if( null_pos < pval & null_accel > pval & null_speed < pval) {
    return("PS")
    
  } else if( null_pos < pval & null_accel < pval & null_speed > pval) {
    return( "PA" )
        
  } else if( null_pos > pval & null_accel < pval & null_speed < pval) {
    return("SA")

  } else if( null_pos < pval & null_accel < pval & null_speed < pval) {
    return("PSA")
    
  } else {
    return("None")
  }
}

```

2. Run on all cells in dataframe
```{r}
spatial_firing <- spatial_firing  %>%
    mutate(final_model_o_b  = pmap(list(o_pos_b, o_speed_b, o_accel_b), model_comparison)) %>%
    mutate(final_model_o_nb  = pmap(list(o_pos_nb, o_speed_nb, o_accel_nb), model_comparison))  %>%
    mutate(final_model_o_p  = pmap(list(o_pos_p, o_speed_p, o_accel_p), model_comparison))

```


### ----------------------------------------------------------------------------------------- ###


### Plot model selection results


1. Split data by linear model result
```{r}

# extracting diff models 
pos <-subset(spatial_firing, slope_criteria_pval == "Positive")
neg <-subset(spatial_firing, slope_criteria_pval == "Negative")
none <-subset(spatial_firing, slope_criteria_pval == "None")

```

2. Split data by mixed effect model result
```{r}

P_positive <- nrow(subset(pos, final_model_o_b == "P"))/nrow(pos)*100
P_negative <- nrow(subset(neg, final_model_o_b == "P"))/nrow(neg)*100
P_none <- nrow(subset(none,final_model_o_b == "P"))/nrow(none)*100

S_positive <- nrow(subset(pos,final_model_o_b == "S"))/nrow(pos)*100
S_negative <- nrow(subset(neg,final_model_o_b == "S"))/nrow(neg)*100
S_none <- nrow(subset(none,final_model_o_b == "S"))/nrow(none)*100

A_positive <- nrow(subset(pos,final_model_o_b == "A"))/nrow(pos)*100
A_negative <- nrow(subset(neg,final_model_o_b == "A"))/nrow(neg)*100
A_none <- nrow(subset(none,final_model_o_b == "A"))/nrow(none)*100

P_S_positive <- nrow(subset(pos,final_model_o_b == "PS"))/nrow(pos)*100
P_S_negative <- nrow(subset(neg,final_model_o_b == "PS"))/nrow(neg)*100
P_S_none <- nrow(subset(none,final_model_o_b == "PS"))/nrow(none)*100

P_A_positive <- nrow(subset(pos ,final_model_o_b == "PA"))/nrow(pos)*100
P_A_negative <- nrow(subset(neg ,final_model_o_b == "PA"))/nrow(neg)*100
P_A_none <- nrow(subset(none,final_model_o_b == "PA"))/nrow(none)*100

S_A_positive <- nrow(subset(pos ,final_model_o_b == "SA"))/nrow(pos)*100
S_A_negative <- nrow(subset(neg ,final_model_o_b == "SA"))/nrow(neg)*100
S_A_none <- nrow(subset(none,final_model_o_b == "SA"))/nrow(none)*100

P_S_A_positive <- nrow(subset(pos ,final_model_o_b == "PSA"))/nrow(pos)*100
P_S_A_negative <- nrow(subset(neg ,final_model_o_b == "PSA"))/nrow(neg)*100
P_S_A_none <- nrow(subset(none ,final_model_o_b == "PSA"))/nrow(none)*100

NONE_positive <- nrow(subset(pos ,final_model_o_b == "None"))/nrow(pos)*100
NONE_negative <- nrow(subset(neg ,final_model_o_b == "None"))/nrow(neg)*100
NONE_none <- nrow(subset(none ,final_model_o_b == "None"))/nrow(none)*100


```

3. Put data into tibble
```{r}


mixed_ramps <- tibble(perc=c(P_positive,P_negative,P_none,S_positive, S_negative, S_none, A_positive,A_negative,A_none,  P_S_positive, P_S_negative,P_S_none, P_A_positive, P_A_negative, P_A_none, S_A_positive, S_A_negative, S_A_none,P_S_A_positive, P_S_A_negative, P_S_A_none, NONE_positive,NONE_negative, NONE_none), 
                      
                      ramp_id= c("P","P","P", 
                                 "S", "S", "S", 
                                 "A", "A", "A",
                                 "PS", "PS", "PS", 
                                 "PA", "PA", "PA", 
                                 "SA", "SA", "SA", 
                                 "PAS", "PAS","PAS",
                                 "Null","Null", "Null"), 
                      ramp_type= c("Positive", "Negative", "Unclassified","Positive", "Negative", "Unclassified", "Positive", "Negative", "Unclassified","Positive", "Negative" ,"Unclassified","Positive", "Negative","Unclassified","Positive", "Negative","Unclassified", "Positive", "Negative", "Unclassified", "Positive", "Negative", "Unclassified" ))

```

4. Plot model results
```{r}
# plot data
level_order <- c("P", "S", "A", "PS", "PA","SA", "PAS", "Null")
ggplot(mixed_ramps, aes(x= factor(ramp_type), y = perc, fill=factor(ramp_id, level = level_order))) +
  geom_bar(stat="identity",width = 0.9, alpha = .7) +
  labs(y = "Percent of neurons") +
  #scale_fill_manual(values=c("deeppink1","indianred3", "steelblue3", "darkred", "orchid", "lightseagreen", "darkgreen", "grey32")) +
  scale_fill_manual(values=c("firebrick1","gold", "dodgerblue2", "darkorange", "darkorchid1", "chartreuse3", "darkslategray", "grey78")) +
  #scale_fill_brewer(palette= "RdYlBu") +
  theme_classic() +
  theme(axis.text.x = element_text(size=12),
        axis.text.y = element_text(size=12),
        legend.position="bottom", 
        legend.title = element_blank(),
        text = element_text(size=12), 
        legend.text=element_text(size=12), 
        axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0))) +
ggsave(file = "plots/cell_proportions-lmmodel_beaconed2.png", width = 4, height = 4.5)


```


