---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



### ------------------------------------------------------------------------------------ ###

## Analysis of average speed vs location 

### ------------------------------------------------------------------------------------ ###

## plot average speed vs location 

1. Write function to add position to speed
```{r}
add_position_withoutcome <- function(hit, try, run) {
  df <- tibble(Speed = c(unlist(hit), unlist(try), unlist(run)), 
               Position = rep(1:200, times=3), 
               Indicator = c(rep("Hit", times=200), rep("Try", times=200), rep("Run", times=200)))
  return(df)
}
```

2. Run on dataframe : Average across trial types

input columns: 
Speed_mean_rewarded = speed on rewarded beaconed trials
Speed_mean_try =  speed ontry beaconed trials
Speed_mean_runthru = speed on run through trials
```{r}
spatial_firing <- spatial_firing %>%
  mutate(Speed_avg = pmap(list(Speed_mean_rewarded, Speed_mean_try, Speed_mean_runthru), add_position_withoutcome))
```

Then average over selected neurons 

Function to plot data mean and SD of the population data based on the classification, as per Figure 2, on beaconed and non-beaconed trials.

```{r}
  # The function to use at each step is `mean`.
  # The window size is 5
  rolling_mean <- rollify(mean, window = 2)

```

```{r}
mean_speed_plots <- function(df, x_start = 30, x_end = 90){
 rolling_mean <- rollify(mean, window = 2)
 
 df <- df %>%
   select(Speed_avg) %>%
   unnest((Speed_avg)) %>%
   mutate(Speed = rolling_mean(Speed)/2)

 df <- df %>%
   group_by(Position, Indicator) %>%
   summarise(mean_b = mean(Speed, na.rm = TRUE),
             se_b = std.error(Speed, na.rm = TRUE))
 ggplot(data=df) +
  annotate("rect", xmin=0, xmax=30, ymin=0,ymax=Inf, alpha=0.2, fill="Grey60") +
  annotate("rect", xmin=170, xmax=200, ymin=0,ymax=Inf, alpha=0.2, fill="Grey60") +
  annotate("rect", xmin=90, xmax=110, ymin=0,ymax=Inf, alpha=0.2, fill="Chartreuse4") +
  geom_ribbon(aes(x=Position, 
                  y=mean_b, ymin = mean_b - se_b, ymax = mean_b + se_b, 
                  fill=as.factor(Indicator)), alpha=0.1) +
   geom_line(aes(y=mean_b, 
                 x=Position, 
                 color=as.factor(Indicator)), alpha=0.5, n= 100, span=0.2) +
   scale_fill_manual(values=c("black", "blue", "red")) +
   scale_color_manual(values=c("black", "blue", "red")) +
   theme_classic() +
   labs(y = "Mean speed (cm/s)", x = "Position") +
   xlim(x_start, x_end) +
   #ylim(10,170) +
   theme(axis.text.x = element_text(size=12),
        axis.text.y = element_text(size=12),
        legend.title = element_blank(),
        text = element_text(size=12))
 
}
```


Subset data by group then average rates for plotting          
```{r}
(Pos_speed_plot <- mean_speed_plots(spatial_firing,  0, 200))
ggsave(file = "plots/PI_speed.png", width = 4.5, height = 2.5)
```



### ------------------------------------------------------------------------------------ ###

## calculate a histogram of speed in the reward zone

Here we want to see the distribution of speed in the reward zone in the trial types (hit, run, try)


```{r}
df <- spatial_firing %>%
  select(rewardzone_speed_hit) %>%
  unnest(rewardzone_speed_hit) 

```

```{r}
ggplot(data=df, aes(x = as.numeric(rewardzone_speed_hit))) +
  coord_cartesian(xlim=c(0,100)) +
  geom_histogram(aes(y=..density..),binwidth = 2, alpha=0.5, fill="black") +
  #scale_y_continuous(breaks = scales::pretty_breaks(n = 4)) +
  labs(y="Density", x="") +
  theme_classic() +
  theme(axis.text.x = element_text(size=16),
        axis.text.y = element_text(size=16),
        text = element_text(size=16), 
        axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)))
ggsave(file = "plots/speedhist_hit.png", width = 4, height = 2.5)

```

4. Plot histogram for rewarded trials

```{r}
df <- spatial_firing %>%
  select(rewardzone_speed_try) %>%
  unnest(rewardzone_speed_try) 

```

```{r}
  ggplot(data=df, aes(x = as.numeric(rewardzone_speed_try))) +
    coord_cartesian(xlim=c(0,100)) +
    geom_histogram(aes(y=..density..),binwidth = 2, alpha=0.5, fill="blue") +
    #scale_y_continuous(breaks = scales::pretty_breaks(n = 4)) +
    labs(y="Density", x="") +
    theme_classic() +
    theme(axis.text.x = element_text(size=16),
          axis.text.y = element_text(size=16),
          text = element_text(size=16), 
          axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)))
ggsave(file = "plots/speedhist_try.png", width = 4, height = 2.5)

```


```{r}
df <- spatial_firing %>%
  select(rewardzone_speed_run) %>%
  unnest(rewardzone_speed_run) 

```

```{r}
  ggplot(data=df, aes(x = as.numeric(rewardzone_speed_run))) +
    coord_cartesian(xlim=c(0,100)) +
    geom_histogram(aes(y=..density..),binwidth = 2, alpha=0.5, fill="red") +
    #scale_y_continuous(breaks = scales::pretty_breaks(n = 4)) +
    labs(y="Density", x="") +
    theme_classic() +
    theme(axis.text.x = element_text(size=16),
          axis.text.y = element_text(size=16),
          text = element_text(size=16), 
          axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)))
ggsave(file = "plots/speedhist_run.png", width = 4, height = 2.5)

```


