---
title: "Figure4_Analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


### --------------------------------------------------------------------------------- ###


## Runs analysis that compares cued trials (beaconed) to uncued (non-beaconed + probe)

_note : focuses on activity in outbound region_


### --------------------------------------------------------------------------------- ###


First, we are interested to see what proportion of neurons has the following pattern ramp activity :

1. ramp in both cued and uncued (PI)
2. ramp in just cued (cue)
3. ramp in just uncued (onlypi)

To classify cells into these catagories above, we will use the criteria established in Figure 2 using linear modelling. 

1. make function to classify cells based on activity in beaconed / non-beaconed&probe trials 
```{r}
mark_neurons <- function(beac, nb){
  if (is.na(beac) | is.na(nb) ) {
    return( "None" )
  } else if( beac == "Positive" & nb == "Positive") {
    return( "Positive-PI" )
  } else if( beac == "Negative" & nb == "Negative") {
    return( "Negative-PI" )
  } else if( beac == "Positive" & nb == "Unclassified") {
    return( "Positive-cue" )
  } else if( beac == "Negative" & nb == "Unclassified") {
    return( "Negative-cue" )
  } else if( beac == "Unclassified" & nb == "Positive") {
    return( "Positive-onlypi" )
  } else if( beac == "Unclassified" & nb == "Negative") {
    return( "Negative-onlypi" )
    } else {
    return("None")
  }
}

```

2. run on all neurons
```{r}
spatial_firing <- spatial_firing %>%
  mutate(cue_group = map2(lm_group, lm_group_nb, mark_neurons))

```



Now I want to visualise the proportion of cells that fit these above criteria. I'm going to do this by plotting a pie chart. 

1. subset neurons by group _just looking at cue dependant or independant for now_
```{r}
ramps <-subset(spatial_firing, lm_group == "Positive" | lm_group == "Negative")

# positive homebound slopes
pi <-nrow(subset(ramps, cue_group == "Positive-PI" | cue_group == "Negative-PI"))/nrow(ramps)*100
cue <-nrow(subset(ramps, cue_group == "Positive-cue" | cue_group == "Negative-cue"))/nrow(ramps)*100
pionly <-nrow(subset(spatial_firing, cue_group == "Positive-onlypi" | cue_group == "Negative-onlypi"))/nrow(spatial_firing)*100
none <-nrow(subset(spatial_firing, cue_group == "None" | cue_group == "None"))/nrow(spatial_firing)*100

# positive homebound slopes
pi_num <-nrow(subset(spatial_firing, cue_group == "Positive-PI" | cue_group == "Negative-PI"))
cue_num <-nrow(subset(spatial_firing, cue_group == "Positive-cue" | cue_group == "Negative-cue"))
pionly_num <-nrow(subset(spatial_firing, cue_group == "Positive-onlypi" | cue_group == "Negative-onlypi"))
none_num <-nrow(subset(spatial_firing, cue_group == "None" | cue_group == "None"))

```

2. Put results into tibble
```{r}

proportions_mixed_ramps <- tibble(perc=c(pi, cue, pionly, none), num=c(pi_num, cue_num, pionly_num, none_num), ramp_id= c("Cue-independant", "Cue-dependant", "Path-Integration-only", "None"),ramp_type = c("Cue-independant", "Cue-dependant", "Path-Integration-only", "None"))

```

3. Plot a pie chart of results, 
_note : pie segments represent the proportions with real values in text_
```{r}

# Create Data
data <- data.frame(
  group=LETTERS[1:4],
  value=c(pi,cue,pionly,none)
)

# Compute the position of labels
data <- proportions_mixed_ramps %>% 
  arrange(desc(ramp_id)) %>%
  mutate(prop = perc) %>%
  mutate(ypos = cumsum(prop)- 0.5*prop )

# Basic piechart
ggplot(data, aes(x="", y=prop, fill=ramp_id)) +
  geom_bar(stat="identity", width=1, color="white") +
  coord_polar("y", start=0) +
  theme_void() + 
  #theme(legend.position="none") +
  
  geom_text(aes(y = ypos, label = num), color = "white", size=3) +
  scale_fill_brewer(palette="Set1")

ggsave(file = "plots/CueComparison_proportions.png", width = 4, height = 4)

```


4. Also just a quick look at the numbers - how many positive and negative of each (cue/PI)
```{r}
ramps <- subset(spatial_firing, lm_group == "Positive" | lm_group == "Negative")

pi_neg <-nrow(subset(ramps, cue_group == "Negative-PI"))/nrow(ramps)*100
cue_neg <-nrow(subset(ramps, cue_group == "Negative-cue"))/nrow(ramps)*100
pi_pos <-nrow(subset(ramps, cue_group == "Positive-PI"))/nrow(ramps)*100
cue_pos <-nrow(subset(ramps, cue_group == "Positive-cue"))/nrow(ramps)*100

```



### -------------------------------------------------------------------------------------------------------- ###

We also want to see the movement of neurons from cue to uncued trials, do this using a Sankey plot


1. Subset based on cue dependancy
```{r}
# positive homebound slopes
pi <-subset(spatial_firing, cue_group == "Positive-PI" | cue_group == "Negative-PI")
cue <-subset(spatial_firing, cue_group == "Positive-cue" | cue_group == "Negative-cue")
pionly <-subset(spatial_firing, cue_group == "Positive-onlypi" | cue_group == "Negative-onlypi")

pi_neg <-subset(spatial_firing, cue_group == "Negative-PI")
cue_neg <-subset(spatial_firing,  cue_group == "Negative-cue")
pi_pos <-subset(spatial_firing, cue_group == "Positive-PI" )
cue_pos <-subset(spatial_firing, cue_group == "Positive-cue" )

```

2. Subset based on non-beaconed activity
```{r}

pi_positive <-subset(spatial_firing, lm_group == "Positive")
pi_negative <-subset(spatial_firing, lm_group == "Negative")
pi_none <-subset(spatial_firing, lm_group == "Unclassified")

pi_positive_pos <-nrow(subset(pi_positive, lm_group_nb == "Positive"))
pi_positive_neg <-nrow(subset(pi_positive, lm_group_nb == "Negative"))
pi_positive_none <-nrow(subset(pi_positive, lm_group_nb == "Unclassified"))
pi_negative_pos <-nrow(subset(pi_negative, lm_group_nb == "Positive"))
pi_negative_neg <-nrow(subset(pi_negative, lm_group_nb == "Negative"))
pi_negative_none <-nrow(subset(pi_negative, lm_group_nb == "Unclassified"))
pi_none_pos <-nrow(subset(pi_none, lm_group_nb == "Positive"))
pi_none_neg <-nrow(subset(pi_none, lm_group_nb == "Negative"))
pi_none_none <-nrow(subset(pi_none, lm_group_nb == "Unclassified"))

```

3. Put data into a tibble with labels
```{r}

data_long <- tibble(value=c(pi_positive_pos, pi_positive_neg, pi_positive_none, pi_negative_pos,pi_negative_neg, pi_negative_none, pi_none_pos, pi_none_neg, pi_none_none), 
                    
                      source= c("Positive","Positive", "Positive", "Negative", "Negative", "Negative", "Unclassified","Unclassified", "Unclassified"),
                     target= c(" Positive"," Negative", " Unclassified"," Positive"," Negative", " Unclassified"," Positive"," Negative", " Unclassified"))


data_long <- data_long %>% 
  filter(value > 0)                           
                    
```

3. Create a node data frame: it lists every entities involved in the flow
```{r}
nodes <- data.frame(name=c(as.character(data_long$source), as.character(data_long$target)) %>% unique())
 
```

4. Reformat dataframe to provide connection using id, not using the real name like in the links dataframe
```{r}
data_long$IDsource=match(data_long$source, nodes$name)-1 
data_long$IDtarget=match(data_long$target, nodes$name)-1
```

5. Plot sankey diagram
```{r}
# prepare colour scale
ColourScal ='d3.scaleOrdinal() .range(["#FDE725FF","#B4DE2CFF","#6DCD59FF","#35B779FF","#1F9E89FF","#26828EFF","#31688EFF","#3E4A89FF","#482878FF","#440154FF"])'

# Make the Network
sankeyNetwork(Links = data_long, Nodes = nodes,
              Source = "IDsource", Target = "IDtarget",
              Value = "value", NodeID = "name", LinkGroup='source',
              sinksRight=FALSE, colourScale=ColourScal,
              nodeWidth=40, fontSize=0, nodePadding=30)
#ggsave(file = "plots/model_movement.png", width = 24, height = 18)

```





### ------------------------------------------------------------------------------------- ###

_same as above but just for position based cells_

```{r}
ramp_neurons <-subset(spatial_firing, lm_group == "Positive" | lm_group == "Negative")
```

```{r}
unclassified_neurons <-subset(spatial_firing, lm_group == "Unclassified")
nb_neurons <-subset(unclassified_neurons, lm_group_nb == "Positive" | lm_group_nb == "Negative")

```

2. subset based on position
```{r}
position_neurons <-subset(nb_neurons, final_model_o_b == "P" | final_model_o_b == "PS" | final_model_o_b == "PA" | final_model_o_b == "PSA")
```


2. Subset based on non-beaconed activity
```{r}

pi_positive <-subset(position_neurons, lm_group == "Positive")
pi_negative <-subset(position_neurons, lm_group == "Negative")
pi_none <-subset(position_neurons, lm_group == "Unclassified")

pi_positive_pos <-nrow(subset(pi_positive, lm_group_nb == "Positive"))
pi_positive_neg <-nrow(subset(pi_positive, lm_group_nb == "Negative"))
pi_positive_none <-nrow(subset(pi_positive, lm_group_nb == "Unclassified"))
pi_negative_pos <-nrow(subset(pi_negative, lm_group_nb == "Positive"))
pi_negative_neg <-nrow(subset(pi_negative, lm_group_nb == "Negative"))
pi_negative_none <-nrow(subset(pi_negative, lm_group_nb == "Unclassified"))
pi_none_pos <-nrow(subset(pi_none, lm_group_nb == "Positive"))
pi_none_neg <-nrow(subset(pi_none, lm_group_nb == "Negative"))
pi_none_none <-nrow(subset(pi_none, lm_group_nb == "Unclassified"))

```

3. Put data into a tibble with labels
```{r}

data_long <- tibble(value=c(pi_positive_pos, pi_positive_neg, pi_positive_none, pi_negative_pos,pi_negative_neg, pi_negative_none, pi_none_pos, pi_none_neg, pi_none_none), 
                    
                      source= c("Positive","Positive", "Positive", "Negative", "Negative", "Negative", "None","None", "None"),
                     target= c(" Positive"," Negative", " None"," Positive"," Negative", " None"," Positive"," Negative", " None"))


data_long <- data_long %>% 
  filter(value > 0)                           
                    
```

3. Create a node data frame: it lists every entities involved in the flow
```{r}
nodes <- data.frame(name=c(as.character(data_long$source), as.character(data_long$target)) %>% unique())
 
```

4. Reformat dataframe to provide connection using id, not using the real name like in the links dataframe
```{r}
data_long$IDsource=match(data_long$source, nodes$name)-1 
data_long$IDtarget=match(data_long$target, nodes$name)-1
```

5. Plot sankey diagram
```{r}
# prepare colour scale
ColourScal ='d3.scaleOrdinal() .range(["#FDE725FF","#B4DE2CFF","#6DCD59FF","#35B779FF","#1F9E89FF","#26828EFF","#31688EFF","#3E4A89FF","#482878FF","#440154FF"])'

# Make the Network
sankeyNetwork(Links = data_long, Nodes = nodes,
              Source = "IDsource", Target = "IDtarget",
              Value = "value", NodeID = "name", LinkGroup='source',
              sinksRight=FALSE, colourScale=ColourScal,
              nodeWidth=40, fontSize=0, nodePadding=30)
#ggsave(file = "plots/model_movement.png", width = 24, height = 18)

```




## calculate for the neurons included in the above sankey, what proportion of neurons are in each lmer group
```{r}
pi_positive <-subset(position_neurons, lm_group == "Positive")
pi_negative <-subset(position_neurons, lm_group == "Negative")

pi_unclassified <-subset(position_neurons, lm_group == "Negative")
pi_unclassified <-subset(pi_unclassified, lm_group_nb == "Negative" | lm_group_nb == "Positive")

```

```{r}
# calculate propotion of groups
P_positive <- nrow(subset(pi_positive, final_model_o_b == "P"))/nrow(pi_positive)*100
PA_positive <- nrow(subset(pi_positive, final_model_o_b == "PA"))/nrow(pi_positive)*100
PS_positive <- nrow(subset(pi_positive, final_model_o_b == "PS"))/nrow(pi_positive)*100
PSA_positive <- nrow(subset(pi_positive, final_model_o_b == "PSA"))/nrow(pi_positive)*100

# calculate propotion of groups
P_negative <- nrow(subset(pi_negative, final_model_o_b == "P"))/nrow(pi_negative)*100
PA_negative <- nrow(subset(pi_negative, final_model_o_b == "PA"))/nrow(pi_negative)*100
PS_negative <- nrow(subset(pi_negative, final_model_o_b == "PS"))/nrow(pi_negative)*100
PSA_negative <- nrow(subset(pi_negative, final_model_o_b == "PSA"))/nrow(pi_negative)*100

```
2. put data in tibble
```{r}

data_groups <- tibble(perc=c(P_positive,PA_positive,PS_positive,PSA_positive, P_negative, PA_negative, PS_negative, PSA_negative),ramp_id= c("P","PA","PS", "PSA", "P","PA","PS", "PSA"), ramp_type = c("Positive", "Positive", "Positive", "Positive", "Negative", "Negative", "Negative", "Negative"))

```

3. plot data
```{r}
# plot data
level_order <- c("P", "PS", "PA", "PSA")
ggplot(data_groups, aes(x = factor(ramp_type), y = perc, fill=factor(ramp_id, level = level_order))) +
  geom_bar(stat="identity",width = 0.9, alpha = .7) +
  labs(y = "Percent of neurons") +
  scale_fill_manual(values=c("firebrick1","darkorange", "darkorchid1","darkslategray")) +
  theme_classic() +
  theme(axis.text.x = element_text(size=14),
        axis.text.y = element_text(size=14),
        legend.position="bottom", 
        legend.title = element_blank(),
        text = element_text(size=14), 
        legend.text=element_text(size=14), 
        axis.title.y = element_text(margin = margin(t = 0, r = 15, b = 0, l = 0))) +
ggsave(file = "plots/cell_proportions-AllNeurons.png", width = 4, height = 4.5)

```

### --------------------------------------------------------------------------------------- ###

Now we want to visualise the average firing rate for each of the groups (cue dependant & cue independant / positive & negative)

1. Extract all data into tibble 
```{r}
df <- tibble(Position = rep(1:200, times=nrow(position_neurons)), Rates = unlist(position_neurons$Rates_averaged_rewarded_b),Rates_nb = unlist(position_neurons$Rates_averaged_rewarded_nb), lm_group_beaconed = rep(position_neurons$lm_group, each=200), lm_group_nonbeaconed = rep(position_neurons$lm_group_nb, each=200), group = rep(as.character(position_neurons$cue_group), each=200))

```

2. Subset data by group then average rates for plotting          **Negative Cue**
```{r}
df_neg_cue <- df %>%
  subset(lm_group_beaconed == "Negative" & lm_group_nonbeaconed == "Unclassified") %>%
  group_by(Position) %>%
  subset(Position >= 30 & Position <= 90) %>%
  summarise(mean_b = mean(Rates,na.rm = TRUE), mean_nb = mean(Rates_nb,na.rm = TRUE), sd_b = std.error(Rates, na.rm = TRUE), sd_nb = std.error(Rates_nb, na.rm = TRUE)) %>%
  mutate(Position = rep(0:60)) # rewriting position for plot because its easier than doing it ggplot
  
```

5. Plot average beaconed and non-beaconed rates                 **Negative Cue**
```{r}
ggplot(data=df_neg_cue) +
  geom_ribbon(aes(x=Position, y=mean_b, ymin = mean_b - sd_b, ymax = mean_b + sd_b), fill = "grey70", alpha=0.2) +
  geom_ribbon(aes(x=Position, y=mean_nb, ymin = mean_nb - sd_nb, ymax = mean_nb + sd_nb), fill = "Red2", alpha=0.05) +
  geom_line(aes(y=mean_b, x=Position), color = "Grey32") +
  #stat_smooth(aes(y=mean_b, x=Position), color = "Grey32", n = 60, span = 0.5) +
  #stat_smooth(aes(y=mean_nb, x=Position), color = "Red2", n = 60, span = 0.5) +
  geom_line(aes(y=mean_nb, x=Position), color = "Red2") +
  theme_classic() +
  labs(y = "Mean firing rate (Hz)", x = "Position") +
  theme(axis.text.x = element_text(size=12),
        axis.text.y = element_text(size=12),
        legend.title = element_blank(),
        text = element_text(size=12))
ggsave(file = "plots/AverageRates_PositionCells_NegCue.png", width = 3.5, height = 2.5)

```


4. Subset data by group then average rates for plotting          **Positive Cue**

```{r}
df_pos_cue <- df %>%
  subset(lm_group_beaconed == "Positive" & lm_group_nonbeaconed == "Unclassified") %>%
  group_by(Position) %>%
  subset(Position >= 30 & Position <= 90) %>%
  summarise(mean_b = mean(Rates,na.rm = TRUE), mean_nb = mean(Rates_nb,na.rm = TRUE), sd_b = std.error(Rates, na.rm = TRUE), sd_nb = std.error(Rates_nb, na.rm = TRUE)) %>%
  mutate(Position = rep(0:60))
  
```

5. Plot average rates                                            **Positive Cue**
```{r}
ggplot(data=df_pos_cue) +
  geom_ribbon(aes(x=Position, y=mean_b, ymin = mean_b - sd_b, ymax = mean_b + sd_b), fill = "grey70", alpha=0.2) +
  geom_ribbon(aes(x=Position, y=mean_nb, ymin = mean_nb - sd_nb, ymax = mean_nb + sd_nb), fill = "Red2", alpha=0.05) +
  geom_line(aes(y=mean_b, x=Position), color = "Grey32") +
  geom_line(aes(y=mean_nb, x=Position), color = "Red2") +
  theme_classic() +
  labs(y = "Mean firing rate (Hz)", x = "Position") +
  theme(axis.text.x = element_text(size=12),
        axis.text.y = element_text(size=12),
        legend.title = element_blank(),
        text = element_text(size=12))
ggsave(file = "plots/AverageRates_PositionCells_PosCue.png", width = 3.5, height = 2.5)


```




4. Subset data by group then average rates for plotting          **Positive PI**

```{r}
df_pos_pi <- df %>%
  subset(lm_group_beaconed == "Positive" & lm_group_nonbeaconed == "Positive") %>%
  group_by(Position) %>%
  subset(Position >= 30 & Position <= 90) %>%
  summarise(mean_b = mean(Rates,na.rm = TRUE), mean_nb = mean(Rates_nb,na.rm = TRUE), sd_b = std.error(Rates, na.rm = TRUE), sd_nb = std.error(Rates_nb, na.rm = TRUE)) %>%
  mutate(Position = rep(0:60))

```

5. Plot average rates

```{r}
ggplot(data=df_pos_pi) +
  geom_ribbon(aes(x=Position, y=mean_b, ymin = mean_b - sd_b, ymax = mean_b + sd_b), fill = "grey70", alpha=0.2) +
  geom_ribbon(aes(x=Position, y=mean_nb, ymin = mean_nb - sd_nb, ymax = mean_nb + sd_nb), fill = "Red2", alpha=0.05) +
  geom_line(aes(y=mean_b, x=Position), color = "Grey32") +
  geom_line(aes(y=mean_nb, x=Position), color = "Red2") +
  theme_classic() +
  labs(y = "Mean firing rate (Hz)", x = "Position") +
  theme(axis.text.x = element_text(size=12),
        axis.text.y = element_text(size=12),
        legend.title = element_blank(),
        text = element_text(size=12))
ggsave(file = "plots/AverageRates_PositionCells_NegPI.png", width = 3.5, height = 2.5)


```




4. Subset data by group then average rates for plotting          **Negative PI**

```{r}
df_neg_pi <- df %>%
  subset(lm_group_beaconed == "Negative" & lm_group_nonbeaconed == "Negative") %>%
  group_by(Position) %>%
  subset(Position >= 30 & Position <= 90) %>%
  summarise(mean_b = mean(Rates,na.rm = TRUE), mean_nb = mean(Rates_nb,na.rm = TRUE), sd_b = std.error(Rates, na.rm = TRUE), sd_nb = std.error(Rates_nb, na.rm = TRUE)) %>%
  mutate(Position = rep(0:60))
  
```

5. Plot average rates

```{r}
ggplot(data=df_neg_pi) +
  geom_ribbon(aes(x=Position, y=mean_b, ymin = mean_b - sd_b, ymax = mean_b + sd_b), fill = "grey70", alpha=0.2) +
  geom_ribbon(aes(x=Position, y=mean_nb, ymin = mean_nb - sd_nb, ymax = mean_nb + sd_nb), fill = "Red2", alpha=0.05) +
  geom_line(aes(y=mean_b, x=Position), color = "Grey32") +
  geom_line(aes(y=mean_nb, x=Position), color = "Red2") +
  theme_classic()  +
  labs(y = "Mean firing rate (Hz)", x = "Position") +
  theme(axis.text.x = element_text(size=12),
        axis.text.y = element_text(size=12),
        legend.title = element_blank(),
        text = element_text(size=12))
ggsave(file = "plots/AverageRates_PositionCells_PosPI.png", width = 3.5, height = 2.5)


```


4. Subset data by group then average rates for plotting          **Negative PI only**

```{r}
df_neg_pi <- df %>%
  subset(lm_group_beaconed == "Unclassified" & lm_group_nonbeaconed == "Negative") %>%
  group_by(Position) %>%
  subset(Position >= 30 & Position <= 90) %>%
  summarise(mean_b = mean(Rates,na.rm = TRUE), mean_nb = mean(Rates_nb,na.rm = TRUE), sd_b = std.error(Rates, na.rm = TRUE), sd_nb = std.error(Rates_nb, na.rm = TRUE)) %>%
  mutate(Position = rep(0:60))
  
```

5. Plot average rates

```{r}
ggplot(data=df_neg_pi) +
  geom_ribbon(aes(x=Position, y=mean_b, ymin = mean_b - sd_b, ymax = mean_b + sd_b), fill = "grey70", alpha=0.2) +
  geom_ribbon(aes(x=Position, y=mean_nb, ymin = mean_nb - sd_nb, ymax = mean_nb + sd_nb), fill = "Red2", alpha=0.05) +
  geom_line(aes(y=mean_b, x=Position), color = "Grey32") +
  geom_line(aes(y=mean_nb, x=Position), color = "Red2") +
  theme_classic()  +
  labs(y = "Mean firing rate (Hz)", x = "Position") +
  theme(axis.text.x = element_text(size=12),
        axis.text.y = element_text(size=12),
        legend.title = element_blank(),
        text = element_text(size=12))
ggsave(file = "plots/AverageRates_PositionCells_NegPIonly.png", width = 3.5, height = 2.5)


```




4. Subset data by group then average rates for plotting          **Positive PI only**

```{r}
df_neg_pi <- df %>%
  subset(lm_group_beaconed == "Unclassified" & lm_group_nonbeaconed == "Positive") %>%
  group_by(Position) %>%
  subset(Position >= 30 & Position <= 90) %>%
  summarise(mean_b = mean(Rates,na.rm = TRUE), mean_nb = mean(Rates_nb,na.rm = TRUE), sd_b = std.error(Rates, na.rm = TRUE), sd_nb = std.error(Rates_nb, na.rm = TRUE)) %>%
  mutate(Position = rep(0:60))
  
```

5. Plot average rates

```{r}
ggplot(data=df_neg_pi) +
  geom_ribbon(aes(x=Position, y=mean_b, ymin = mean_b - sd_b, ymax = mean_b + sd_b), fill = "grey70", alpha=0.2) +
  geom_ribbon(aes(x=Position, y=mean_nb, ymin = mean_nb - sd_nb, ymax = mean_nb + sd_nb), fill = "Red2", alpha=0.05) +
  geom_line(aes(y=mean_b, x=Position), color = "Grey32") +
  geom_line(aes(y=mean_nb, x=Position), color = "Red2") +
  theme_classic()  +
  labs(y = "Mean firing rate (Hz)", x = "Position") +
  theme(axis.text.x = element_text(size=12),
        axis.text.y = element_text(size=12),
        legend.title = element_blank(),
        text = element_text(size=12))
ggsave(file = "plots/AverageRates_PositionCells_PosPIonly.png", width = 3.5, height = 2.5)


```


### ---------------------------------------------------------------------------------------- ### 


Now, i want to visualise cue dependant and indpedant on the same plot so i can compare them

1. Subset data by group then average rates for plotting          **Negative slopes only**

```{r}

df_neg <- df %>%
  group_by(Position, group) %>%
  subset(Position >= 30 & Position <= 90) %>%
  summarise(mean_b = mean(Rates,na.rm = TRUE), mean_nb = mean(Rates_nb,na.rm = TRUE), sd_b = std.error(Rates, na.rm = TRUE), sd_nb = std.error(Rates_nb, na.rm = TRUE)) %>%
  subset(group != "None" & group == "Negative-cue" | group == "Negative-PI") #%>%
  #mutate(Position = rep(0:60))
  
```

2. Plot data 
```{r}
ggplot(data=df_neg) +
  geom_ribbon(aes(x=Position, y=mean_b, ymin = mean_b - sd_b, ymax = mean_b + sd_b, fill=group), alpha=0.2) +
  geom_line(aes(y=mean_b, x=Position, color=group)) +
  theme_classic() +
  scale_color_manual(values=c("deeppink1", "steelblue3", "chartreuse3")) +
  scale_fill_manual(values=c("deeppink1", "steelblue3", "chartreuse3")) +
  labs(y = "Mean firing rate (Hz)", x = "Position") +
  theme(axis.text.x = element_text(size=12),
        axis.text.y = element_text(size=12),
        legend.title = element_blank(),
        text = element_text(size=12))
ggsave(file = "plots/Negative_outbound.png", width = 6, height = 3)


```


3. Subset data by group then average rates for plotting          **Positive slopes only**


```{r}

df_pos <- df %>%
  group_by(Position, group) %>%
  subset(Position >= 30 & Position <= 90) %>%
  summarise(mean_b = mean(Rates,na.rm = TRUE), mean_nb = mean(Rates_nb,na.rm = TRUE), sd_b = std.error(Rates, na.rm = TRUE), sd_nb = std.error(Rates_nb, na.rm = TRUE)) %>%
  subset(group != "None" & group == "Positive-cue" | group == "Positive-PI")
  #mutate(Position = rep(0:60))
  
```


```{r}
ggplot(data=df_pos) +
  geom_ribbon(aes(x=Position, y=mean_b, ymin = mean_b - sd_b, ymax = mean_b + sd_b, fill=group), alpha=0.2) +
  geom_line(aes(y=mean_b, x=Position, color=group)) +
  theme_classic() +
  scale_color_manual(values=c("deeppink1", "steelblue3", "chartreuse3")) +
  scale_fill_manual(values=c("deeppink1", "steelblue3", "chartreuse3")) +
  labs(y = "Mean firing rate (Hz)", x = "Position") +
  theme(axis.text.x = element_text(size=12),
        axis.text.y = element_text(size=12),
        legend.title = element_blank(),
        text = element_text(size=12))
ggsave(file = "plots/Positive_outbound.png", width = 6, height = 3)

```




