---
title: "RampCodes_Figure1"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


---
title: "RampCodes_Figure1"
author: "Sarah Tennant & Matt Nolan"
date: "20/10/2021"
output: html_document
---


### ------------------------------------------------------------------------------------------ ### 

## Do ramping neurons encode speed, position or acceleration?

### ------------------------------------------------------------------------------------------ ### 



1. Test model

```{r}
df <- spatial_firing_2[140,] %>%
  select(spikes_in_time)

df1 <- tibble(
      Rates = as.numeric(unlist(df$spikes_in_time[[1]][1])),
      Position = as.numeric(unlist(df$spikes_in_time[[1]][2])),
      Acceleration = as.numeric(unlist(df$spikes_in_time[[1]][4])),
      Speed = as.numeric(unlist(df$spikes_in_time[[1]][3])),
      Trials = as.factor(unlist(df$spikes_in_time[[1]][5])),
      Types = as.factor(unlist(df$spikes_in_time[[1]][6]))
    )

```

```{r}
df1 <- df1 %>%
    subset(Position >= 30 & Position <= 90 & Speed >= 3 & Types == 0 & Acceleration > 0.01 & Rates > 0.01) %>%
    select(-Types) 

df1$Acceleration <- scale(df1$Acceleration, center=FALSE, scale=TRUE)
df1$Rates <- scale(df1$Rates, center=FALSE, scale=TRUE)
df1$Speed <- scale(df1$Speed, center=FALSE, scale=TRUE)
df1$Position <- scale(df1$Position, center=FALSE, scale=TRUE)

```

```{r}
ggplot()+
  geom_point(data = df1, aes(y=Rates, x=Position))


```


```{r}
glm1 <- glm(Rates ~ Position + Speed + Acceleration , family = Gamma(link = "log"), data = df1)

df_int <- lme4::glmer(formula = Rates ~ Position + Speed + Acceleration + (1 + Position | Trials), 
                      data = df1, 
                      na.action = na.exclude,
                      family = Gamma(link = "log"),
                      start=list(fixef=coef(glm1)),
                      control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
summary(df_int)

```
control=glmerControl(nAGQ0initStep=FALSE
                      control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)), 

```{r}
modelAnova <- car::Anova(df_int,type="III")
summary(modelAnova)
return_tibble <- tibble(pos = modelAnova$"Pr(>Chisq)"[[1]],
              speed = modelAnova$"Pr(>Chisq)"[[2]],
              accel = modelAnova$"Pr(>Chisq)"[[3]])
```




2. Run on all cells

## Fit mixed effect models to evaluate contributions of speed, acceleration and position to firing rate

Function to fit mixed effect models
```{r}

glm_fit <- function(df, TT = 0) {
  if (length(df) == 1){
    return(NA)}
  df <-
    tibble(
      Rates = as.numeric(df[[1]]),
      Position = as.numeric(df[[2]]),
      Acceleration = as.numeric(df[[4]]),
      Speed = as.numeric(df[[3]]),
      Trials = as.factor(df[[5]]), 
      Types = as.factor(df[[6]])
    )
  
  df <- df %>%
    subset(Position >= 30 & Position <= 90 & Speed >= 3 & Types == 0 & Rates > 0.01) %>%
    select(-Types) 

  df$Acceleration <- scale(df$Acceleration, center=FALSE, scale=TRUE)
  df$Rates <- scale(df$Rates, center=FALSE, scale=TRUE)
  df$Speed <- scale(df$Speed, center=FALSE, scale=TRUE)
  df$Position <- scale(df$Position, center=FALSE, scale=TRUE)
  
  if (length(df) == 1 | nrow(df) < 20) {
    return(NA)
  }
  glm1 <- glm(Rates ~ Position + Speed + Acceleration , family = Gamma(link = "log"), data = df)

  df_int <- lme4::glmer(formula = Rates ~ Position + Speed + Acceleration + (1 + Position | Trials), 
                        data = df, 
                        na.action = na.exclude,
                        family = Gamma(link = "log"),
                        start=list(fixef=coef(glm1)),
                        control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
}
```
#glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 100000)))
 df_int <- lme4::glmer(formula = Rates ~ Position + Speed + Acceleration + (1 + Position | Trials), 
                        data = df, 
                        na.action = na.exclude,
                        family = Gamma(link = "log"),
                        start=list(fixef=coef(glm1)),
                      control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))

  if (nrow(df) > 20 | nrow(df) < 100) {
    glm1 <- glm(Rates ~ Position + Speed + Acceleration , family = Gamma(link = "log"), data = df)
  }

Function to extract P values for each coefficient from the model
```{r}
glm_function <- function(mm, session_id) {
  if (is.na(mm)) {
    return(tibble(pos = NA, speed = NA, accel = NA))
  }
    modelAnova <- car::Anova(mm)
    return_tibble <- tibble(pos = modelAnova$"Pr(>Chisq)"[[1]],
                  speed = modelAnova$"Pr(>Chisq)"[[2]],
                  accel = modelAnova$"Pr(>Chisq)"[[3]])
    #print(return_tibble)
}
```

Function to extract P values for each coefficient from the model
```{r}

glm_pvalues <- function(mm, session_id) {
  tryCatch({
      glm_function(mm,session_id)
      },
    error=function(e){cat("ERROR :",conditionMessage(e), "\n")})
}
   
```


Function to extract P values for each coefficient from the model
```{r}

glm_fit_function <- function(mm, TT) {
  tryCatch({
      glm_fit(mm,TT)
      },
    error=function(e){cat("ERROR :",conditionMessage(e), "\n")})
}
   
```


2. Run on all cells.
Note here, there may be some overfitting with the mixed effect model. This is likely because some  coefficients likely do not vary with position. However, we can't address this by tailoring the model to each cell as we want to treat each cell the same way. The standardized coefficients should still be interpretable.
See discussion in ?isSingular and here: https://stats.stackexchange.com/questions/378939/dealing-with-singular-fit-in-mixed-models
```{r, warning=FALSE}
spatial_firing <- spatial_firing  %>%
  select(-contains('o_glm_p_b')) %>%
  mutate(o_glm_b = map2(spikes_in_time, 0, glm_fit_function)) %>%
  mutate(o_glm_p_b = map2(o_glm_b, session_id, glm_pvalues)) %>%
  unnest_wider(o_glm_p_b, names_sep = "_", names_repair = "universal") 
```



### ----------------------------------------------------------------------------------------- ###


## Select best model 

1. Write function to categorise neurons based on significant model coefficients
```{r}

model_comparison <- function(null_pos, null_speed, null_accel){
  pval <- 0.01
  if( is.na(null_pos) & is.na(null_accel)) {
    return( "None" )
  
  } else if( null_pos < pval & null_accel > pval & null_speed > pval) {
    return( "P" )
    
  } else if( null_pos > pval & null_accel > pval & null_speed < pval) {
    return( "S" ) 
    
  } else if( null_pos > pval & null_accel < pval & null_speed > pval) {
    return( "A" )
    
  } else if( null_pos < pval & null_accel > pval & null_speed < pval) {
    return("PS")
    
  } else if( null_pos < pval & null_accel < pval & null_speed > pval) {
    return( "PA" )
        
  } else if( null_pos > pval & null_accel < pval & null_speed < pval) {
    return("SA")

  } else if( null_pos < pval & null_accel < pval & null_speed < pval) {
    return("PSA")
    
  } else {
    return("None")
  }
}

```


2. Run on all cells in dataframe
```{r}
spatial_firing <- spatial_firing  %>%
    select(-contains('final_model_o_b')) %>%
    mutate(final_model_o_b  = pmap(list(o_glm_p_b_pos, o_glm_p_b_speed, o_glm_p_b_accel), model_comparison))
           #final_model_o_nb  = pmap(list(o_mm_p_nb_pos, o_mm_p_nb_speed, o_mm_p_nb_accel), model_comparison))#%>%
    #mutate(final_model_o_p  = pmap(list(o_pos_p, o_speed_p, o_accel_p), model_comparison))

```

### ----------------------------------------------------------------------------------------- ###

position encoding ramp neurons were classified with a similar slope on the non-beaconed and probe trials as on beaconed trials ....
1. extract position cells
```{r}
ramp_cells <- subset(spatial_firing, lm_group_b == "Negative" | lm_group_b == "Positive")

position_cells <- subset(ramp_cells, final_model_o_b == "P" | final_model_o_b == "PS" | final_model_o_b == "PA" | final_model_o_b == "PSA")

```



### ----------------------------------------------------------------------------------------- ###


### Plot model selection results

First for all cells. 

1. Split data by linear model result
```{r}
# extracting diff models 
pos <-subset(spatial_firing, lm_group_b == "Positive")
neg <-subset(spatial_firing, lm_group_b == "Negative")
none <-subset(spatial_firing, lm_group_b == "Unclassified")

```

2. Split data by mixed effect model result
```{r}

P_positive <- nrow(subset(pos, glm_model_o_b == "P"))/nrow(pos)*100
P_negative <- nrow(subset(neg, glm_model_o_b == "P"))/nrow(neg)*100
P_none <- nrow(subset(none,glm_model_o_b == "P"))/nrow(none)*100

S_positive <- nrow(subset(pos,glm_model_o_b == "S"))/nrow(pos)*100
S_negative <- nrow(subset(neg,glm_model_o_b == "S"))/nrow(neg)*100
S_none <- nrow(subset(none,glm_model_o_b == "S"))/nrow(none)*100

A_positive <- nrow(subset(pos,glm_model_o_b == "A"))/nrow(pos)*100
A_negative <- nrow(subset(neg,glm_model_o_b == "A"))/nrow(neg)*100
A_none <- nrow(subset(none,glm_model_o_b == "A"))/nrow(none)*100

P_S_positive <- nrow(subset(pos,glm_model_o_b == "PS"))/nrow(pos)*100
P_S_negative <- nrow(subset(neg,glm_model_o_b == "PS"))/nrow(neg)*100
P_S_none <- nrow(subset(none,glm_model_o_b == "PS"))/nrow(none)*100

P_A_positive <- nrow(subset(pos ,glm_model_o_b == "PA"))/nrow(pos)*100
P_A_negative <- nrow(subset(neg ,glm_model_o_b == "PA"))/nrow(neg)*100
P_A_none <- nrow(subset(none,glm_model_o_b == "PA"))/nrow(none)*100

S_A_positive <- nrow(subset(pos ,glm_model_o_b == "SA"))/nrow(pos)*100
S_A_negative <- nrow(subset(neg ,glm_model_o_b == "SA"))/nrow(neg)*100
S_A_none <- nrow(subset(none,glm_model_o_b == "SA"))/nrow(none)*100

P_S_A_positive <- nrow(subset(pos ,glm_model_o_b == "PSA"))/nrow(pos)*100
P_S_A_negative <- nrow(subset(neg ,glm_model_o_b == "PSA"))/nrow(neg)*100
P_S_A_none <- nrow(subset(none ,glm_model_o_b == "PSA"))/nrow(none)*100

NONE_positive <- nrow(subset(pos ,glm_model_o_b == "None"))/nrow(pos)*100
NONE_negative <- nrow(subset(neg ,glm_model_o_b == "None"))/nrow(neg)*100
NONE_none <- nrow(subset(none ,glm_model_o_b == "None"))/nrow(none)*100


```

2. number of cells in each group - positive sloping neurons
```{r}
P_positive_num <- nrow(subset(pos, glm_model_o_b == "P"))
P_A_positive_num <- nrow(subset(pos, glm_model_o_b == "PA"))
P_S_positive_num <- nrow(subset(pos, glm_model_o_b == "PS"))
P_S_A_positive_num <- nrow(subset(pos, glm_model_o_b == "PSA"))
S_A_positive_num <- nrow(subset(pos, glm_model_o_b == "SA"))
S_positive_num <- nrow(subset(pos, glm_model_o_b == "S"))
A_positive_num <- nrow(subset(pos, glm_model_o_b == "A"))
NONE_positive_num <- nrow(subset(pos, glm_model_o_b == "None"))

```

3. number of cells in each group - negative sloping neurons
```{r}
P_negative_num <- nrow(subset(neg, glm_model_o_b == "P"))
P_A_negative_num <- nrow(subset(neg, glm_model_o_b == "PA"))
P_S_negative_num <- nrow(subset(neg, glm_model_o_b == "PS"))
P_S_A_negative_num <- nrow(subset(neg, glm_model_o_b == "PSA"))
S_A_negative_num <- nrow(subset(neg, glm_model_o_b == "SA"))
S_negative_num <- nrow(subset(neg, glm_model_o_b == "S"))
A_negative_num <- nrow(subset(neg, glm_model_o_b == "A"))
NONE_negative_num <- nrow(subset(neg, glm_model_o_b == "None"))

```

3. number of cells in each group - unclassified  neurons
```{r}
P_none_num <- nrow(subset(none, glm_model_o_b == "P"))
P_A_none_num <- nrow(subset(none, glm_model_o_b == "PA"))
P_S_none_num <- nrow(subset(none, glm_model_o_b == "PS"))
P_S_A_none_num <- nrow(subset(none, glm_model_o_b == "PSA"))
S_A_none_num <- nrow(subset(none, glm_model_o_b == "SA"))
S_none_num <- nrow(subset(none, glm_model_o_b == "S"))
A_none_num <- nrow(subset(none, glm_model_o_b == "A"))
NONE_none_num <- nrow(subset(none, glm_model_o_b == "None"))

```

3. Put data into tibble
```{r}


mixed_ramps <- tibble(perc=c(P_positive,P_negative,P_none,S_positive, S_negative, S_none, A_positive,A_negative,A_none,  P_S_positive, P_S_negative,P_S_none, P_A_positive, P_A_negative, P_A_none, S_A_positive, S_A_negative, S_A_none,P_S_A_positive, P_S_A_negative, P_S_A_none, NONE_positive,NONE_negative, NONE_none), 
                      num=c(P_positive_num,P_negative_num,P_none_num,S_positive_num, S_negative_num, S_none_num, A_positive_num,A_negative_num,A_none_num,  P_S_positive_num, P_S_negative_num,P_S_none_num, P_A_positive_num, P_A_negative_num, P_A_none_num, S_A_positive_num, S_A_negative_num, S_A_none_num,P_S_A_positive_num, P_S_A_negative_num, P_S_A_none_num, NONE_positive_num,NONE_negative_num, NONE_none_num),
                      
                      ramp_id= c("P","P","P", 
                                 "S", "S", "S", 
                                 "A", "A", "A",
                                 "PS", "PS", "PS", 
                                 "PA", "PA", "PA", 
                                 "SA", "SA", "SA", 
                                 "PAS", "PAS","PAS",
                                 "None","None", "None"), 
                      ramp_type= c("Positive", "Negative", "Unclassified","Positive", "Negative", "Unclassified", "Positive", "Negative", "Unclassified","Positive", "Negative" ,"Unclassified","Positive", "Negative","Unclassified","Positive", "Negative","Unclassified", "Positive", "Negative", "Unclassified", "Positive", "Negative", "Unclassified" ))

```

4. Plot model results
```{r}
# plot data
level_order <- c("P", "S", "A", "PS", "PA","SA", "PAS", "None")
ggplot(mixed_ramps, aes(x= factor(ramp_type), y = perc, fill=factor(ramp_id, level = level_order))) +
  geom_bar(stat="identity",width = 0.9, alpha = .7) +
  labs(y = "Percent of neurons", x="") +
  scale_fill_manual(values=c("firebrick1","gold", "dodgerblue2", "darkorange", "darkorchid1", "chartreuse3", "darkslategray", "grey78")) +
  geom_text(aes(label = num), hjust = 0.7, vjust = 0.2, size = 5, position = position_stack(vjust= 0.5)) +
  #scale_fill_brewer(palette= "RdYlBu") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 50, vjust=0.65)) +
  theme(axis.text.x = element_text(size=17),
        axis.text.y = element_text(size=16),
        legend.position="bottom", 
        legend.title = element_blank(),
        text = element_text(size=16), 
        legend.text=element_text(size=16), 
        axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)))
if (save_figures == 1) {
  ggsave(file = "plots/GLMProportions_beaconed_update.png", width = 4, height = 5.5)
}
```





### Plot model selection results

First for all cells. 

1. Split data by linear model result
```{r}
# extracting diff models 
pos <-subset(spatial_firing, lm_group_b == "Positive")
neg <-subset(spatial_firing, lm_group_b == "Negative")
none <-subset(spatial_firing, lm_group_b == "Unclassified")

```

2. Split data by mixed effect model result
```{r}

P_positive <- subset(pos, glm_model_o_b == "P")
P_negative <- subset(neg, glm_model_o_b == "P")
P_none <- subset(none,glm_model_o_b == "P")

P_positive_glm <- nrow(subset(P_positive, final_model_o_b == "P"))/nrow(P_positive)*100
P_negative_glm <- nrow(subset(P_negative, final_model_o_b == "P"))/nrow(P_negative)*100
P_none_glm <- nrow(subset(P_none,final_model_o_b == "P"))/nrow(P_none)*100

P_positive_glm_num <- nrow(subset(P_positive, final_model_o_b == "P"))
P_negative_glm_num <- nrow(subset(P_negative, final_model_o_b == "P"))
P_none_glm_num <- nrow(subset(P_none,final_model_o_b == "P"))

```

2. Split data by mixed effect model result
```{r}

P_positive <- subset(pos, final_model_o_b == "P")
P_negative <- subset(neg, final_model_o_b == "P")
P_none <- subset(none,final_model_o_b == "P")

P_positive_lm <- nrow(subset(P_positive, glm_model_o_b == "P"))/nrow(P_positive)*100
P_negative_lm <- nrow(subset(P_negative, glm_model_o_b == "P"))/nrow(P_negative)*100
P_none_lm <- nrow(subset(P_none,glm_model_o_b == "P"))/nrow(P_none)*100

P_positive_lm_num <- nrow(subset(P_positive, glm_model_o_b == "P"))
P_negative_lm_num <- nrow(subset(P_negative, glm_model_o_b == "P"))
P_none_lm_num <- nrow(subset(P_none,glm_model_o_b == "P"))

```


3. Put data into tibble
```{r}


mixed_ramps <- tibble(perc=c(P_positive_glm,P_negative_glm,P_none_glm,P_positive_lm,P_negative_lm,P_none_lm), 
                      num=c(P_positive_glm_num,P_negative_glm_num,P_none_glm_num,P_positive_lm_num,P_negative_lm_num,P_none_lm_num),
                      
                      ramp_id= c("GLM","GLM","GLM", 
                                 "LMER", "LMER", "LMER"), 
                      ramp_type= c("Positive", "Negative", "Unclassified","Positive", "Negative", "Unclassified" ))

```

4. Plot model results
```{r}
# plot data
ggplot(mixed_ramps, aes(x= factor(ramp_type), y = perc, fill=factor(ramp_id))) +
  geom_bar(stat="identity",width = 0.9, alpha = .7) +
  labs(y = "Percent of neurons", x="") +
  scale_fill_manual(values=c("firebrick1","gold", "dodgerblue2", "darkorange", "darkorchid1", "chartreuse3", "darkslategray", "grey78")) +
  geom_text(aes(label = num), hjust = 0.7, vjust = 0.2, size = 5, position = position_stack(vjust= 0.5)) +
  #scale_fill_brewer(palette= "RdYlBu") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 50, vjust=0.65)) +
  theme(axis.text.x = element_text(size=17),
        axis.text.y = element_text(size=16),
        legend.position="bottom", 
        legend.title = element_blank(),
        text = element_text(size=16), 
        legend.text=element_text(size=16), 
        axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)))
if (save_figures == 1) {
  ggsave(file = "plots/GLMProportions_beaconed_Position.png", width = 4, height = 5.5)
}
```








### ----------------------------------------------------------------------------------------- ###

## Calculate standardized coefficients for position, speed and acceleration in LMER model


1. Load functions to calculate and extract standardised coefficients for each variable in the lmer
```{r}
#1. Function to calculate standardized coefficients for a LMER
#https://stackoverflow.com/questions/25142901/standardized-coefficients-for-lmer-model 


stdCoef.merMod <- function(object) {
  sdy <- sd(getME(object,"y"))
  sdx <- apply(getME(object,"X"), 2, sd)
  sc <- fixef(object)*sdx/sdy
  se.fixef <- coef(summary(object))[,"Std. Error"]
  se <- se.fixef*sdx/sdy
  return(data.frame(stdcoef=sc, stdse=se))
}
```

1. calculate and extract standardized coefficients for position, speed and acceleration

Function to calculate standardized coefficients from the model fits
```{r}
std_coef <- function(mm) {
  tryCatch({
  mod <- stdCoef.merMod(mm) 
  mod_coefs <- tibble(pos = mod[2,1],
                      speed = mod[3,1],
                      accel = mod[4,1])
      },
    error=function(e){cat("ERROR :",conditionMessage(e), "\n")})
}
  
```


3. Run on all cells
```{r, warning=FALSE}

spatial_firing <- spatial_firing  %>%
  select(-contains('o_b_mod_coefs_')) %>%
  mutate(o_b_mod_coefs = map(o_glm_b, std_coef)) %>%
  unnest_wider(o_b_mod_coefs, names_sep = "_", names_repair = "universal")
```

### plot distribution of coefficients for all cells
_split by positive and negative sloping neurons_

1. make unique id for each neuron (session_id + cluster_id)
```{r}
# First make a function to concatenate session id and cluster id
make_unique_id <- function(session,cluster) {
  x <- paste(session, cluster, sep="_")
  return(as.character(x))
}

# run on all cells
spatial_firing <- spatial_firing  %>%
  mutate(unique_id = map2(session_id, cluster_id, make_unique_id))

```

2. take only columns we need for the rest of the analysis
```{r}
spatial_firing_save <- select(spatial_firing, session_id, cluster_id, unique_id, o_b_mod_coefs_pos, o_b_mod_coefs_speed, o_b_mod_coefs_accel, final_model_o_b, lm_group_b) %>%
  unnest(cols = c(unique_id, o_b_mod_coefs_pos, o_b_mod_coefs_speed, o_b_mod_coefs_accel,
    final_model_o_b, lm_group_b)) %>%
  as.tibble()

```

4. put data into a tibble for plotting
```{r}
data_coef <- tibble(session_id = rep(unlist(spatial_firing_save$unique_id), times=3), 
                    cluster_id = rep(spatial_firing_save$cluster_id, times=3), 
                    coef = c(as.character(spatial_firing_save$o_b_mod_coefs_pos),
                             as.character(spatial_firing_save$o_b_mod_coefs_speed),
                             as.character(spatial_firing_save$o_b_mod_coefs_accel)),
                    group = c(as.character(spatial_firing_save$final_model_o_b),
                              as.character(spatial_firing_save$final_model_o_b),
                              as.character(spatial_firing_save$final_model_o_b)), 
                    # cue_group = c(as.character(spatial_firing_save$cue_group_o),
                    #            as.character(spatial_firing_save$cue_group_o),
                    #            as.character(spatial_firing_save$cue_group_o)),
                    coef_type = rep(c("P", "S", "A"),
                                    each = nrow(spatial_firing_save)),
                    lm_result = rep(as.character(spatial_firing_save$lm_group_b), times=3))
```

_Plot coefficients for all cells_


Make function for plotting standardised coefficients
```{r}
standard_plot <- function(df) {
  level_order <- c("P", "S", "A")
  ggplot(data=df, aes(x = factor(coef_type), y = as.numeric(coef))) +
  #coord_cartesian(ylim=c(0,1)) +
  geom_violin(aes(x = factor(coef_type), y = as.numeric(coef), fill=factor(coef_type, level=level_order)), alpha=0.7) +
  stat_summary(fun.y=mean, geom="point", shape=23, size=2) +
  geom_jitter(alpha=0.05) +
  scale_fill_manual(values=c("firebrick1","gold","dodgerblue2")) +
  #scale_y_log10() +
  #scale_y_continuous(trans='log2') +
  labs(y = "std coef", x="\n model parameter") +
  theme_classic() +
  theme(axis.text.x = element_text(size=14),
        axis.text.y = element_text(size=12),
        legend.position="bottom", 
        legend.title = element_blank(),
        text = element_text(size=12), 
        legend.text=element_text(size=12), 
        axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0))) 
}
```





5. Split by positive slope _all cells_
```{r}
data_coef_pos <- data_coef %>%
  subset(lm_result == "Positive" )

(pos_coef_plot <- standard_plot(data_coef_pos))
if (save_figures == 1) {
   ggsave(file = "plots/CoefficientValues_GLM_positivecells.png", width = 3, height = 2.5)
}
```

5. Split by negative slope _all cells_
```{r}
data_coef_neg <- data_coef %>%
  subset(lm_result == "Negative" )

(neg_coef_plot <- standard_plot(data_coef_neg))
if (save_figures == 1) {
  ggsave(file = "plots/CoefficientValues_GLM_negativecells.png", width = 3, height = 2.5)
}
```

_Plot coefficients for all cells_

5. Split by positive slope _PS cells_
```{r}
data_coef_pos_PS <- data_coef %>%
  subset(group == "PS") %>%
  subset(lm_result == "Positive" )

(pos_PS_coef_plot <- standard_plot(data_coef_pos_PS))
if (save_figures == 1) {
  ggsave(file = "plots/CoefficientValues_GLM_PositivePScells.png", width = 3, height = 2.5)
}
```

6. Split by negative slope
```{r}
data_coef_neg_PS <- data_coef %>%
  subset(group == "PS") %>%
  subset(lm_result == "Negative" )

(neg_PS_coef_plot <- standard_plot(data_coef_neg_PS))
if (save_figures == 1) {
  ggsave(file = "plots/CoefficientValues_GLM_NegativePScells.png", width = 3, height = 2.5)
}
```


_Plot coefficients for just position cells_


6a. Plot coefficients for cells classified in Figure 2 as having a positive slope and in Figure 3 as having significant fit coefficients for position only.

```{r}
data_coef_pos_P <- data_coef %>%
  subset(group == "P") %>%
  subset(lm_result == "Positive")

(pos_P_coef_plot <- standard_plot(data_coef_pos_P))
if (save_figures == 1) {
  ggsave(file = "plots/CoefficientValues_GLM_PositivePcells.png", width = 3, height = 2.5)
}
```



6b. Plot coefficients for cells classified in Figure 2 as having a negative slope and in Figure 3 as having significant fit coefficients for position only.

```{r}
data_coef_neg_P <- data_coef %>%
  subset(group == "P") %>%
  subset(lm_result == "Negative")

(neg_P_coef_plot <- standard_plot(data_coef_neg_P))
if (save_figures == 1) {
  ggsave(file = "plots/CoefficientValues_GLM_NegativePcells.png", width = 3, height = 2.5)
}
```


