---
title: "RampCodes_Supplemental3"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


### ------------------------------------------------------------------------------------------ ### 

### ------------------------------------------------------------------------------------------ ### 

Now, we can classify cells based on their predicted activity. 

1. Function to classify neurons based on offset 

```{r}
mark_reset_group_predict <- function(offset){
  if (is.na(offset) ) {
    return( "None" )
  } else if( offset == "None") {
    return( "Continuous" )
  } else if( ( offset == "Neg" ||  offset == "Pos")) {
    return( "Reset" ) 
  }
}

```

2. Run on all cells
```{r}
spatial_firing <- spatial_firing %>%
  mutate(reset_group = map(offset, mark_reset_group_predict))

```



### ------------------------------------------------------------------------------------------ ### 



## plot bar chart of mean apsolute difference between predicted and real

- do only for neurons that have slopes in outbound zone
- do this for both negative and positive slopes in the outbound zone

1. extract neurons that are ++ or -- on beaconed trials, position encoding (Figure 3) and driven by path integration (Figure 4)
```{r}
df_position_pi <- spatial_firing %>%
  filter(lm_group_b == "Positive" | lm_group_b == "Negative")  %>% 
  filter(final_model_o_b == "P" | final_model_o_b == "PS" | final_model_o_b == "PA" | final_model_o_b == "PSA")
  
```

4. Plot bar charts - positive neurons
```{r}
ggplot(data=subset(df_position_pi, lm_group_b == "Positive"), aes(x = unlist(predict_diff), fill=as.factor(unlist(reset_group)))) +
  coord_cartesian(xlim=c(-6,6)) +
  geom_histogram(aes(y=..count..), alpha=0.5) +
  scale_fill_manual(values=c(  "grey", "chartreuse3","chartreuse3")) +
  scale_y_continuous(breaks = scales::pretty_breaks(n = 3)) +
  labs(y="Density", x="") +
  theme_classic() +
  theme(axis.text.x = element_text(size=13),
        axis.text.y = element_text(size=13),
        legend.position="bottom", 
        legend.title = element_blank(),
        text = element_text(size=13), 
        legend.text=element_text(size=13), 
        axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)))

if (save_figures == 1) {
  ggsave(file = "plots/PredictHomeboundMean_positive.png",width = 4, height = 2.5)
}
```

5. Plot bar charts - Negative neurons
```{r}

ggplot(data=subset(df_position_pi,lm_group_b == "Negative"), aes(x = unlist(predict_diff), fill=as.factor(unlist(reset_group)))) +
  coord_cartesian(xlim=c(-5,5)) +
  geom_histogram(aes(y=..count..), alpha=0.5) +
  scale_fill_manual(values=c( "grey", "violetred2","violetred2")) +
  scale_y_continuous(breaks = scales::pretty_breaks(n = 3)) +
  labs(y="Density", x="") +
  theme_classic() +
  theme(axis.text.x = element_text(size=13),
        axis.text.y = element_text(size=13),
        legend.position="bottom", 
        legend.title = element_blank(),
        text = element_text(size=13), 
        legend.text=element_text(size=13), 
        axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)))

if (save_figures == 1) {
  ggsave(file = "plots/PredictHomeboundMean_negative.png",width = 4, height = 2.5)
}
```




### ------------------------------------------------------------------------------------------ ### 


## now plot scatter of slopes for outbound and slopes for homebound with neurons marked accordng to whether they are reset or continuous

1. Here we subset neurons based on position encoding (Figure 3) and path integrating (Figure 4) and either reset or contiuous firing. 
```{r}
position_neurons_reset <- spatial_firing  %>% 
  filter(final_model_o_b == "P" | final_model_o_b == "PS" | final_model_o_b == "PA" | final_model_o_b == "PSA")  %>% 
  filter(lm_group_b == "Positive" | lm_group_b == "Negative")  %>% 
  filter(reset_group == "Reset")

position_neurons_continuous <- spatial_firing  %>% 
  filter(final_model_o_b == "P" | final_model_o_b == "PS" | final_model_o_b == "PA" | final_model_o_b == "PSA")  %>% 
  filter(lm_group_b == "Positive" | lm_group_b == "Negative")  %>% 
  filter(reset_group == "Continuous")

position_neurons_all <- spatial_firing  %>% 
  filter(final_model_o_b == "P" | final_model_o_b == "PS" | final_model_o_b == "PA" | final_model_o_b == "PSA")  %>% 
  filter(lm_group_b == "Positive" | lm_group_b == "Negative") 
```

2. Plot scatter plot
```{r}

ggplot() + 
    geom_point(data=subset(position_neurons_all, track_category == "pospos" | track_category == "negneg"),
               aes(x = as.numeric(unlist(asr_b_o_rewarded_fit_slope)), 
                   y = as.numeric(unlist(asr_b_h_rewarded_fit_slope)), 
                   color=factor(unlist(lm_group_b))), alpha=0.8) +
    geom_point(data=subset(position_neurons_all, track_category == "posneg" | track_category == "negpos"),
               aes(x = as.numeric(unlist(asr_b_o_rewarded_fit_slope)), 
                   y = as.numeric(unlist(asr_b_h_rewarded_fit_slope)), 
                   color=factor(unlist(lm_group_b))), shape=2, alpha=0.8) +
    geom_point(data=subset(position_neurons_all, track_category == "posnon" | track_category == "negnon"),
               aes(x = as.numeric(unlist(asr_b_o_rewarded_fit_slope)), 
                   y = as.numeric(unlist(asr_b_h_rewarded_fit_slope)), 
                   color=factor(unlist(lm_group_b))), shape=3, alpha=0.8) +  
    #geom_point(data=subset(position_neurons_continuous, track_category == "pospos" | track_category == "negneg"),
               #aes(x = as.numeric(unlist(asr_b_o_rewarded_fit_slope)), 
               #    y = as.numeric(unlist(asr_b_h_rewarded_fit_slope)), 
               #    color=factor(unlist(lm_group_b))), shape=1, alpha=0.8) +

      #geom_point(data=position_neurons_reset,aes(x = as.numeric(unlist(asr_b_o_rewarded_fit_slope)), y = as.numeric(unlist(asr_b_h_rewarded_fit_slope)), color=factor(unlist(lm_group_b)))) +
    #geom_point(data=position_neurons_continuous,aes(x = as.numeric(unlist(asr_b_o_rewarded_fit_slope)), y = as.numeric(unlist(asr_b_h_rewarded_fit_slope)), color=factor(unlist(lm_group_b))), shape=1) +
    coord_cartesian(ylim = c(-.45,.61), xlim = c(-.45,.45)) +
    geom_abline(intercept = 0, slope = 1, colour = "grey", linetype = "dashed") +
    geom_abline(intercept = 0, slope = -1, colour = "grey", linetype = "dashed") +
    xlab("Outbound slope") +
    ylab("Homebound slope") +
    theme_classic() +
    scale_color_manual(values=c("violetred2", "chartreuse3")) +
    theme(axis.text.x = element_text(size=18),
          axis.text.y = element_text(size=18),
          legend.position="bottom", 
          legend.title = element_blank(),
          text = element_text(size=17), 
          legend.text=element_text(size=16), 
          axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0))) 

if (save_figures == 1) {
 ggsave(file = "plots/slope_comparison_reset.png", width = 4, height = 4) 
}
```

