---
title: "LMERhomebound"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Fit mixed effect models to evaluate contributions of speed, acceleration and position to firing rate

## Fit mixed effect models to evaluate contributions of speed, acceleration and position to firing rate

Function to fit mixed effect models
```{r}
mm_fit <- function(df, TT = 0) {
  if (length(df) == 1)
    return(NA)
  df <-
    tibble(
      Rates = as.numeric(Re(df[[1]])),
      Position = as.numeric(Re(df[[2]])),
      Acceleration = as.numeric(Re(df[[4]])),
      Speed = as.numeric(Re(df[[3]])),
      Trials = as.factor(df[[5]]),
      Types = as.factor(df[[6]])
    )
  df <- df %>%
    subset(Position >= 30 & Position <= 190 & Speed >= 3 & Types == TT)
  
  if (length(df) == 1 | nrow(df) < 3)
    return(NA)

  df_int <-
    lme4::lmer(
      Rates ~ Position + Speed + Acceleration + (1 + Position | Trials),
      data = df,
      na.action = na.exclude
    )

}
```


Function to extract P values for each coefficient from the model
```{r}
mm_function <- function(mm, session_id) {
  if (is.na(mm)) {
    return(tibble(pos = NA, speed = NA, accel = NA))
  }
    print(session_id)
    modelAnova <- car::Anova(mm)
    return_tibble <- tibble(pos = modelAnova$"Pr(>Chisq)"[[1]],
                  speed = modelAnova$"Pr(>Chisq)"[[2]],
                  accel = modelAnova$"Pr(>Chisq)"[[3]])
}
```

Function to extract P values for each coefficient from the model
```{r}

mm_pvalues <- function(mm, session_id) {
  tryCatch({
      mm_function(mm,session_id)
      },
    error=function(e){cat("ERROR :",conditionMessage(e), "\n")})
}
   
```


2. Run on all cells.
Note here, there may be some overfitting with the mixed effect model. This is likely because some  coefficients likely do not vary with position. However, we can't address this by tailoring the model to each cell as we want to treat each cell the same way. The standardized coefficients should still be interpretable.
See discussion in ?isSingular and here: https://stats.stackexchange.com/questions/378939/dealing-with-singular-fit-in-mixed-models
```{r, warning=FALSE}
spatial_firing <- spatial_firing  %>%
  #select(-contains('o_mm_p_b_')) %>%
  mutate(h_mm_b = map2(spikes_in_time, 0, mm_fit),
         #o_mm_nb = map2(spikes_in_time, 1, mm_fit),
         h_mm_p_b = map2(h_mm_b, session_id, mm_pvalues)) %>%
         #o_mm_p_nb = map(o_mm_nb, mm_pvalues))
  unnest_wider(h_mm_p_b, names_sep = "_", names_repair = "universal") #%>%
  #unnest_wider(o_mm_p_nb, names_sep = "_", names_repair = "universal")
```

Model p values are stored in:
spatial_firing$h_mm_p_b_pos
spatial_firing$h_mm_p_b_accel
spatial_firing$h_mm_p_b_speed


### ----------------------------------------------------------------------------------------- ###


## Select best model 

1. Write function to categorise neurons based on significant model coefficients
```{r}

model_comparison <- function(null_pos, null_speed, null_accel){
  pval <- 0.01
  if( is.na(null_pos) & is.na(null_accel)) {
    return( "None" )
  
  } else if( null_pos < pval & null_accel > pval & null_speed > pval) {
    return( "P" )
    
  } else if( null_pos > pval & null_accel > pval & null_speed < pval) {
    return( "S" ) 
    
  } else if( null_pos > pval & null_accel < pval & null_speed > pval) {
    return( "A" )
    
  } else if( null_pos < pval & null_accel > pval & null_speed < pval) {
    return("PS")
    
  } else if( null_pos < pval & null_accel < pval & null_speed > pval) {
    return( "PA" )
        
  } else if( null_pos > pval & null_accel < pval & null_speed < pval) {
    return("SA")

  } else if( null_pos < pval & null_accel < pval & null_speed < pval) {
    return("PSA")
    
  } else {
    return("None")
  }
}

```


2. Run on all cells in dataframe
```{r}

spatial_firing <- spatial_firing  %>%
    mutate(final_model_h_b  = pmap(list(h_mm_p_b_pos, h_mm_p_b_speed, h_mm_p_b_accel), model_comparison))
```




## save dataset for harry

2. take only columns we need for the rest of the analysis
```{r}
if(save_figures == 1) {
  spatial_firing_save <- select(spatial_firing, session_id, cluster_id, lm_group_b, final_model_o_b, final_model_h_b, lm_group_b_h, ramp_score) %>%
    unnest(cols = c(session_id, cluster_id, lm_group_b, final_model_o_b,final_model_h_b, lm_group_b_h, ramp_score)) %>%
  as.tibble()
}
```

3. save to csv file _this is for matching to plots from python_
```{r}
write_csv2(spatial_firing_save, "all_results_linearmodel.csv")
```


```{r}
saveRDS(spatial_firing_save, "SpatialFiring_dataset.Rda")

```


## save dataset for harry

2. take only columns we need for the rest of the analysis
```{r}
if(save_figures == 1) {
  spatial_firing_save <- select(spatial_firing, session_id, cluster_id, track_category) %>%
    unnest(cols = c(session_id, cluster_id, track_category)) %>%
  as.tibble()
}
```

3. save to csv file _this is for matching to plots from python_
```{r}
write_csv2(spatial_firing_save, "all_results_linearmodel.csv")
```

