---
title: "LMERhomebound"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Fit mixed effect models to evaluate contributions of speed, acceleration and position to firing rate

Function to fit mixed effect models in homebound region
```{r}
mm_fit_home <- function(df, TT = 0) {
  if (length(df) == 1)
    return(NA)
  df <-
    tibble(
      Rates = as.numeric(Re(df[[1]])),
      Position = as.numeric(Re(df[[2]])),
      Acceleration = as.numeric(Re(df[[4]])),
      Speed = as.numeric(Re(df[[3]])),
      Trials = as.factor(df[[5]]),
      Types = as.factor(df[[6]])
    )
  df <- df %>%
    subset(Position >= 30 & Position <= 90 & Speed > 3 & Types == TT)
  
  if (length(df) == 1 | nrow(df) < 3)
    return(NA)

  df_int <-
    lme4::lmer(
      Rates ~ Position + Speed + Acceleration + (1 + Position | Trials),
      data = df,
      na.action = na.exclude
    )

}
```


Function to extract P values for each coefficient from the model
```{r}
mm_pvalues <- function(mm) {
  if (is.na(mm)) {
    return(tibble(pos = NA, speed = NA, accel = NA))
  }
    modelAnova <- car::Anova(mm)
    return_tibble <- tibble(pos = modelAnova$"Pr(>Chisq)"[[1]],
                  speed = modelAnova$"Pr(>Chisq)"[[2]],
                  accel = modelAnova$"Pr(>Chisq)"[[3]])
}

```


2. Run on all cells 
```{r, warning=FALSE}
spatial_firing <- spatial_firing  %>%
  select(-contains('h_mm_p_b_')) %>%
  mutate(h_mm_b = map2(spikes_in_time, 0, mm_fit_home),
         h_mm_p_b = map(h_mm_b, mm_pvalues)) %>%
  unnest_wider(h_mm_p_b, names_sep = "_", names_repair = "universal")
```

Model p values are stored in:
spatial_firing$h_mm_p_b_pos
spatial_firing$h_mm_p_b_accel
spatial_firing$h_mm_p_b_speed


### ----------------------------------------------------------------------------------------- ###


## Select best model 

1. Write function to categorise neurons based on significant model coefficients
```{r}

model_comparison <- function(null_pos, null_speed, null_accel){
  pval <- 0.01
  if( is.na(null_pos) & is.na(null_accel)) {
    return( "None" )
  
  } else if( null_pos < pval & null_accel > pval & null_speed > pval) {
    return( "P" )
    
  } else if( null_pos > pval & null_accel > pval & null_speed < pval) {
    return( "S" ) 
    
  } else if( null_pos > pval & null_accel < pval & null_speed > pval) {
    return( "A" )
    
  } else if( null_pos < pval & null_accel > pval & null_speed < pval) {
    return("PS")
    
  } else if( null_pos < pval & null_accel < pval & null_speed > pval) {
    return( "PA" )
        
  } else if( null_pos > pval & null_accel < pval & null_speed < pval) {
    return("SA")

  } else if( null_pos < pval & null_accel < pval & null_speed < pval) {
    return("PSA")
    
  } else {
    return("None")
  }
}

```


2. Run on all cells in dataframe
```{r}
spatial_firing <- spatial_firing  %>%
    mutate(final_model_h_b  = pmap(list(h_mm_p_b_pos, h_mm_p_b_speed, h_mm_p_b_accel), model_comparison))
           #final_model_h_nb  = pmap(list(h_mm_p_nb_pos, h_mm_p_nb_speed, h_mm_p_nb_accel), model_comparison)) #%>%
    #mutate(final_model_h_p  = pmap(list(h_mm_p_p_pos, h_mm_p_p_speed, h_mm_p_p_accel), model_comparison))

```




## save dataset for harry

2. take only columns we need for the rest of the analysis
```{r}
if(save_figures == 1) {
  spatial_firing_save <- select(spatial_firing, session_id, cluster_id, lm_group_b, final_model_o_b, final_model_h_b, lm_group_b_h, cue_group_o) %>%
    unnest(cols = c(session_id, cluster_id, lm_group_b, final_model_o_b, final_model_h_b, lm_group_b_h, cue_group_o)) %>%
  as.tibble()
}
```

3. save to csv file _this is for matching to plots from python_
```{r}
write_csv2(spatial_firing_save, "all_results_linearmodel.csv")
```

