---
title: "RampCodes_Supplemental6"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```




### ------------------------------------------------------------------------------------------------- ### 

## Script aims plot properties and proportions of cells that classify as positive or negative in the linear model and plot schematic elements for explaining the shuffled data. 

### ------------------------------------------------------------------------------------------------- ### 

How many neurons are ramp cells? 

2. get total numbers numbers
```{r}
ramp_num <- nrow(subset(spatial_firing, lm_group_b == "Negative" | lm_group_b == "Positive"))
```

### ------------------------------------------------------------------------------------------------- ### 

Now we want to visualise the coefficients of all neurons and all shuffled datasets

Now lets find and plot the proportion of cells according to the classification

1. extract proportion of cells that meet each criteria
```{r}
start <- nrow(subset(spatial_firing, lm_group_b == "Negative"))/nrow(spatial_firing)*100
reward <- nrow(subset(spatial_firing, lm_group_b == "Positive"))/nrow(spatial_firing)*100
nonslope <- nrow(subset(spatial_firing, lm_group_b == "Unclassified"))/nrow(spatial_firing)*100
```

2. get total numbers numbers
```{r}
start_num <- nrow(subset(spatial_firing, lm_group_b == "Negative"))
reward_num <- nrow(subset(spatial_firing, lm_group_b == "Positive"))
nonslope_num <- nrow(subset(spatial_firing, lm_group_b == "Unclassified"))

```

3. Put into a tibble 
```{r}
proportions_mixed_ramps <- tibble(perc=c(start, reward, nonslope), num=c(start_num, reward_num, nonslope_num), ramp_id= c("Start", "ToReward", "Unclassified"),ramp_type = c("Start", "ToReward", "Unclassified"))
```


3. Plot bar graph of proportions
```{r}
ggplot(proportions_mixed_ramps, aes(x= ramp_type, y = perc, fill=factor(ramp_id))) +
  geom_bar(stat="identity",width = 0.9, alpha = .4) +
  labs(y = "Percent", x="") +
  scale_fill_manual(values=c("violetred2", "chartreuse3", "grey62")) +
  geom_text(aes(label = num), hjust = 1.5, vjust = 0.5, srt=90, size = 6, position = position_dodge(-0.5)) +
  theme_classic() +
  theme(axis.text.x = element_text(size=19),
        axis.text.y = element_text(size=20),
        legend.position="bottom", 
        legend.title = element_blank(),
        text = element_text(size=19), 
        legend.text=element_text(size=19), 
        axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)))
if (save_figures == 1) {
  ggsave(file = "plots/Outbound_ramp_proportions_update.png", width = 3, height = 5.5)
}
```


We might also want to visualise the coefficients for the real and shuffled dataset as a histogram.

1. First, make stacked histogram of slope values for real dataset 
```{r}
level_order <- c("Negative", "Positive", "Unclassified")

(exp_slopes_plot <- ggplot(data=spatial_firing, aes(x= asr_b_o_rewarded_fit_slope, fill=factor(unlist(lm_group_b), level = level_order))) +
    coord_cartesian(xlim = c(-0.45,0.45), ylim = c(0, 0.4)) +
    geom_histogram(aes(y=..count../sum(..count..)), binwidth=0.01, alpha=1) +
    labs(x = "Slope (Hz/cm)") +
    ylab("Proportion") +
    scale_y_continuous(breaks = scales::pretty_breaks(n = 4)) +
    scale_fill_manual(values=c("violetred2", "chartreuse3", "grey62")) +
    theme_classic() +
    theme(axis.text.x = element_text(size=16),
          axis.text.y = element_text(size=16),
          legend.title = element_blank(),
          legend.position = "none",
          text = element_text(size=16),
          legend.text=element_text(size=16),
          axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0))))
if (save_figures == 1) {
  ggsave(file = "plots/Outbound_slope_histogram_update.png", width = 4, height = 2)
}

level_order <- c("Negative", "Positive", "Unclassified")

ggplot(data=subset(spatial_firing, lm_group_b == "Positive"), aes(x= asr_b_o_rewarded_fit_slope, fill=factor(unlist(lm_group_b), level = level_order))) +
  coord_cartesian(xlim = c(-0.45,0.45)) +
  geom_histogram(aes(y=..count../sum(..count..)), binwidth=0.01, alpha=0.5) +
  ylab("Proportion") +
  scale_y_continuous(breaks = scales::pretty_breaks(n = 4)) +
  scale_fill_manual(values=c("violetred2", "chartreuse3", "grey62")) +
  theme_classic() +
  theme(axis.text.x = element_text(size=16),
        axis.text.y = element_text(size=16),
        legend.title = element_blank(),
        legend.position = "none",
        text = element_text(size=16),
        legend.text=element_text(size=16),
        axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)))
if (save_figures == 1) {
  ggsave(file = "plots/Outbound_slope_histogram_update_pos.png", width = 4, height = 2)
}


ggplot(data=subset(spatial_firing, lm_group_b == "Negative"), aes(x= asr_b_o_rewarded_fit_slope, fill=factor(unlist(lm_group_b), level = level_order))) +
  coord_cartesian(xlim = c(-0.45,0.45)) +
  geom_histogram(aes(y=..count../sum(..count..)), binwidth=0.01, alpha=0.5) +
  ylab("Proportion") +
  scale_y_continuous(breaks = scales::pretty_breaks(n = 4)) +
  scale_fill_manual(values=c("violetred2", "chartreuse3", "grey62")) +
  theme_classic() +
  theme(axis.text.x = element_text(size=16),
        axis.text.y = element_text(size=16),
        legend.title = element_blank(),
        legend.position = "none",
        text = element_text(size=16),
        legend.text=element_text(size=16),
        axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)))
if (save_figures == 1) {
  ggsave(file = "plots/Outbound_slope_histogram_update_neg.png", width = 4, height = 2)
}
```

## extract the home bound classifations for the shuffled data
```{r}
local_circ_shuffles_hb <- function(df_in, cs_path) {
  shuffled_df <- read_feather(cs_path)
  
  
  # get list of cells based on session id + cluster id
  # add unique id for each cell to both data frames
  shuffled_df$unique_cell_id <- paste(shuffled_df$session_id, shuffled_df$cluster_id)
  unique_cells = unique(shuffled_df[c("unique_cell_id")])
  number_of_cells = nrow(unique_cells)
  print('Number of cells in spike-level shuffle data:')
  print(number_of_cells)
  
  # reformat shuffled data
  shuffled_b <- shuffled_df %>%
    select(unique_cell_id, shuffle_id, beaconed_r2_hb, beaconed_slope_hb, beaconed_p_val_hb) %>%
    rename(neuron = "shuffle_id", slope = "beaconed_slope_hb", r.squared = "beaconed_r2_hb", p.value = "beaconed_p_val_hb") %>%
    group_by(unique_cell_id) %>%
    nest()
  shuffled_nb <- shuffled_df %>%
    select(unique_cell_id, shuffle_id, non_beaconed_r2_hb, non_beaconed_slope_hb, non_beaconed_p_val_hb) %>%
    rename(neuron = "shuffle_id", slope = "non_beaconed_slope_hb", r.squared = "non_beaconed_r2_hb", p.value = "non_beaconed_p_val_hb") %>%
    group_by(unique_cell_id) %>%
    nest()
  shuffled_p <- shuffled_df %>%
    select(unique_cell_id, shuffle_id, probe_r2_hb, probe_slope_hb, probe_p_val_hb) %>%
    rename(neuron = "shuffle_id", slope = "probe_slope_hb", r.squared = "probe_r2_hb", p.value = "probe_p_val_hb") %>%
    group_by(unique_cell_id) %>%
    nest()
  
  
  # Provides a reference for cell IDs in the experimental data
  unique_cell_ids <- paste(df_in$session_id, df_in$cluster_id)
  
  # initialise
  shuffled_results_b <- shuffled_b %>% filter(unique_cell_id == unique_cell_ids[1])
  shuffled_results_nb <- shuffled_b %>% filter(unique_cell_id == unique_cell_ids[1])
  shuffled_results_p <- shuffled_b %>% filter(unique_cell_id == unique_cell_ids[1])
  
  # iterate on list of cells in the main datset
  for(i in 2:length(unique_cell_ids)) {
    # find the shuffled data that correspond to the current cell
    shuffled_results_b <- rbind(shuffled_results_b,
                                shuffled_b %>%filter(unique_cell_id == unique_cell_ids[i]))
    shuffled_results_nb <- rbind(shuffled_results_nb,
                                 shuffled_b %>% filter(unique_cell_id == unique_cell_ids[i]))
    shuffled_results_p <- rbind(shuffled_results_p,
                                shuffled_b %>% filter(unique_cell_id == unique_cell_ids[i]))
 
  }
  
  df <- tibble(unique_cell_id = shuffled_results_b$unique_cell_id,
               shuffle_results_b_h = shuffled_results_b$data,
               shuffled_results_nb_h = shuffled_results_nb$data,
               shuffled_results_p_h = shuffled_results_p$data)
  
  return(df)
}

```

```{r}
# To load circular shuffle results
if(shuffle_type=="circular") {
  cs_path = "data_in/all_mice_concatenated_shuffle_data_rewarded_unsmoothened.feather"
  spatial_firing_circ <- local_circ_shuffles_hb(spatial_firing, cs_path)
  
  spatial_firing <- spatial_firing %>%
  select(-contains('shuffle_results_b_h')) %>%
  select(-contains('shuffle_results_nb_h')) %>%
  select(-contains('shuffle_results_pb_h')) %>%
  mutate(shuffle_results_b_h = spatial_firing_circ$shuffle_results_b_h,
         shuffle_results_nb_h = spatial_firing_circ$shuffled_results_nb_h,
         shuffle_results_p_h = spatial_firing_circ$shuffled_results_p_h)
  # Remove unused frame
  rm(spatial_firing_circ)
}

# Check to see if the column shuffle_results_b_o exists.
# It will exist if shuffles have been pre-loaded or if circular shuffle results have been loaded.
# If it doesn't exist then the mean firing rate as a function of position will be shuffled.
if(!"shuffle_results_b_h" %in% colnames(spatial_firing)) {
  spatial_firing <- spatial_firing %>%
    mutate(shuffle_results_b_h = future_pmap(list(Rates_averaged_rewarded_b, 110, 170, shuffles), shuffle_rates)) %>%
    mutate(shuffle_results_nb_h = future_pmap(list(Rates_averaged_rewarded_nb, 110, 170, shuffles), shuffle_rates)) %>%
    mutate(shuffle_results_p_h = future_pmap(list(Rates_averaged_rewarded_p, 110, 170, shuffles), shuffle_rates))
}
```
```{r}
spatial_firing <- spatial_firing %>%
  unnest_wider(shuffle_results_b_h, names_sep = "_", names_repair = "universal")
```


### How much of the shuffled dataset is past criteria? 
1. Extract shuffled slopes and rsquared values. 
```{r}
shuff_slopes <- tibble(slopes = unlist(spatial_firing$shuffle_results_b_o_slope), 
                       r2 = unlist(spatial_firing$shuffle_results_b_o_r.squared), 
                       pval = unlist(spatial_firing$shuffle_results_b_o_p.value), 
                       min_slope = rep(spatial_firing$shuffle_min_slope_b_o, each = 1000), 
                       max_slope = rep(spatial_firing$shuffle_max_slope_b_o, each = 1000),
                       
                       slopes_h = unlist(spatial_firing$shuffle_results_b_h_slope), 
                       r2_h = unlist(spatial_firing$shuffle_results_b_h_r.squared), 
                       pval_h = unlist(spatial_firing$shuffle_results_b_h_p.value))
#shuff_slopes <- head(shuff_slopes, n =1000)         
```

2. Function to classify shuffled cells based on shuffled distribution
```{r}
shuff_slopes <- shuff_slopes %>%
  mutate(shuff_lm_group_b = pmap(list(min_slope,max_slope,slopes,pval),compare_slopes))

shuff_slopes <- shuff_slopes %>%
  mutate(shuff_lm_group_b_h = pmap(list(min_slope,max_slope,slopes_h,pval_h),compare_slopes))

shuff_slopes <- shuff_slopes %>%
  select(-contains('track_category')) %>%
  mutate(track_category = future_map2(shuff_lm_group_b, shuff_lm_group_b_h, mark_track_category),
         track_category_numeric = map2(shuff_lm_group_b, shuff_lm_group_b_h, mark_numeric_track_category))
```

2. Plot pre reward vs post reward slope for shuffled dataset
```{r}
position_shuff_slopes <- shuff_slopes %>% 
  filter(shuff_lm_group_b == "Positive" | shuff_lm_group_b == "Negative") %>%
  select(slopes, slopes_h,track_category, shuff_lm_group_b)


ggplot() + 
    geom_point(data=subset(position_shuff_slopes, track_category == "pospos" | track_category == "negneg"),
               aes(x = as.numeric(unlist(slopes)), 
                   y = as.numeric(unlist(slopes_h)), 
                   color=factor(unlist(shuff_lm_group_b))), alpha=0.8) +
    geom_point(data=subset(position_shuff_slopes, track_category == "posneg" | track_category == "negpos"),
               aes(x = as.numeric(unlist(slopes)), 
                   y = as.numeric(unlist(slopes_h)), 
                   color=factor(unlist(shuff_lm_group_b))), shape=2, alpha=0.8) +
    geom_point(data=subset(position_shuff_slopes, track_category == "posnon" | track_category == "negnon"),
               aes(x = as.numeric(unlist(slopes)), 
                   y = as.numeric(unlist(slopes_h)), 
                   color=factor(unlist(shuff_lm_group_b))), shape=3, alpha=0.8) +  
  
    geom_point(data=shuff_slopes %>% filter(shuff_lm_group_b == "Unclassified"),
               aes(x = as.numeric(unlist(slopes)), 
                   y = as.numeric(unlist(slopes_h)), 
                   color=factor(unlist(shuff_lm_group_b))), shape=4, alpha=0.8) +     
    coord_cartesian(ylim = c(-.45,.61), xlim = c(-.45,.45)) +
    geom_abline(intercept = 0, slope = 1, colour = "grey", linetype = "dashed") +
    geom_abline(intercept = 0, slope = -1, colour = "grey", linetype = "dashed") +
    xlab("Pre-reward slope") +
    ylab("Post-reward slope") +
    theme_classic() +
    scale_color_manual(values=c("violetred2", "chartreuse3", "grey81")) +
    theme(axis.text.x = element_text(size=18),
          axis.text.y = element_text(size=18),
          legend.position="bottom", 
          legend.title = element_blank(),
          text = element_text(size=17), 
          legend.text=element_text(size=16), 
          axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0))) 

if (save_figures == 1) {
 ggsave(file = "plots/shuffle_slope_comparison_reset.png", width = 4, height = 4) 
}

```


2. Plot histogram of slopes
```{r}
level_order <- c("Negative", "Positive", "Unclassified")

(shuffle_slopes_plot <- ggplot(data=shuff_slopes, aes(x = slopes, fill=factor(unlist(shuff_lm_group_b), level = level_order))) +
    coord_cartesian(xlim = c(-0.45,0.45), ylim = c(0, 0.4)) +
    geom_histogram(aes(y=..count../sum(..count..)), binwidth=0.01) +
    labs(x = "Slope (Hz/cm)") +
    ylab("Proportion") +
    scale_fill_manual(values=c("violetred2", "chartreuse3", "grey62")) +
    scale_y_continuous(breaks = scales::pretty_breaks(n = 4)) +
    theme_classic() +
    theme(axis.text.x = element_text(size=16),
          axis.text.y = element_text(size=16),
          legend.title = element_blank(),
          legend.position = "none",
          text = element_text(size=16),
          legend.text=element_text(size=16),
          axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0))))
if (save_figures == 1) {
  ggsave(file = "plots/Outbound_slope_histogram_shuffled.png", width = 4, height = 2)
}
```


3. Make stacked histogram of rsquared values for real dataset
```{r}
level_order <- c("Negative", "Positive", "Unclassified")

(exp_r2_plot <- ggplot(data=spatial_firing, aes(x= asr_b_o_rewarded_fit_r.squared, fill=factor(unlist(lm_group_b), level = level_order))) + 
  coord_cartesian(xlim = c(0,1), ylim = c(0,0.12)) +
  geom_histogram(aes(y=..count../sum(..count..)), binwidth=0.01) +
  ylab("Proportion") +
  xlab(expression(R^2)) +
  scale_fill_manual(values=c("violetred2", "chartreuse3", "grey62")) +
  scale_y_continuous(breaks = scales::pretty_breaks(n = 4)) +
  theme_classic() +
  theme(axis.text.x = element_text(size=16),
        axis.text.y = element_text(size=16),
        legend.title = element_blank(),
        legend.position = "none",
        text = element_text(size=16),
        legend.text=element_text(size=16),
        axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0))))

if (save_figures == 1) {
  ggsave(file = "plots/Outbound_rsquared_histogram_update.png", width = 4, height = 2)
}
```

4. Same as above but for shuffled datasets
```{r}
(shuffle_r2_plot <- ggplot(data=shuff_slopes, aes(x = r2, fill=factor(unlist(shuff_lm_group_b)))) +
    coord_cartesian(xlim = c(0,1), ylim = c(0,0.12)) +
    geom_histogram(aes(y=..count../sum(..count..)), binwidth=0.01) +
    xlab(expression(R^2)) +
    ylab("Proportion") +
    scale_fill_manual(values=c("violetred2", "chartreuse3", "grey62")) +
    scale_y_continuous(breaks = scales::pretty_breaks(n = 3)) +
    theme_classic() +
    theme(axis.text.x = element_text(size=16),
          axis.text.y = element_text(size=16),
          legend.position="none",
          legend.title = element_blank(),
          text = element_text(size=16),
          legend.text=element_text(size=16),
          axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0))))

if (save_figures == 1) {
  ggsave(file = "plots/Outbound_rsquared_histogram_shuffled.png", width = 4, height = 2)
}
```


Make a figure
```{r}
cowplot::plot_grid(exp_slopes_plot, shuffle_slopes_plot, exp_r2_plot, shuffle_r2_plot, labels = c("A", "B", "C", "D"), label_size = 16)
ggsave(file = "plots/exp_vs_shuffle.jpg")
```


Look at p values too
```{r}
(exp_pval_plot <- ggplot(data=spatial_firing, aes(x= asr_b_o_rewarded_fit_p.value, fill=factor(unlist(lm_group_b), level = level_order))) + 
  coord_cartesian(xlim = c(0,1), ylim = c(0,0.7)) +
   geom_histogram(aes(y=..count../sum(..count..)),
                   binwidth=0.005) +
  ylab("Proportion") +
  xlab(expression(p)) +
  scale_fill_manual(values=c("violetred2", "chartreuse3", "grey62")) +
  scale_y_continuous(breaks = scales::pretty_breaks(n = 4)) +
  theme_classic() +
  theme(axis.text.x = element_text(size=16),
        axis.text.y = element_text(size=16),
        legend.title = element_blank(),
        legend.position = "none",
        text = element_text(size=16),
        legend.text=element_text(size=16),
        axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0))))

```

```{r}
(shuffle_pval_plot <- ggplot(data=shuff_slopes, aes(x = pval, fill=factor(unlist(shuff_lm_group_b)))) +
    coord_cartesian(xlim = c(0,1), ylim = c(0,0.7)) +
    geom_histogram(aes(y=..count../sum(..count..)),
                   binwidth=0.005) +
    xlab(expression(p)) +
    ylab("Proportion") +
    scale_fill_manual(values=c("violetred2", "chartreuse3", "grey62")) +
    scale_y_continuous(breaks = scales::pretty_breaks(n = 3)) +
    theme_classic() +
    theme(axis.text.x = element_text(size=16),
          axis.text.y = element_text(size=16),
          legend.position="none",
          legend.title = element_blank(),
          text = element_text(size=16),
          legend.text=element_text(size=16),
          axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0))))


```

```{r}
cowplot::plot_grid(exp_pval_plot, shuffle_pval_plot, labels = c("A", "B"), label_size = 16)
ggsave(file = "plots/exp_vs_shuffle_pvals.jpg")
```

### ------------------------------------------------------------------------------------------------- ### 

## Plot shuffled example for Supplemental Figure 7A

### ------------------------------------------------------------------------------------------------- ### 


1. Function to generate shuffles
- shuffles spikes using sample() function
- runs lm
- extracts coefficients
- stores coefficients for each 1000 shuffles (less memory than saving 1000 shuffles)
```{r}
# shuffles defines the number of shuffes. Use a smaller value for testing.
shuffle_rates_example <- function(df, shuffles = 10) {
  df_modified <- data.frame(neuron = as.numeric(),
                 Rates=as.double())
  names(df_modified) <- c("neuron", "Rates")
  x <- 1
  repeat {
  fr_shuffled <- sample(as.vector(unlist(df)),replace = TRUE, prob = NULL)
  data <- data.frame(as.numeric(x),list(fr_shuffled))
  names(data) <- c("neuron","Rates")
  df_modified <- rbind(df_modified,data)

  x = x+1
  if (x == shuffles){ 
  break
  }
  }
return(df_modified)
}
```

2. Run if shuffles haven't already been generated.
```{r}

# Check to see if the column shuffle_results exists. If it does then don't run again.
shuffles <- 1000
spatial_firing_example <- spatial_firing[14,] %>%
  #select(-contains('shuffle_rates')) %>%
  select(cluster_id, session_id, Rates_averaged_rewarded_b, asr_b_o_rewarded_fit_r.squared, asr_b_o_rewarded_fit_slope) %>%
  mutate(shuffle_rates = map2(Rates_averaged_rewarded_b, shuffles, shuffle_rates_example))

```

```{r}
spatial_firing_example <- spatial_firing_example %>%
  unnest_wider(shuffle_rates, names_sep = "_", names_repair = "universal")

```


Function to plot mean and SEM of firing rate as a function of position.
```{r}
position = c(-29:169)
rates = unlist(unlist(spatial_firing_example$Rates_averaged_rewarded_b))

ggplot() +
  geom_point(aes(x=position, y=rates)) +
  theme_classic() +
  annotate("rect", xmin=-30, xmax=0, ymin=5,ymax=Inf, alpha=0.2, fill="Grey60") +
  annotate("rect", xmin=140, xmax=170, ymin=5,ymax=Inf, alpha=0.2, fill="Grey60") +
  annotate("rect", xmin=60, xmax=80, ymin=5,ymax=Inf, alpha=0.2, fill="Chartreuse4") +
  scale_x_continuous(breaks=seq(-30,170,100), expand = c(0, 0)) +
  scale_y_continuous(breaks=seq(5,50,10), expand = c(0, 0)) +
  labs(y = "Mean firing rate (Hz)", x = "Position") +
  theme(axis.text.x = element_text(size=18),
        axis.text.y = element_text(size=18),
        legend.title = element_blank(),
        text = element_text(size=18),
        plot.margin = margin(21, 25, 5, 20))
 ggsave(file = "plots/ExampleShuffled_Real.png",  width = 3.6, height = 2.9) 

```



Function to plot mean and SEM of firing rate as a function of position.
```{r}

Frates = unlist(unlist(spatial_firing_example$shuffle_rates_Rates))
Fposition = rep(c(-29:169), times = as.integer(length(Frates)/199))
Ftrials = rep(c(1:999), each = 199) #198801

frame <- tibble(rates = Frates,
                position = Fposition, 
                trials = Ftrials)
                   
data_wide <- spread(frame, position, rates)

position = c(-29:169)
rates = unlist(unlist(spatial_firing_example$Rates_averaged_rewarded_b))
position_o = position[30:90]
rates_o = rates[30:90]

ggplot() +
  geom_smooth(data=frame, aes(x=frame$position, y=frame$rates, group=factor(frame$trials)), method = "lm", se = FALSE, color ="grey", alpha=0.5) +
  geom_smooth(aes(x=position, y=rates), method = "lm", se = FALSE, color ="red") +
  theme_classic() +
  xlim(0, 60) +
  #scale_x_continuous(breaks=seq(0,30,60), expand = c(0, 0)) +
  #scale_y_continuous(breaks=seq(0,40), expand = c(0, 0)) +
  labs(y = "Mean firing rate (Hz)", x = "Location (cm)") +
  theme(axis.text.x = element_text(size=18),
        axis.text.y = element_text(size=18),
        legend.title = element_blank(),
        text = element_text(size=18),
        plot.margin = margin(21, 25, 5, 20))
 ggsave(file = "plots/ExampleShuffled_ShuffledLM.png",  width = 4, height = 2.9) 

```


2. Run if shuffles haven't already been generated.
```{r}

# Check to see if the column shuffle_results exists. If it does then don't run again.
shuffles <- 1000
spatial_firing_example <- spatial_firing[14,] %>%
  select(cluster_id, session_id, Rates_averaged_rewarded_b, asr_b_o_rewarded_fit_r.squared, asr_b_o_rewarded_fit_slope) %>%
  mutate(shuffle_results = pmap(list(Rates_averaged_rewarded_b, 30, 90, shuffles), shuffle_rates))

```

2. Run on all neurons
```{r}
spatial_firing_example <- spatial_firing_example %>%
  mutate(shuffle_min_slope = map_dbl(shuffle_results, extract_min_shuffle_slopes),
         shuffle_max_slope = map_dbl(shuffle_results, extract_max_shuffle_slopes))

```


We also want to extract slopes, r2 and pvalues of the 1000 shuffles for each neuron

1. Extract shuffle results (slopes and r2 for each shuffle)
2. run on all neurons
```{r}
spatial_firing_example <- spatial_firing_example %>%
  unnest_wider(shuffle_results, names_sep = "_", names_repair = "universal") 
```

1. extract shuffled values into tibble _each 1000 shuffled datasets are nested for each neuron_
```{r}
shuff_slopes <- tibble(slopes = unlist(spatial_firing_example$shuffle_results_slope), r2 = unlist(spatial_firing_example$shuffle_results_r.squared))
```



Plot distribution of the shuffled data

1. Extract shuffled slopes and rsquared values. This is already done above.

2. Plot in scatter
```{r}
ggplot(data=spatial_firing_example) +
    geom_point(data=shuff_slopes, aes(x = slopes, y = r2)) +
    geom_point(data=spatial_firing_example, aes(x = asr_b_o_rewarded_fit_slope, y = asr_b_o_rewarded_fit_r.squared), color="Red") +
    geom_vline(xintercept = spatial_firing_example$shuffle_min_slope, linetype="dotted", 
                color = "blue", size=1) +
    geom_vline(xintercept = spatial_firing_example$shuffle_max_slope, linetype="dotted", 
                color = "blue", size=1) +  
    xlab("Slope (Hz/cm)") +
    ylab(expression(R^2)) +
    theme_classic() +
    theme(axis.text.x = element_text(size=12),
          axis.text.y = element_text(size=12),
          legend.position="bottom",
          legend.title = element_blank(),
          text = element_text(size=12),
          legend.text=element_text(size=12),
          axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)))
if (save_figures == 1) {
  ggsave(file = "plots/Outbound_coefficient_scatter_shuffledeg.png", width = 3.5, height = 2.5)
}
```




Function to plot mean and SEM of firing rate as a function of position.
```{r}
position = c(-29:169)
rates_measured = unlist(unlist(spatial_firing_example$Rates_averaged_rewarded_b))
position_o = c(0:60)
position_h = c(80:140)
rates_o <- rates[30:90]
rates_h <- rates[110:170]

ggplot() +
  #geom_point(aes(x=position, y=rates)) +
  geom_smooth(aes(x=position_o, y=rates_o), method = "lm", se = FALSE, color ="red") +
  theme_classic() +
  annotate("rect", xmin=-30, xmax=0, ymin=5,ymax=Inf, alpha=0.2, fill="Grey60") +
  annotate("rect", xmin=140, xmax=170, ymin=5,ymax=Inf, alpha=0.2, fill="Grey60") +
  annotate("rect", xmin=60, xmax=80, ymin=5,ymax=Inf, alpha=0.2, fill="Chartreuse4") +
  scale_x_continuous(breaks=seq(-30,170,100), expand = c(0, 0)) +
  scale_y_continuous(breaks=seq(5,50,10), expand = c(0, 0)) +
  labs(y = "Mean firing rate (Hz)", x = "Position") +
  theme(axis.text.x = element_text(size=18),
        axis.text.y = element_text(size=18),
        legend.title = element_blank(),
        text = element_text(size=18),
        plot.margin = margin(21, 25, 5, 20))
 ggsave(file = "plots/ExampleShuffled_Real.png",  width = 3.6, height = 2.9) 

```


