---
title: "RampCodes_Supplemental6"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```




### ------------------------------------------------------------------------------------------------- ### 

## Script aims plot properties and proportions of cells that classify as positive or negative in the linear model and plot schematic elements for explaining the shuffled data. 

### ------------------------------------------------------------------------------------------------- ### 

How many neurons are ramp cells? 

2. get total numbers numbers
```{r}
ramp_num <- nrow(subset(spatial_firing, lm_group_b == "Negative" | lm_group_b == "Positive"))
```

### ------------------------------------------------------------------------------------------------- ### 

Now we want to visualise the coefficients of all neurons and all shuffled datasets

Now lets find and plot the proportion of cells according to the classification

1. extract proportion of cells that meet each criteria
```{r}
start <- nrow(subset(spatial_firing, lm_group_b == "Negative"))/nrow(spatial_firing)*100
reward <- nrow(subset(spatial_firing, lm_group_b == "Positive"))/nrow(spatial_firing)*100
nonslope <- nrow(subset(spatial_firing, lm_group_b == "Unclassified"))/nrow(spatial_firing)*100
```

2. get total numbers numbers
```{r}
start_num <- nrow(subset(spatial_firing, lm_group_b == "Negative"))
reward_num <- nrow(subset(spatial_firing, lm_group_b == "Positive"))
nonslope_num <- nrow(subset(spatial_firing, lm_group_b == "Unclassified"))

```

3. Put into a tibble 
```{r}
proportions_mixed_ramps <- tibble(perc=c(start, reward, nonslope), num=c(start_num, reward_num, nonslope_num), ramp_id= c("Start", "ToReward", "Unclassified"),ramp_type = c("Start", "ToReward", "Unclassified"))
```


3. Plot bar graph of proportions
```{r}
ggplot(proportions_mixed_ramps, aes(x= ramp_type, y = perc, fill=factor(ramp_id))) +
  geom_bar(stat="identity",width = 0.9, alpha = .4) +
  labs(y = "Percent", x="") +
  scale_fill_manual(values=c("violetred2", "chartreuse3", "grey62")) +
  geom_text(aes(label = num), hjust = 1.5, vjust = 0.5, srt=90, size = 6, position = position_dodge(-0.5)) +
  theme_classic() +
  theme(axis.text.x = element_text(size=19),
        axis.text.y = element_text(size=20),
        legend.position="bottom", 
        legend.title = element_blank(),
        text = element_text(size=19), 
        legend.text=element_text(size=19), 
        axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)))
if (save_figures == 1) {
  ggsave(file = "plots/Outbound_ramp_proportions_update.png", width = 3, height = 5.5)
}
```


We might also want to visualise the coefficients for the real and shuffled dataset as a histogram.

1. First, make stacked histogram of slope values for real dataset 
```{r}
level_order <- c("Negative", "Positive", "Unclassified")

ggplot(data=spatial_firing, aes(x= asr_b_o_rewarded_fit_slope, fill=factor(unlist(lm_group_b), level = level_order))) +
  coord_cartesian(xlim = c(-0.45,0.45)) +
  geom_histogram(aes(y=..count../sum(..count..)), binwidth=0.01, alpha=0.9999) +
  ylab("Proportion") +
  scale_y_continuous(breaks = scales::pretty_breaks(n = 4)) +
  scale_fill_manual(values=c("violetred2", "chartreuse3", "grey62")) +
  theme_classic() +
  theme(axis.text.x = element_text(size=16),
        axis.text.y = element_text(size=16),
        legend.title = element_blank(),
        legend.position = "none",
        text = element_text(size=16),
        legend.text=element_text(size=16),
        axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)))
if (save_figures == 1) {
  ggsave(file = "plots/Outbound_slope_histogram_update.png", width = 4, height = 2)
}

level_order <- c("Negative", "Positive", "Unclassified")

ggplot(data=subset(spatial_firing, lm_group_b == "Positive"), aes(x= asr_b_o_rewarded_fit_slope, fill=factor(unlist(lm_group_b), level = level_order))) +
  coord_cartesian(xlim = c(-0.45,0.45)) +
  geom_histogram(aes(y=..count../sum(..count..)), binwidth=0.01, alpha=0.5) +
  ylab("Proportion") +
  scale_y_continuous(breaks = scales::pretty_breaks(n = 4)) +
  scale_fill_manual(values=c("violetred2", "chartreuse3", "grey62")) +
  theme_classic() +
  theme(axis.text.x = element_text(size=16),
        axis.text.y = element_text(size=16),
        legend.title = element_blank(),
        legend.position = "none",
        text = element_text(size=16),
        legend.text=element_text(size=16),
        axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)))
if (save_figures == 1) {
  ggsave(file = "plots/Outbound_slope_histogram_update_pos.png", width = 4, height = 2)
}


ggplot(data=subset(spatial_firing, lm_group_b == "Negative"), aes(x= asr_b_o_rewarded_fit_slope, fill=factor(unlist(lm_group_b), level = level_order))) +
  coord_cartesian(xlim = c(-0.45,0.45)) +
  geom_histogram(aes(y=..count../sum(..count..)), binwidth=0.01, alpha=0.5) +
  ylab("Proportion") +
  scale_y_continuous(breaks = scales::pretty_breaks(n = 4)) +
  scale_fill_manual(values=c("violetred2", "chartreuse3", "grey62")) +
  theme_classic() +
  theme(axis.text.x = element_text(size=16),
        axis.text.y = element_text(size=16),
        legend.title = element_blank(),
        legend.position = "none",
        text = element_text(size=16),
        legend.text=element_text(size=16),
        axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)))
if (save_figures == 1) {
  ggsave(file = "plots/Outbound_slope_histogram_update_neg.png", width = 4, height = 2)
}
```

same as above but for shuffled datasets

1. extract shuffled values into tibble _each 1000 shuffled datasets are nested for each neuron_
```{r}
shuff_slopes <- tibble(slopes = unlist(spatial_firing$shuffle_results_b_o_slope), r2 = unlist(spatial_firing$shuffle_results_b_o_r.squared))
```

### How much of the shuffled dataset is past criteria? 
1. Extract shuffled slopes and rsquared values. 
```{r}
shuff_slopes <- tibble(slopes = unlist(spatial_firing$shuffle_results_b_o_slope), 
                       r2 = unlist(spatial_firing$shuffle_results_b_o_r.squared), 
                       pval = unlist(spatial_firing$shuffle_results_b_o_p.value), 
                       min_slope = rep(spatial_firing$shuffle_min_slope_b_o, times = 1000), 
                       max_slope = rep(spatial_firing$shuffle_max_slope_b_o, times = 1000))
```

2. Function to classify shuffled cells based on shuffled distribution
```{r}
shuff_slopes <- shuff_slopes %>%
  mutate(
    shuff_lm_group_b = pmap(
      list(
        min_slope,
        max_slope,
        slopes,
        pval
      ),
      compare_slopes
    )
  )
```

2. Plot histogram of slopes
```{r}
level_order <- c("Negative", "Positive", "Unclassified")

ggplot(data=shuff_slopes, aes(x = slopes, fill=factor(unlist(shuff_lm_group_b), level = level_order))) +
    coord_cartesian(xlim = c(-0.45,0.45)) +
    geom_histogram(aes(y=..count../sum(..count..)), binwidth=0.01) +
    labs(x = "Slope (Hz/cm)") +
    ylab("Proportion") +
    scale_fill_manual(values=c("violetred2", "chartreuse3", "grey62")) +
    scale_y_continuous(breaks = scales::pretty_breaks(n = 4)) +
    theme_classic() +
    theme(axis.text.x = element_text(size=16),
          axis.text.y = element_text(size=16),
          legend.title = element_blank(),
          legend.position = "none",
          text = element_text(size=16),
          legend.text=element_text(size=16),
          axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)))
if (save_figures == 1) {
  ggsave(file = "plots/Outbound_slope_histogram_shuffled.png", width = 4, height = 2)
}
```


3. Make stacked histogram of rsquared values for real dataset
```{r}
level_order <- c("Negative", "Positive", "Unclassified")

ggplot(data=spatial_firing, aes(x= asr_b_o_rewarded_fit_r.squared, fill=factor(unlist(lm_group_b), level = level_order))) + 
  coord_cartesian(xlim = c(0,1), ylim = c(0,0.06)) +
  geom_histogram(aes(y=..count../sum(..count..)), binwidth=0.01) +
  ylab("Proportion") +
  xlab(" ") +
  scale_fill_manual(values=c("violetred2", "chartreuse3", "grey62")) +
  scale_y_continuous(breaks = scales::pretty_breaks(n = 4)) +
  theme_classic() +
  theme(axis.text.x = element_text(size=16),
        axis.text.y = element_text(size=16),
        legend.title = element_blank(),
        legend.position = "none",
        text = element_text(size=16),
        legend.text=element_text(size=16),
        axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)))
if (save_figures == 1) {
  ggsave(file = "plots/Outbound_rsquared_histogram_update.png", width = 4, height = 2)
}
```

4. Same as above but for shuffled datasets
```{r}
ggplot(data=shuff_slopes, aes(x = r2, fill=factor(unlist(shuff_lm_group_b)))) +
    coord_cartesian(xlim = c(0,1)) +
    geom_histogram(aes(y=..count../sum(..count..)), binwidth=0.01) +
    xlab(expression(R^2)) +
    ylab("Proportion") +
    scale_fill_manual(values=c("violetred2", "chartreuse3", "grey62")) +
    scale_y_continuous(breaks = scales::pretty_breaks(n = 3)) +
    theme_classic() +
    theme(axis.text.x = element_text(size=16),
          axis.text.y = element_text(size=16),
          legend.position="none",
          legend.title = element_blank(),
          text = element_text(size=16),
          legend.text=element_text(size=16),
          axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)))
if (save_figures == 1) {
  ggsave(file = "plots/Outbound_rsquared_histogram_shuffled.png", width = 4, height = 2)
}
```






### ------------------------------------------------------------------------------------------------- ### 

## Plot shuffled example for Supplemental Figure 7A

### ------------------------------------------------------------------------------------------------- ### 


1. Function to generate shuffles
- shuffles spikes using sample() function
- runs lm
- extracts coefficients
- stores coefficients for each 1000 shuffles (less memory than saving 1000 shuffles)
```{r}
# shuffles defines the number of shuffes. Use a smaller value for testing.
shuffle_rates_example <- function(df, shuffles = 10) {
  df_modified <- data.frame(neuron = as.numeric(),
                 Rates=as.double())
  names(df_modified) <- c("neuron", "Rates")
  x <- 1
  repeat {
  fr_shuffled <- sample(as.vector(unlist(df)),replace = TRUE, prob = NULL)
  data <- data.frame(as.numeric(x),list(fr_shuffled))
  names(data) <- c("neuron","Rates")
  df_modified <- rbind(df_modified,data)

  x = x+1
  if (x == shuffles){ 
  break
  }
  }
return(df_modified)
}
```

2. Run if shuffles haven't already been generated.
```{r}

# Check to see if the column shuffle_results exists. If it does then don't run again.
shuffles <- 1000
spatial_firing_example <- spatial_firing[14,] %>%
  #select(-contains('shuffle_rates')) %>%
  select(cluster_id, session_id, Rates_averaged_rewarded_b, asr_b_o_rewarded_fit_r.squared, asr_b_o_rewarded_fit_slope) %>%
  mutate(shuffle_rates = map2(Rates_averaged_rewarded_b, shuffles, shuffle_rates_example))

```

```{r}
spatial_firing_example <- spatial_firing_example %>%
  unnest_wider(shuffle_rates, names_sep = "_", names_repair = "universal")

```


Function to plot mean and SEM of firing rate as a function of position.
```{r}
position = c(-29:169)
rates = unlist(unlist(spatial_firing_example$Rates_averaged_rewarded_b))

ggplot() +
  geom_point(aes(x=position, y=rates)) +
  theme_classic() +
  annotate("rect", xmin=-30, xmax=0, ymin=5,ymax=Inf, alpha=0.2, fill="Grey60") +
  annotate("rect", xmin=140, xmax=170, ymin=5,ymax=Inf, alpha=0.2, fill="Grey60") +
  annotate("rect", xmin=60, xmax=80, ymin=5,ymax=Inf, alpha=0.2, fill="Chartreuse4") +
  scale_x_continuous(breaks=seq(-30,170,100), expand = c(0, 0)) +
  scale_y_continuous(breaks=seq(5,50,10), expand = c(0, 0)) +
  labs(y = "Mean firing rate (Hz)", x = "Position") +
  theme(axis.text.x = element_text(size=18),
        axis.text.y = element_text(size=18),
        legend.title = element_blank(),
        text = element_text(size=18),
        plot.margin = margin(21, 25, 5, 20))
 ggsave(file = "plots/ExampleShuffled_Real.png",  width = 3.6, height = 2.9) 

```



Function to plot mean and SEM of firing rate as a function of position.
```{r}

Frates = unlist(unlist(spatial_firing_example$shuffle_rates_Rates))
Fposition = rep(c(-29:169), times = as.integer(length(Frates)/199))
Ftrials = rep(c(1:999), each = 199) #198801

frame <- tibble(rates = Frates,
                position = Fposition, 
                trials = Ftrials)
                   
data_wide <- spread(frame, position, rates)

position = c(-29:169)
rates = unlist(unlist(spatial_firing_example$Rates_averaged_rewarded_b))
position_o = position[30:90]
rates_o = rates[30:90]

ggplot() +
  geom_smooth(data=frame, aes(x=frame$position, y=frame$rates, group=factor(frame$trials)), method = "lm", se = FALSE, color ="grey", alpha=0.5) +
  geom_smooth(aes(x=position, y=rates), method = "lm", se = FALSE, color ="red") +
  theme_classic() +
  xlim(0, 60) +
  #scale_x_continuous(breaks=seq(0,30,60), expand = c(0, 0)) +
  #scale_y_continuous(breaks=seq(0,40), expand = c(0, 0)) +
  labs(y = "Mean firing rate (Hz)", x = "Location (cm)") +
  theme(axis.text.x = element_text(size=18),
        axis.text.y = element_text(size=18),
        legend.title = element_blank(),
        text = element_text(size=18),
        plot.margin = margin(21, 25, 5, 20))
 ggsave(file = "plots/ExampleShuffled_ShuffledLM.png",  width = 4, height = 2.9) 

```


2. Run if shuffles haven't already been generated.
```{r}

# Check to see if the column shuffle_results exists. If it does then don't run again.
shuffles <- 1000
spatial_firing_example <- spatial_firing[14,] %>%
  select(cluster_id, session_id, Rates_averaged_rewarded_b, asr_b_o_rewarded_fit_r.squared, asr_b_o_rewarded_fit_slope) %>%
  mutate(shuffle_results = pmap(list(Rates_averaged_rewarded_b, 30, 90, shuffles), shuffle_rates))

```

2. Run on all neurons
```{r}
spatial_firing_example <- spatial_firing_example %>%
  mutate(shuffle_min_slope = map_dbl(shuffle_results, extract_min_shuffle_slopes),
         shuffle_max_slope = map_dbl(shuffle_results, extract_max_shuffle_slopes))

```


We also want to extract slopes, r2 and pvalues of the 1000 shuffles for each neuron

1. Extract shuffle results (slopes and r2 for each shuffle)
2. run on all neurons
```{r}
spatial_firing_example <- spatial_firing_example %>%
  unnest_wider(shuffle_results, names_sep = "_", names_repair = "universal") 
```

1. extract shuffled values into tibble _each 1000 shuffled datasets are nested for each neuron_
```{r}
shuff_slopes <- tibble(slopes = unlist(spatial_firing_example$shuffle_results_slope), r2 = unlist(spatial_firing_example$shuffle_results_r.squared))
```



Plot distribution of the shuffled data

1. Extract shuffled slopes and rsquared values. This is already done above.

2. Plot in scatter
```{r}
ggplot(data=spatial_firing_example) +
    geom_point(data=shuff_slopes, aes(x = slopes, y = r2)) +
    geom_point(data=spatial_firing_example, aes(x = asr_b_o_rewarded_fit_slope, y = asr_b_o_rewarded_fit_r.squared), color="Red") +
    geom_vline(xintercept = spatial_firing_example$shuffle_min_slope, linetype="dotted", 
                color = "blue", size=1) +
    geom_vline(xintercept = spatial_firing_example$shuffle_max_slope, linetype="dotted", 
                color = "blue", size=1) +  
    xlab("Slope (Hz/cm)") +
    ylab(expression(R^2)) +
    theme_classic() +
    theme(axis.text.x = element_text(size=12),
          axis.text.y = element_text(size=12),
          legend.position="bottom",
          legend.title = element_blank(),
          text = element_text(size=12),
          legend.text=element_text(size=12),
          axis.title.y = element_text(margin = margin(t = 0, r = 20, b = 0, l = 0)))
if (save_figures == 1) {
  ggsave(file = "plots/Outbound_coefficient_scatter_shuffledeg.png", width = 3.5, height = 2.5)
}
```




Function to plot mean and SEM of firing rate as a function of position.
```{r}
position = c(-29:169)
rates_measured = unlist(unlist(spatial_firing_example$Rates_averaged_rewarded_b))
position_o = c(0:60)
position_h = c(80:140)
rates_o <- rates[30:90]
rates_h <- rates[110:170]

ggplot() +
  #geom_point(aes(x=position, y=rates)) +
  geom_smooth(aes(x=position_o, y=rates_o), method = "lm", se = FALSE, color ="red") +
  theme_classic() +
  annotate("rect", xmin=-30, xmax=0, ymin=5,ymax=Inf, alpha=0.2, fill="Grey60") +
  annotate("rect", xmin=140, xmax=170, ymin=5,ymax=Inf, alpha=0.2, fill="Grey60") +
  annotate("rect", xmin=60, xmax=80, ymin=5,ymax=Inf, alpha=0.2, fill="Chartreuse4") +
  scale_x_continuous(breaks=seq(-30,170,100), expand = c(0, 0)) +
  scale_y_continuous(breaks=seq(5,50,10), expand = c(0, 0)) +
  labs(y = "Mean firing rate (Hz)", x = "Position") +
  theme(axis.text.x = element_text(size=18),
        axis.text.y = element_text(size=18),
        legend.title = element_blank(),
        text = element_text(size=18),
        plot.margin = margin(21, 25, 5, 20))
 ggsave(file = "plots/ExampleShuffled_Real.png",  width = 3.6, height = 2.9) 

```


